### 2022-09-16 src/MS1_report01.Rmd
add report for milestone 1

---
title: "Milestone 1: Play with the data"
author: "Anders"
date: "6/9/2022"
output: pdf_document
#output: html_notebook
editor_options: 
  chunk_output_type: console
---

# Load R packages
```{r include=FALSE}
# install.packages("glmnet", repos = "https://cran.us.r-project.org")
library(MASS)
library(glmnet)
library(mboost)
library(pcalg)
```

## Read data "6 genes" and create dataframes and matrixes
### NAN is removed
```{r}
df01 <- readxl::read_xlsx('/Users/anders/Documents/Master/data/SCR_SUR_6genes_noNAN.xlsx')
df02 <- df01[df01$timepoint %in% "SCR", ]
df03 <- df01[df01$timepoint %in% "SUR", ]
df04 <- df02
df04$ProliferationScore <- df03$ProliferationScore
df05 <- subset(df04, TrialArmNeo %in% "Letro+Ribo", select=-c(UniqueID, timepoint, TrialArmNeo))

ma02 <- as.matrix(subset(df02, select=-c(UniqueID, timepoint, TrialArmNeo)))
ma03 <- as.matrix(subset(df03, select=-c(UniqueID, timepoint, TrialArmNeo)))
ma04 <- as.matrix(subset(df04, select=-c(UniqueID, timepoint, TrialArmNeo)))
ma05 <- as.matrix(subset(df05))
```

## Formula for modles
```{r}
fm01 = ProliferationScore ~ CCND1 + CCNE1 + CDKN1A + ESR1 + MYC + RB1
fm02 = ProliferationScore ~ CCND1*RB1 + CCND1*CDKN1A + CCND1*ESR1 + CCNE1*CDKN1A + CCNE1*RB1 + MYC*ESR1 + MYC*CDKN1A
fm03 = ProliferationScore ~ CCND1:RB1 + CCND1:CDKN1A + CCND1:ESR1 + CCNE1:CDKN1A + CCNE1:RB1 + MYC:ESR1 + MYC:CDKN1A
```

# A: Variable selection focusing on one timpoint at a time (SCR or SUR)

## plot at SCR
```{r echo=FALSE}
par(mfrow=c(2,3), mar=rep(2,4))
names = c('CCND1', 'CCNE1', 'CDKN1A', 'ESR1', 'MYC','RB1') 
for(i in 1:6){
  x = ma02[,i+1]
  y = ma02[,1]
  plot(x, y, main=names[i])
  abline(lm(y ~ x), col = "red", lwd=3)
  mtext(paste("Correlation:", round(cor(x, y), 2)), side=1, line=-1.5, cex=1.2)
  cat(names[i])
  print(cor(x,y), method = c("pearson"))
}
```

## plot at SUR
```{r echo=FALSE}
par(mfrow=c(2,3), mar=rep(2,4))
names = c('CCND1', 'CCNE1', 'CDKN1A', 'ESR1', 'MYC','RB1') 
for(i in 1:6){
  x = ma03[,i+1]
  y = ma03[,1]
  plot(x, y, main=names[i])
  abline(lm(y ~ x), col = "red", lwd=3)
  mtext(paste("Correlation:", round(cor(x, y), 2)), side=1, line=-1.5, cex=1.2)
  cat(names[i])
  print(cor(x,y), method = c("pearson"))
}
```

## plot prolif: SCR vs SUR
```{r echo=FALSE}
par(mfrow=c(1,1))
x=df02$ProliferationScore; y=df03$ProliferationScore
plot(x, y)
abline(lm(y ~ x), col = "red", lwd=3)
mtext(paste("Correlation:", round(cor(x, y), 2)), side=1, line=-1.5, cex=1.2)
```

## plot SCR genes vs SUR Proliferation
### But: the two treatments are pooled 
```{r echo=FALSE}
par(mfrow=c(2,3), mar=rep(2,4))
names = c('CCND1', 'CCNE1', 'CDKN1A', 'ESR1', 'MYC','RB1') 
for(i in 1:6){
  x = ma02[,i+1]
  y = ma03[,1]
  plot(x, y, main=names[i])
  abline(lm(y ~ x), col = "red", lwd=3)
  mtext(paste("Correlation:", round(cor(x, y), 2)), side=1, line=-1.5, cex=1.2)
  cat(names[i])
  print(cor(x,y), method = c("pearson"))
}
```

## SCR: Step AIC/BIC
```{r}
lm01 = lm(fm01, data = df02)
lm02 = lm(fm02, data = df02)
summary(lm01)
summary(lm02)

stepAIC(lm01, direction="both", trace=0,)
stepAIC(lm02, direction="both", trace=0,)
stepAIC(lm01, direction="both", trace=0, k = log(95))
stepAIC(lm02, direction="both", trace=0, k = log(95))
```
## SUR: Step AIC/BIC
```{r}
lm03 = lm(fm01, data = df03)
lm04 = lm(fm02, data = df03)
summary(lm03)
summary(lm04)

stepAIC(lm03, direction="both", trace=0,)
stepAIC(lm04, direction="both", trace=0,)
stepAIC(lm03, direction="both", trace=0, k = log(95))
stepAIC(lm04, direction="both", trace=0, k = log(95))
```

## SCR: Lasso
```{r}
par(mfrow=c(1,1))
lasso01 <- glmnet(ma02[,-1], ma02[,1])
plot(lasso01, label = T)
print("coefficients values:")
coef(lasso01, s = 0.02)
```

## SUR: Lasso
```{r}
par(mfrow=c(1,1))
lasso02 <- glmnet(ma03[,-1], ma03[,1])
plot(lasso02, label = T)
print("coefficients values:")
coef(lasso01, s = 0.02)
```

## SCR: Lasso with cross validation
```{r}
lasso.cv01 <- cv.glmnet(ma02[,-1], ma02[,1])
plot(lasso.cv01)

lasso.cv01$lambda.min
lasso.cv01$lambda.1se
coef(lasso.cv01, s = "lambda.min")
coef(lasso.cv01, s = "lambda.1se")
```

## SUR: Lasso with cross validation
```{r}
lasso.cv02 <- cv.glmnet(ma03[,-1], ma03[,1])
plot(lasso.cv02)

lasso.cv02$lambda.min
lasso.cv02$lambda.1se
coef(lasso.cv02, s = "lambda.min")
coef(lasso.cv02, s = "lambda.1se")
```

## SCR: boosting with linear base learner
```{r}
boost00 = glmboost(fm01, data = df02)
coef(boost00, which = "")
plot(boost00, ylim=range(coef(boost00, which = colnames(df02)[5:10])))

boost01 = gamboost(fm01, data = df02,
                   family=Gaussian(),
                   baselearner="bols",
                   boost_control(mstop = 5, nu=0.1))
coef(boost01, which = "")
par(mfrow=c(2,3))
#plot(boost01, off2int=TRUE)
plot(boost01)
cols_chosen = unique(boost01$xselect())
colnames(df02)[cols_chosen+4]
boost01$xselect()
#unique(boost01$xselect())

# With interactions
boost02 = glmboost(fm02, data = df02)
coef(boost02, which = "")
#plot(boost02, ylim=range(coef(boost02, which = "CCND1,RB1,CDKN1A,ESR1,CCNE1, MYC, CCND1:RB1, CCND1:CDKN1A, #CCND1:ESR1,CDKN1A:CCNE1, RB1:CCNE1, ESR1:MYC,CDKN1A:MYC" )))

boost03 = gamboost(fm02, 
                   data = df02,
                   baselearner="bols")
unique(boost03$xselect())
print("RB1, CCND1*RB1, CCND1, CCNE1, ESR1, MYC, CDKN1A")
```

## SCR: boosting with stump as base learner
```{r}
stump01 = gamboost(fm01, data = df02, 
                   family=Gaussian(), 
                   baselearner='btree',
                   boost_control(mstop = 10))
frame()
dev.new()
par(mfrow=c(1,2), mar=rep(4,4))
plot(stump01)
cols_chosen = unique(stump01$xselect())
colnames(df02)[cols_chosen+4]
stump01$xselect()
```

## Boosting with boostrap cross-validation
```{r}
boost00.cv = cvrisk(boost00)
par(mfrow=c(1,1))
plot(boost00.cv)
mstop(boost00.cv)
boost00[mstop(boost00.cv)]
names(coef(boost00))

boost01.cv = cvrisk(boost01)
plot(boost01.cv)
mstop(boost01.cv)
boost01[mstop(boost01.cv)]
names(coef(boost01))

stump01.cv = cvrisk(stump01)
plot(stump01.cv)
mstop(stump01.cv)
stump01[mstop(stump01.cv)]
names(coef(stump01))

```

# Graphs
```{r echo=FALSE}
cor.ma02 <- cor(ma02)

pc.fit.10prec <- pc(suffStat = list(C = cor.ma02, n = 100),
             indepTest = gaussCItest, # indep.test: partial correlations
             alpha=0.1, 
             labels = colnames(cor.ma02), 
             verbose = TRUE)
pc.fit.5prec <- pc(suffStat = list(C = cor.ma02, n = 100),
             indepTest = gaussCItest, # indep.test: partial correlations
             alpha=0.05, 
             labels = colnames(cor.ma02), 
             verbose = TRUE)
```

```{r}
par(mfrow=c(1,2))
plot(pc.fit.10prec, main = "Estimated CPDAG (alpha=10%)")
plot(pc.fit.5prec, main = "Estimated CPDAG (alpha=5%)")
#as(pc.fit.10prec, "amat")
```

# B: PREDICTION

## plot gene(SCR) vs Prolif(SUR)
```{r echo=FALSE}
par(mfrow=c(2,3), mar=rep(2,4))
names = c('CCND1', 'CCNE1', 'CDKN1A', 'ESR1', 'MYC','RB1') 
for(i in 1:6){
  x = ma04[,i+1]
  y = ma04[,1]
  plot(x, y, main=names[i])
  abline(lm(y ~ x), col = "red", lwd=3)
  mtext(paste("Correlation:", round(cor(x, y), 2)), side=1, line=-1.5, cex=1.2)
  cat(names[i])
  print(cor(x,y), method = c("pearson"))
}
```

## Lasso prediction
```{r}
X  <- subset(df05, select= -ProliferationScore)
Y  <- subset(df05, select= ProliferationScore)

prediction.lasso <- function(X, Y){
  X = as.matrix(X)
  Y = as.matrix(Y)
  sample = sample.int(n=48, size=45)
  X_train = X[sample,]
  X_test = X[-sample,]
  Y_train = Y[sample,]
  Y_test = Y[-sample,]

  lasso.cv <- cv.glmnet(X_train, Y_train)
  #lasso.pred = predict(lasso, newx = as.matrix(X_test), type = "response", s = "lambda.1se")
  lasso.pred = predict(lasso.cv, newx = X_test, type = "response", s = "lambda.min")
  out = data.frame(lasso.pred, Y_test)
  return(out)
}

# prediction.lasso(X,Y)
set.seed(111)

pred.lasso.loop = function(X, Y){
  df_ <- data.frame(matrix(ncol = 2, nrow = 0))
  colnames(df_) <- c("lambda.min", "Y_test")

  for (i in c(1:100)) {
    df_ = rbind(df_, prediction.lasso(X,Y))
  }  
  return(df_)
}

df06 = pred.lasso.loop(X,Y)
```
## Results: Lasso prediction
```{r}
plot(df06[,1], df06[,2])
abline(lm(df06[,2] ~ df06[,1]), col = "red", lwd=3)
mtext(paste("Correlation:", round(cor(df06[,2], df06[,1]), 3)), side=1, line=-1, cex=1.4)

mean((df06[,1] - df06[,2])^2)
```

## Stump prediction
```{r}
prediction.stump <- function(){
  sample = sample.int(n=48, size=45)
  df_train = df05[sample,]
  df_test = df05[-sample,]

  stump = gamboost(fm01, data = df_train, 
                   family=Gaussian(), 
                   baselearner='btree',
                   boost_control(mstop = 100))

  stump.cv = cvrisk(stump)
  stump.pred = predict(stump, newdata = df_test, type = "response")

  out = data.frame(stump.pred, df_test[,1])
  return(out)
}

prediction.stump()
set.seed(111)

pred.stump.loop = function(){
  df_ <- data.frame(matrix(ncol = 2, nrow = 0))
  colnames(df_) <- c("stump.pred", "ProliferationScore")

  for (i in c(1:100)) {
    df_ = rbind(df_, prediction.stump())
  }  
  return(df_)
}

df07 <- pred.stump.loop()
```

## Results: Stump prediction
```{r}
plot(df07[,1], df07[,2])
abline(lm(df07[,2] ~ df07[,1]), col = "red", lwd=3)
mtext(paste("Correlation:", round(cor(df07[,2], df07[,1]), 3)), side=1, line=-1, cex=1.4)

mean((df07[,1] - df07[,2])^2)
```

## Prediction only at SCR
```{r}

df08 = subset(df02, select=-c(UniqueID, timepoint, TrialArmNeo))

pred.lasso.stump = function(){
  sample = sample.int(n=95, size=90)
  df_train = df08[sample,]
  df_test = df08[-sample,]

  lasso <- cv.glmnet(as.matrix(df_train[,2:7]), as.matrix(df_train[,1]))

  # lasso.pred = predict(lasso, newx = as.matrix(X_test), s = "lambda.1se")
  lasso.pred = predict(lasso, newx = as.matrix(df_test[,2:7]), type = "response", s = "lambda.min")

  stump = gamboost(fm01, data = df_train, 
                   family=Gaussian(), 
                   baselearner='btree',
                   boost_control(mstop = 100))

  stump.cv = cvrisk(stump)
  stump.pred = predict(stump, newdata = df_test, type = "response")

  out = data.frame(lasso.pred, stump.pred, df_test[,1])
  return(out)
}

pred.lasso.stump()

pred.l.s = pred.lasso.stump()

set.seed(111)

pred.l.s.loop = function(){
  df_ <- data.frame(matrix(ncol = 3, nrow = 0))
  colnames(df_) <- c("lambda.min" ,"stump.pred", "ProliferationScore")

  for (i in c(1:10)) {
    df_ = rbind(df_,  pred.lasso.stump())
  }  
  return(df_)
}

df.l.s <- pred.l.s.loop()

par(mfrow=c(1,2), mar=rep(2,4))
plot(df.l.s$lambda.min, df.l.s$ProliferationScore, main="Lasso")
abline(lm(df.l.s[,3] ~ df.l.s[,1]), col = "red", lwd=3)
mtext(paste("Correlation:", round(cor(df.l.s[,3], df.l.s[,1]), 3)), side=1, line=-1, cex=1.4)

plot(df.l.s$stump.pred, df.l.s$ProliferationScore, , main="Stump")
abline(lm(df.l.s[,3] ~ df.l.s[,2]), col = "red", lwd=3)
mtext(paste("Correlation:", round(cor(df.l.s[,3], df.l.s[,2]), 3)), side=1, line=-1, cex=1.4)

mean((df.l.s$lambda.min - df.l.s$ProliferationScore)**2)
mean((df.l.s$stump.pred - df.l.s$ProliferationScore)**2)
```

### 2023-01-25 R_codeP01/reports/MS2_report02.Rmd
started on report

---
title: "Milestone 2: Core results 01"
author: "Anders"
date: "25/1/2023"
output: pdf_document
#output: html_notebook
editor_options: 
  chunk_output_type: console
---

# Major goal
1. Predict outcome of cancer treatment with genetic profile as independent features
2. Features selection

# Data
Clinical trail on breast cancer using two different drug combination

# Evaluation
Preliminary experiments (on given data set) showed instability in prediction and feature selection between bootstrap samples. A more thorough evaluation is conducted. Two levels of evaluation is planed:

## 1. Comparison of models
1000 bootstrap models are fitted and then evaluated on the original sample. This gives a relative comparison of the various models with respect to data similar to the given data set. In addition to Correlation and MSE, frequency of selected features is compared.

## 2. Expected outcome of future patients
3 strategies are considered:  
1. Repeated cross-validations (100 rep) \
2. Bootstrap models with 0.632 (or 0.632?) adjustment \
3. Test data set from a second trail (This trail have different responses) \

# Models
## Lasso
## Post Lasso
## Ridge
## Elastic Net
## Boosting with stumps as base learner

# RESULTS

# Lasso
```{r include=TRUE}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/lb_object_AllGenes01.RData")

# Correlation
cor_vec <- as.numeric(lb_object[[1]])
sum(is.na(cor_vec))/length(cor_vec)    # fraction of NA
mean(cor_vec, na.rm=TRUE)
median(cor_vec, na.rm=TRUE)
var(cor_vec, na.rm=TRUE)
# par(mfrow=c(1,1))
hist(cor_vec, breaks = 100)

```

# Post Lasso
# Ridge
# Elastic Net
# Boosting with stumps as base learner

### 2023-01-25 R_codeP01/scripts/03_linear_regression01.R

@@ -11,6 +11,12 @@ fm02 <- Y ~ CCND1*RB1 + CCND1*CDKN1A + CCND1*ESR1 + CCNE1*CDKN1A + CCNE1*RB1 + M
 fm03 <- Y ~ CDKN1A + ESR1 + MYC + ESR1:MYC + CDKN1A:MYC
 # nodes:
 fm04 <- Y ~ cyclinD1 + cyclinD1Palbo + p21 + cyclinD1p21 + cMyc + cyclinEp21 + Rb1 + ppRb1
+# 771 genes:
+fm05 <- Y ~ page(genes, collapse("+"))
+fm05 <- as.formula(paste(Y, "~", genes))
+fm05 <- formula(paste(x, collapse = " ")) 
+fm05 <- as.formula(paste("Y", paste(genes, collapse="+"), sep=" ~ "))
+
 
 ##############################################
 ## Linear models evaluated at training data ##

### 2023-01-25 R_codeP01/scripts/08_boosting02.R

@@ -15,8 +15,9 @@ library(mboost)
 
 # linear base learner
 fm01 <- Y ~ CCND1 + CCNE1 + CDKN1A + ESR1 + MYC + RB1
+fm05 <- as.formula(paste("Y", paste(genes, collapse="+"), sep=" ~ "))
 
-boost_bootstrap_sample <- function(df_train, df_test, method="pearson"){
+boost_bootstrap_sample <- function(fm, df_train, df_test, method="pearson"){
   # one bootstrap sample
   # output: 
   # 1. correlation between prediction and full input sample  (pearson or spearman should be set)
@@ -27,12 +28,12 @@ boost_bootstrap_sample <- function(df_train, df_test, method="pearson"){
   int <- sample.int(n, size = n, replace = TRUE)
   data_train = df_train[int,]
   
-  # fit <- glmboost(fm01, data = data_train)
-  # fit <- gamboost(fm01, data = data_train,
+  # fit <- glmboost(fm, data = data_train)
+  # fit <- gamboost(fm, data = data_train,
   #                      baselearner = "bbs", # dfbase=4
   #                      control = boost_control(mstop = 50))
   
-  fit = gamboost(fm01, data = data_train, 
+  fit = gamboost(fm, data = data_train, 
                      family=Gaussian(), 
                      baselearner='btree',
                      boost_control(mstop = 50))
@@ -49,10 +50,10 @@ boost_bootstrap_sample <- function(df_train, df_test, method="pearson"){
   return(list(cor=cor, co=co, inds=inds, MSE=MSE))
 }
 
-boost_bootstrap_sample(Proliferation_6genes, Proliferation_6genes)
+boost_bootstrap_sample(fm01, Proliferation_6genes, Proliferation_6genes)
 
 # 1000 bootstrap fits
-boost_boot = function(df_train, df_test, method="pearson", n_bootstraps=1000){
+boost_boot = function(fm, df_train, df_test, method="pearson", n_bootstraps=1000){
   # run many bootstraps
   # output: - vector with correlations 
   #         - vector with selected features as integers values wrt to X
@@ -62,7 +63,7 @@ boost_boot = function(df_train, df_test, method="pearson", n_bootstraps=1000){
   inds_vec <- integer(length = 0)
   MSE_vec <- rep(NA, n_bootstraps)
[…]

### 2023-01-26 R_codeP01/scripts/01_dataclean02.R
started with XGboost

@@ -32,10 +32,6 @@ ext.OS_months <- df04 |> select(OS_months)
 
 
 
-
-
-
-
 ########################################
 ## 771 GENES + ROR categorical output ##
 ########################################

### 2023-01-26 R_codeP01/scripts/test.R

@@ -1,3 +1,38 @@
+
+
+
+# Load the dataframe
+data(mtcars)
+
+# Convert the dataframe to a DMatrix object
+dtrain <- xgb.DMatrix(data = as.matrix(mtcars[, -1]), label = mtcars$mpg)
+
+dtrain <- xgb.DMatrix(data = data.matrix(mtcars[,-1]), label = mtcars$mpg)
+
+
+
+
+
+# Create the dataset
+data(agaricus.train, package='xgboost')
+dtrain <- xgb.DMatrix(agaricus.train$data, label = agaricus.train$label)
+
+# Set the xgboost parameters
+params <- list(objective = "binary:logistic",
+               eta = 0.3,
+               max_depth = 2)
+
+# Find the best iteration using the cv function
+cv <- xgb.cv(params = params, data = dtrain, nrounds = 10, nfold = 5, showsd = T, stratified = T)
+best_iteration <- which.min(cv$evaluation_log$test_error_mean)
+
+# Train the model with the best iteration
+xgb.train(params = params, data = dtrain, nrounds = best_iteration)
+
+
+
+
+
 library(glmnet)
 
 # load data
@@ -31,3 +66,16 @@ idx = which(fit$cvm == min_error)
 best_alpha = fit$alpha[idx]
 best_lambda = fit$lambda[idx]
 
+
+
+# Create a dataset for demonstration purposes
+set.seed(123)
+x <- matrix(rnorm(200*5), ncol = 5)
+y <- rnorm(200)
+
+# Fit the model using mboost
+model <- mboost(x, y, control = boost_control(mstop = 5, base_learners = "stump"))
+model <- gamboost(x, y, control = boost_control(mstop = 5, base_learners = "stump"))
+model <- gamboost(y~.,data = df,control = boost_control(mstop = 5, base_learners = "stump"))
+# Print the model
+print(model)

### 2023-01-27 R_codeP01/reports/MS2_report02.Rmd
worked on XGboost and rapport

@@
 
+<!-- ```{r echo=FALSE}  -->
+<!-- knitr::opts_chunk$set(echo=FALSE)  -->
+<!-- ``` -->
+
+```{r global-options, include=FALSE}
+knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='Figs/',
+                      echo=FALSE, warning=FALSE, message=FALSE)
+```
+# Data
+Two clinical trails on breast cancer (advanced HR+/HER2- and HER2-E breast cancer) using two different drug combination
+## Trail 1
+Two treatments which differ with respect to drug combination 
+- Target: ribociclib and endocrine therapy (letrozole)
+- Chemotherapy: doxorubicin, cyclophosphamide and paclitaxel. 
+approx. 50 patients in each group.
+Endpoints: proliferation score, ROR score
+
+## Trail 2
+The primary objective of this study is to compare two cdk4/6 targeted drugs (Palbociclib, n=36; Abemaciclib, n=3 in combination with endocrine therapy (tamoxifen, fulvestrant or aromatase inhibitors,  I think?)
+
+Endpoints: progression free survival (months), OS?, and status of the two former (dont know what that means)
+
 # Major goal
-1. Predict outcome of cancer treatment with genetic profile as independent features
-2. Features selection
+1. Find best model to predict outcome of cancer treatment with genetic profile as predictive features
+2. Features selection in order to understand cancer biology
 
-# Data
-Clinical trail on breast cancer using two different drug combination
+# Major challanges
+Preliminary experiments (on trail 1) showed instability in prediction and feature selection between bootstrap samples og Lasso. I believe this is a classical problem of high-dim data?
 
-# Evaluation
-Preliminary experiments (on given data set) showed instability in prediction and feature selection between bootstrap samples.
-A more thorough evaluation is conducted.
-Two levels of evaluation is planed:
+# Approch
+Test all thinkable models to see if some is surperior
+
+# Evaluation of models
+Two levels of evaluation is scheduled:
 
@@
 ## Boosting with stumps as base learner
+### - mboost
+### - xgboost
+## Feature selecting ensemble model
 

### 2023-01-27 R_codeP01/scripts/08_boosting03.R

@@ -19,13 +19,6 @@ fm01 <- Y ~ CCND1 + CCNE1 + CDKN1A + ESR1 + MYC + RB1
 fm05 <- as.formula(paste("Y", paste(genes, collapse="+"), sep=" ~ "))
 
 XGboost_bootstrap_sample <- function(fm, df_train, df_test, method="pearson") {
-  # one bootstrap sample
-  # data input need to be dataframe
-  # output: 
-  # 1. correlation between prediction and full input sample  (pearson or spearman should be set)
-  # 2. Coefficients of variables 
-  # 3. MSE
-  
   n = dim(df_train)[1]
   int <- sample.int(n, size = n, replace = TRUE)
   df_fit = df_train[int,]
@@ -38,57 +31,78 @@ XGboost_bootstrap_sample <- function(fm, df_train, df_test, method="pearson") {
   validation_sparse = sparse.model.matrix(object = fm01, data = df_test)
   dvalidation = xgb.DMatrix(data = validation_sparse, label = df_test$Y)
 
-  xgb_params = list(eta = 0.1, max_depth = 1)
-  N_ROUNDS = 1000
+  param <- list(booster = "gbtree", 
+                objective = "reg:squarederror", 
+                eval_metric = "rmse", 
+                # nthread = 4, 
+                max_depth = 1, 
+                min_child_weight = 1,
+                tree_method = "hist",   # tree_methods=  exact, approx and hist, depending on the dataset size, memory and time constraints
+                #eta_decay=0.1,
+                eta=0.3)
+ # param <- list(eta = 0.1, max_depth = 5)
+
+  cv <- xgb.cv(data = dtrain, 
+               params = param, 
+               nrounds = 100, 
+               nfold = 5, 
+               #showsd = T, stratified = T,
+               print_every_n = 10,
+               early_stopping_rounds = 5,
+               verbose = FALSE)
+  
+  n_rounds <- cv$best_iteration
+  
   xgb_model = xgb.train(data = dtrain,
                         # The following is needed if to monitor training and validation error
-                        watchlist = list(train = dtrain, 
-                                         val = dvalidation),
-                        params = xgb_params,
-                        nrounds = N_ROUNDS,
+                        # watchlist = list(train = dtrain, 
[…]

### 2023-01-27 R_codeP01/scripts/test.R

@@ -1,3 +1,56 @@
+# Here I added the following parameters:
+#   max_depth = 1: This tells XGBoost to use a tree with a depth of 1 (i.e., a stump).
+#   min_child_weight = 1: This tells XGBoost to use a single decision tree as the base learner
+#   tree_method = "hist": This tells XGBoost to use histogram-based algorithm for decision tree learning.
+#   You can use different tree_methods like exact, approx and hist, depending on the dataset size, memory and time constraints.
+# 
+
+
+
+# Load the training and test datasets
+train <- read.csv("train.csv")
+test <- read.csv("test.csv")
+
+# Define the label and feature columns
+label_column <- "target"
+feature_columns <- setdiff(colnames(train), label_column)
+
+# Define the xgboost parameters
+param <- list(booster = "gbtree", 
+              objective = "reg:squarederror", 
+              eval_metric = "rmse", 
+              nthread = 4, 
+              max_depth = 1, 
+              min_child_weight = 1,
+              tree_method = "hist")
+
+# Define the xgboost train control with large number of rounds and early stopping
+train_control <- xgb.cv(data = as.matrix(train[, feature_columns]), 
+                        label = train[, label_column], 
+                        nrounds = 10000,
+                        nfold = 5, 
+                        early_stopping_rounds = 10, 
+                        verbose = FALSE, 
+                        print_every_n = 10, 
+                        seed = 123, 
+                        params = param)
+
+# Select the optimal nrounds
+best_nrounds <- train_control$best_ntreelimit
+
+# Train the final model using the optimal nrounds
+model <- xgboost(data = as.matrix(train[, feature_columns]), 
+                 label = train[, label_column], 
+                 nrounds = best_nrounds, 
+                 nthread = 4, 
+                 verbose = FALSE, 
+                 params = param)
+
+# Make predictions on the test dataset
+predictions <- predict(model, as.matrix(test[, feature_columns]))
+
+
+
 
 
 
@@ -29,6 +82,47 @@ best_iteration <- which.min(cv$evaluation_log$test_error_mean)
 # Train the model with the best iteration
 xgb.train(params = params, data = dtrain, nrounds = best_iteration)
 
+#######################################################################
+# Load necessary libraries
+library(xgboost)
+
+# Load the training and test datasets
+train <- read.csv("train.csv")
+test <- read.csv("test.csv")
+
+# Define the label and feature columns
+label_column <- "target"
+feature_columns <- setdiff(colnames(train), label_column)
+
[…]

### 2023-01-29 R_codeP01/scripts/01_dataclean01.R
finished repeated cross-validation on Lasso

@@ -51,7 +51,7 @@ df_6genes_with_output <- function(output){
     filter(timepoint=="SUR") |> 
     filter(TrialArmNeo=="Letro+Ribo")
   
-  df_6genes <- full_join(df_genes, df_output, by = "UniqueID")
+  df_6genes <- full_join(df_output, df_genes, by = "UniqueID")
   
   #rename(df_6genes, c("Y") = c(output))
   colnames(df_6genes)[which(names(df_6genes) == output)] <- "Y"
@@ -82,10 +82,12 @@ df_Nodes_with_output <- function(output){
     filter(timepoint=="SUR") |> 
     filter(TrialArmNeo=="Letro+Ribo")
   
-  df_Nodes_Y <- full_join(df_features, df_output, by = "UniqueID")
-  #rename(df_6genes, c("Y") = c(output))
+  df_Nodes_Y <- full_join(df_output, df_features, by = "UniqueID")
+
   colnames(df_Nodes_Y)[which(names(df_Nodes_Y) == output)] <- "Y"
   print(output)
+  
+  df_Nodes_Y <- df_Nodes_Y |> select(-c(UniqueID, timepoint.x, TrialArmNeo.x, timepoint.y, TrialArmNeo.y)) # remove unnecessary columns
   df_Nodes_Y <- na.omit(df_Nodes_Y) # remove row containing NA
   return(df_Nodes_Y)
 }
@@ -120,15 +122,16 @@ df_genes_with_output <- function(df, predictors, output){
   df_output <- df |> select(c(UniqueID, output, timepoint, TrialArmNeo)) |>
     filter(timepoint=="SUR") |> 
     filter(TrialArmNeo=="Letro+Ribo")
-  
-  df_out <- full_join(df_genes, df_output, by = "UniqueID") |> 
-    select(-UniqueID)
+
+  df_out <- full_join(df_output, df_genes, by = "UniqueID")
   
   colnames(df_out)[which(names(df_out) == output)] <- "Y"
-  print(output)
+  
+  df_out <- df_out |> select(-c(UniqueID, timepoint.x, TrialArmNeo.x, timepoint.y, TrialArmNeo.y)) # remove unnecessary columns
   df_out <- na.omit(df_out) # remove rows with missing values
   return(df_out)
 }
+
 
 Proliferation_ALLgenes <- df_genes_with_output(df01, genes, "ProliferationScore")
 Proliferation_ALLgenes <- df_genes_with_output(df01, genes, "ROR_P_Subtype_Proliferation")

### 2023-01-29 R_codeP01/scripts/04_lasso03.R

@@ -1,69 +1,101 @@
-## Lasso using bootstrap sample to train 1000 models
+## Repeated cross-validation for testing the Lasso model
+##
+## Test against the fold
 ## Cross-validation (5-fold) used for training/tuning lambda and selecting features
-## Test against original data sample and leave-out bootstrap sample
 ## output: selected genes; proliferation.score correlation; SEM
 
 ## Post Lasso model is made at the bottom
 
 library(glmnet)
+library(caret)
+library(ggplot2)
 
 ###########################################################
 ##  Repeated cross validation ##
 ###########################################################
 
-
-lasso_sample <- function(data, lambda.min=TRUE){
-  X_ <- as.matrix(data |> 
-                   select(CCND1, CCNE1, CDKN1A, ESR1, MYC, RB1))
-  Y_ <- as.matrix(select(data, Y))
-
-  fit.cv <- cv.glmnet(X_, Y_, nfolds = 5)
+# Custom function for repeated k-fold cross validation
+repeated_kfold_cv <- function(data, func=lasso_sample, folds=5, repeats=100) {
   
-  features <- coef(fit.cv, s = "lambda.min")
-  inds <- which(features != 0)
-  # If want to print selected features
-  # inds <- inds[-1] # dropping the first covariates 
-  # variables <- row.names(co)[inds]
-  # variables <- variables[!(variables %in% '(Intercept)')];
+  correlations <- numeric(repeats * folds)
+  print(length(correlations))
+  MSE_vec <- rep(NA, repeats * folds)
+  coef_matrix <- matrix(NA, nrow = repeats*folds, ncol = ncol(data[,-1]))
+  colnames(coef_matrix) <- colnames(data[, -1])
+  coef_matrix_row_index <- 1
   
-  if (lambda.min == TRUE) {
-    pred_values = predict(fit.cv, newx = ext.X, type = "response", s = "lambda.min")      
+  # Repeat the cross-validation process
+  for (i in 1:repeats) {
+    # Create the folds for evaluating the performance
+    kf <- caret::createFolds(data[,1], k = folds, list = TRUE, returnTrain = TRUE)
+    # Loop through the folds
+    for (j in 1:folds) {
+      # Get the training and testing data
+      train_data <- data[kf[[j]],]
[…]

### 2023-01-29 R_codeP01/scripts/test02.R

@@ -1,52 +1,79 @@
 library(caret)
-
+library(ggplot2)
 
 # Custom function for repeated k-fold cross validation
-repeated_kfold_cv <- function(data, response=Y, func=lasso_sample, k=5, repeats=100) {
-  # Initialize empty lists to store results
-  results_list <- list()
+repeated_kfold_cv <- function(data, func=lasso_sample, folds=5, repeats=100) {
   
-  # Loop for the number of repeats
+  correlations <- numeric(repeats * folds)
+  print(length(correlations))
+  SEM_vec <- rep(NA, repeats * folds)
+  coef_matrix <- matrix(NA, nrow = repeats*folds, ncol = ncol(data[,-1]))
+  colnames(coef_matrix) <- colnames(data[, -1])
+  coef_matrix_row_index <- 1
+  
+  # Repeat the cross-validation process
   for (i in 1:repeats) {
-    # Perform k-fold cross validation
-    print(data$response)
-    kf <- caret::createFolds(data$Y, k = k, list = TRUE, returnTrain = TRUE)
+    # Create the folds for evaluating the performance
+    kf <- caret::createFolds(data[,1], k = folds, list = TRUE, returnTrain = TRUE)
     # Loop through the folds
-    for (j in 1:k) {
+    for (j in 1:folds) {
       # Get the training and testing data
       train_data <- data[kf[[j]],]
       test_data <- data[-kf[[j]],]
-      test_data <- as.matrix(test_data |> select(-Y))
+
+      # Fit the function on the training data and get results
+      fit <- func(train_data)
       
-      # Fit the function on the training data and get the results
-      fit.cv <- func(train_data)
-      co <- coef(fit.cv, s = "lambda.min")
-      #co <- (co != 0)
-      co <- co[-which(rownames(co) == "(Intercept)"), ]
-      inds <- which(co != 0)
-      #co <- colnames(inds)
-      print(names(co[inds]))
- 
-      # test_results <- predict(model_fit, newdata = test_data)
+      coef_matrix[coef_matrix_row_index, ] <- coef(fit, s = "lambda.min")[-1]
       
-      test_results = predict(fit.cv, newx = test_data, type = "response", s = "lambda.min")  
+      pred = predict(fit, newx = as.matrix(test_data)[,-1], type = "response", s = "lambda.min")  
[…]

### 2023-01-29 R_codeP01/scripts/test03.R

@@ -1,0 +1,58 @@
+library(glmnet)
+library(caret)
+
+# Define the number of repeats and folds
+repeats = 200
+folds = 5
+
+# Load your data into a variable called "data"
+# Make sure the response variable is in the first column and the feature variables are in the remaining columns
+data = Proliferation_6genes
+  
+
+
+# Initialize variables to store the results
+# correlations = c()
+# selected_features = matrix(0, nrow = repeats * folds, ncol = ncol(data) - 1)
+
+# Initialize lists to store the results
+correlations <- list()
+selected_features <- list()
+
+
+# Repeat the cross-validation process
+for(i in 1:repeats) {
+  # Create the folds
+  cv_split = createFolds(data[,1], k = folds, list = TRUE, returnTrain = TRUE)
+  
+  # Fit the Lasso model and collect the selected features
+  fit = cv.glmnet(data[-1], data[,1], family = "gaussian", alpha = 1, standardize = TRUE, type.measure = "mse", foldid = cv_split, nlambda = 100)
+  selected_features[[i]] = (coef(fit, s = "lambda.min") != 0)
+  
+  # Collect the correlations
+  predictions <- predict(fit, newx = data[-1])
+  correlations[[i]] <- cor(predictions, data[,1])
+}
+
+
+
+
+
+# Fit the Lasso model and collect the results for each repeat and fold
+for (i in 1:length(cv_split)) {
+  train_data = data[cv_split[[i]],]
+  test_data = data[-cv_split[[i]],]
+  
+  # Fit the Lasso model on the training data
+  lasso_fit = cv.glmnet(x = as.matrix(train_data[,-1]), y = train_data[,1], family = "gaussian", alpha = 1)
+  
+  # Make predictions on the test data
+  test_predictions = predict(lasso_fit, newx = as.matrix(test_data[,-1]))
+  
+  # Calculate the correlation between the predicted and actual test responses
+  corr = cor(test_predictions, test_data[,1])
+  correlations = c(correlations, corr)
+  
+  # Collect the selected features from the Lasso model
+  selected_features[i, colSums(abs(coef(lasso_fit)) > 0) > 0] = selected_features[i, colSums(abs(coef(lasso_fit)) > 0) > 0] + 1
+}

### 2023-01-29 R_codeP01/scripts/04_lasso03.R
Preapering for post lasso

@@ -49,11 +49,13 @@ repeated_kfold_cv <- function(data, func=lasso_sample, folds=5, repeats=100) {
   }
   return(list(correlations=correlations, coef_matrix=coef_matrix, MSE_vec=MSE_vec))
 }
+
 # Set repeats and folds of the cross-validations
 repeats = 100
 folds = 5
-
+# RUN
 lasso_k_ob  <- repeated_kfold_cv(Proliferation_ALLgenes, lasso_sample, folds, repeats)
+
 head(lasso_k_ob$coef_matrix)[,1:10]
 mean(na.omit(lasso_k_ob$correlations))
 
@@ -62,8 +64,7 @@ frequency <- data.frame(Feature = colnames(lasso_k_ob$coef_matrix), Frequency = 
 frequency <- frequency[order(frequency$Frequency, decreasing = TRUE),]
 frequency[1:3, 1:2]
 
-
-# Create a bar plot of the selection frequency of the features
+# Bar plot of the selection frequency of the features
 ggplot(frequency[1:50,], aes(x = Frequency, y = reorder(Feature, Frequency))) +
   geom_bar(stat = "identity") +
   xlab("Selection Frequency") +
@@ -71,7 +72,7 @@ ggplot(frequency[1:50,], aes(x = Frequency, y = reorder(Feature, Frequency))) +
   ggtitle("Selection Frequency of Features") +
   theme(axis.text.y = element_text(angle = 0, hjust = 0))
 
-# Create a histogram over correlations
+# Histogram over correlations
 correlations_finite <- lasso_k_ob$correlations[is.finite(lasso_k_ob$correlations)]
 MSE_df <- data.frame(correlation = correlations_finite)
 
@@ -81,7 +82,7 @@ ggplot(corr_df, aes(x=correlation)) +
   ylab("Frequency") +
   ggtitle("Histogram of Correlation Values")
 
-# Create a histogram over MSE
+# Histogram over MSE
 MSE_finite <- lasso_k_ob$MSE_vec[is.finite(lasso_k_ob$MSE_vec)]
 corr_df <- data.frame(correlation = MSE_finite)
 
@@ -91,7 +92,28 @@ ggplot(corr_df, aes(x=MSE_vec)) +
   ylab("Frequency") +
   ggtitle("Histogram of Correlation Values")
 
+## Extracting best features
+# calculate the number of features to keep
+num_features_to_keep <- round(0.1 * ncol(lasso_k_ob$coef_matrix))
 
[…]

### 2023-01-30 R_codeP01/reports/MS2_report02.Rmd
Working on report

@@
 # Data
-Two clinical trails on breast cancer (advanced HR+/HER2- and HER2-E breast cancer) using two different drug combination
-## Trail 1
+One clinical trails on breast cancer (advanced HR+/HER2- and HER2-E breast cancer) using two different drug combination; and a cohorts study (here used as test data set). /
+Both data set have 771 genes. This genes are specifically selected based likely potential role in breast cancer. /
+The gene set is dived into X numbers of "signature genes"; which are thought to represent unities with respect to cancer biology...
+
+## Trail
 Two treatments which differ with respect to drug combination 
@@
 
-## Trail 2
+## Cohort
 The primary objective of this study is to compare two cdk4/6 targeted drugs (Palbociclib, n=36; Abemaciclib, n=3 in combination with endocrine therapy (tamoxifen, fulvestrant or aromatase inhibitors,  I think?)
@@
 # Major challanges
-Preliminary experiments (on trail 1) showed instability in prediction and feature selection between bootstrap samples og Lasso. I believe this is a classical problem of high-dim data?
+Preliminary experiments (on trail 1) showed instability in prediction and feature selection between bootstrap samples of Lasso. I believe this is a classical problem of high-dim data?
 
@@
 
-## 1. Comparison of models
+## 1. Relative comparison of models
 1000 bootstrap models are fitted and then evaluated on the original sample.
@@
 # Lasso
-```{r include=TRUE}
+```{r}
 load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/lb_object_AllGenes01.RData")
@@
 cor_vec <- as.numeric(lb_object[[1]])
-sum(is.na(cor_vec))/length(cor_vec)    # fraction of NA
-mean(cor_vec, na.rm=TRUE)
-median(cor_vec, na.rm=TRUE)
-var(cor_vec, na.rm=TRUE)
+cat("Fraction no selected features:", sum(is.na(cor_vec))/length(cor_vec) )   # fraction of NA
+cat("Mean correlation:", mean(cor_vec, na.rm=TRUE))
+cat("Median correlation:", median(cor_vec, na.rm=TRUE))
+cat("Variance", var(cor_vec, na.rm=TRUE))
 # par(mfrow=c(1,1))
 hist(cor_vec, breaks = 100)
+
+```
+
+```{r}
+load("/Users/anders/Documents/MASTER/Cancer/model_instances/lk_AllGenesProlif.RData")
+
+## ANALYSIS
+sum(is.na(lasso_k_ob$correlations))/length(lasso_k_ob$correlations)    # fraction of NA
+
+## Correlations
+mean(na.omit(lasso_k_ob$correlations))
+mean(lasso_k_ob$correlations, na.rm=TRUE)
+median(lasso_k_ob$correlations, na.rm=TRUE)
+var(lasso_k_ob$correlations, na.rm=TRUE)
+sd(na.omit(lasso_k_ob$correlations))
+
+# Histogram
+correlations_finite <- lasso_k_ob$correlations[is.finite(lasso_k_ob$correlations)]
+cor_df <- data.frame(correlation = correlations_finite)
+
+ggplot(cor_df, aes(x=correlation)) +
+  geom_histogram(bins = 30, color = "black", fill = "white") +
+  xlab("Correlation") +
+  ylab("Frequency") +
+  ggtitle("Histogram of Correlation Values")
+
+## MSE
+mean(lasso_k_ob$MSE_vec)
+sd(lasso_k_ob$MSE_vec)
+# Histogram
+MSE_df <- data.frame(MSE = lasso_k_ob$MSE_vec)
+
+ggplot(MSE_df, aes(x=MSE)) +
+  geom_histogram(bins = 30, color = "black", fill = "white") +
+  xlab("MSE") +
+  ylab("Frequency") +
+  ggtitle("Histogram of MSE Values")
+
+## Most prevalent Features
+# Order the features based on their selection frequency
+frequency <- data.frame(Feature = colnames(lasso_k_ob$coef_matrix), Frequency = colSums(lasso_k_ob$coef_matrix != 0) / (repeats * folds))
+frequency <- frequency[order(frequency$Frequency, decreasing = TRUE),]
+frequency[1:5, 1:2]
+
+# Bar plot of the selection frequency of the features
+n_best <- 50
+ggplot(frequency[1:n_best ,], aes(x = Frequency, y = reorder(Feature, Frequency))) +
+  geom_bar(stat = "identity") +
+  xlab("Selection Frequency") +
+  ylab("Features") +
+  ggtitle("Selection Frequency of Features") +
+  theme(axis.text.y = element_text(angle = 0, hjust = 0))
+
+## Extracting best features
+# calculate the number of features to keep
+perc_best <- 0.1
+num_features_to_keep <- round(perc_best * ncol(lasso_k_ob$coef_matrix))
+# count the frequency of each feature in coef_matrix
+counts <- colSums(lasso_k_ob$coef_matrix != 0)
+# sort the features based on their frequency
+sorted_features <- names(sort(counts, decreasing = TRUE))
+sorted_features[1:num_features_to_keep]
+
+## Extracting best features for POST lasso
+# extract the top features
+perc_best <- 0.1 # the %/100 best fraction 
+top_features_with_index = which(colSums(lasso_k_ob$coef_matrix != 0) >= perc_best * repeats)
+top_feature_names = colnames(lasso_k_ob$coef_matrix)[top_features_with_index]
+# make linear formula of top features
+response <- "Y"
+formula_string <- paste(response, "~", paste(top_features, collapse = " + "))
+formula <- as.formula(formula_string)
+# Make data.frame containing only top features
+post_lasso_df <- cbind(Proliferation_ALLgenes[, 1], Proliferation_ALLgenes[, top_features_with_index + 1])
+colnames(post_lasso_df)[1] <- "Y"
 

### 2023-01-30 R_codeP01/scripts/01_dataclean01.R

@@ -108,9 +108,7 @@ Y <- as.matrix(select(Nodes_Proliferation, Y))
 # select all gene names from original data table structure
 genes <- colnames(df01 |> select(41:811))
 genes <- colnames(df01 |> select(41:46)) # just for testing with fewer features
-
 length(genes)
-
 
 df_genes_with_output <- function(df, predictors, output){
   features <- c("UniqueID", "timepoint", "TrialArmNeo", predictors)

### 2023-01-30 R_codeP01/scripts/04_lasso03.R

@@ -15,7 +15,7 @@ library(ggplot2)
 ###########################################################
 
 # Custom function for repeated k-fold cross validation
-repeated_kfold_cv <- function(data, func=lasso_sample, folds=5, repeats=100) {
+repeated_kfold_cv <- function(data, func=lasso_sample, folds=5, repeats=200) {
   
   correlations <- numeric(repeats * folds)
   print(length(correlations))
@@ -50,91 +50,102 @@ repeated_kfold_cv <- function(data, func=lasso_sample, folds=5, repeats=100) {
   return(list(correlations=correlations, coef_matrix=coef_matrix, MSE_vec=MSE_vec))
 }
 
+# Lasso base function returning a trained object
+lasso_sample <- function(train_data){
+  X_ <- as.matrix(train_data |> select(-1))
+  Y_ <- as.matrix(train_data |>  select(1))
+  fit.cv <- cv.glmnet(X_, Y_, family = "gaussian", alpha = 1, standardize = TRUE, nlambda = 100)
+  return(fit.cv)
+}
+
 # Set repeats and folds of the cross-validations
-repeats = 100
+repeats = 200
 folds = 5
 # RUN
+set.seed(123)
 lasso_k_ob  <- repeated_kfold_cv(Proliferation_ALLgenes, lasso_sample, folds, repeats)
-
 head(lasso_k_ob$coef_matrix)[,1:10]
-mean(na.omit(lasso_k_ob$correlations))
+save(lasso_k_ob, file="/Users/anders/Documents/MASTER/Cancer/model_instances/lk_AllGenesProlif.RData")
+load("/Users/anders/Documents/MASTER/Cancer/model_instances/lk_AllGenesProlif.RData")
 
+## ANALYSIS
+sum(is.na(lasso_k_ob$correlations))/length(lasso_k_ob$correlations)    # fraction of NA
+
+## Correlations
+mean(na.omit(lasso_k_ob$correlations))
+mean(lasso_k_ob$correlations, na.rm=TRUE)
+median(lasso_k_ob$correlations, na.rm=TRUE)
+var(lasso_k_ob$correlations, na.rm=TRUE)
+sd(na.omit(lasso_k_ob$correlations))
+
+# Histogram
+correlations_finite <- lasso_k_ob$correlations[is.finite(lasso_k_ob$correlations)]
+cor_df <- data.frame(correlation = correlations_finite)
+
+ggplot(cor_df, aes(x=correlation)) +
[…]

### 2023-01-30 R_codeP01/scripts/test02.R

@@ -1,48 +1,5 @@
-library(caret)
-library(ggplot2)
 
-# Custom function for repeated k-fold cross validation
-repeated_kfold_cv <- function(data, func=lasso_sample, folds=5, repeats=100) {
-  
-  correlations <- numeric(repeats * folds)
-  print(length(correlations))
-  SEM_vec <- rep(NA, repeats * folds)
-  coef_matrix <- matrix(NA, nrow = repeats*folds, ncol = ncol(data[,-1]))
-  colnames(coef_matrix) <- colnames(data[, -1])
-  coef_matrix_row_index <- 1
-  
-  # Repeat the cross-validation process
-  for (i in 1:repeats) {
-    # Create the folds for evaluating the performance
-    kf <- caret::createFolds(data[,1], k = folds, list = TRUE, returnTrain = TRUE)
-    # Loop through the folds
-    for (j in 1:folds) {
-      # Get the training and testing data
-      train_data <- data[kf[[j]],]
-      test_data <- data[-kf[[j]],]
 
-      # Fit the function on the training data and get results
-      fit <- func(train_data)
-      
-      coef_matrix[coef_matrix_row_index, ] <- coef(fit, s = "lambda.min")[-1]
-      
-      pred = predict(fit, newx = as.matrix(test_data)[,-1], type = "response", s = "lambda.min")  
-      correlations[coef_matrix_row_index]  <- suppressWarnings(cor(pred, test_data[,1]))
-      MSE_vec <- mean((pred - test_data[,1])^2)
-      
-      cat(coef_matrix_row_index, "")
-      coef_matrix_row_index <- coef_matrix_row_index + 1
-    }
-  }
-  return(list(correlations=correlations, coef_matrix=coef_matrix, MSE_vec=MSE_vec))
-}
-# Set repeats and folds of the cross-validations
-repeats = 100
-folds = 5
-
-lasso_k_ob  <- repeated_kfold_cv(Proliferation_ALLgenes, lasso_sample, folds, repeats)
-head(lasso_k_ob$coef_matrix)[,1:10]
-mean(na.omit(lasso_k_ob$correlations))
 
 # Order the features based on their selection frequency
 frequency <- data.frame(Feature = colnames(lasso_k_ob$coef_matrix), Frequency = colSums(lasso_k_ob$coef_matrix != 0) / (repeats * folds))
[…]

### 2023-01-30 R_codeP01/reports/MS2_report02.Rmd
worked on report

--- 2023-01-27 R_codeP01/reports/MS2_report02.Rmd
@@
 ```
+
+```{r}
+library(ggplot2)
+```
+
 # Data
-Two clinical trails on breast cancer (advanced HR+/HER2- and HER2-E breast cancer) using two different drug combination
-## Trail 1
+One clinical trails on breast cancer (advanced HR+/HER2- and HER2-E breast cancer) using two different drug combination; and a cohorts study (here used as test data set). /
+Both data set have 771 genes. This genes are specifically selected based likely potential role in breast cancer. /
+The gene set is dived into X numbers of "signature genes"; which are thought to represent unities with respect to cancer biology...
+
+## Trail
 Two treatments which differ with respect to drug combination 
@@
 # Lasso
-```{r include=TRUE}
-load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/lb_object_AllGenes01.RData")
 
-# Correlation
-cor_vec <- as.numeric(lb_object[[1]])
-sum(is.na(cor_vec))/length(cor_vec)    # fraction of NA
-mean(cor_vec, na.rm=TRUE)
-median(cor_vec, na.rm=TRUE)
-var(cor_vec, na.rm=TRUE)
-# par(mfrow=c(1,1))
-hist(cor_vec, breaks = 100)
+```{r}
+report02_out <- function(object){
+  cor_vec <- object$correlations
+  n_models <- length(cor_vec)
+  fr <- sum(is.na(cor_vec))/n_models
+  cat("Fraction of model fits with no selected genes:", fr, "\n")
+  print("Correlation results:")
+  cat("Mean correlation:", mean(na.omit(cor_vec)), "\n") 
+  cat("Median correlation:", median(cor_vec, na.rm=TRUE), "\n")
+  cat("Variance", var(cor_vec, na.rm=TRUE), "\n")
+  print("st.dev.:")
+  print(sd(na.omit(lasso_k_ob$correlations)))
 
+  # Histogram correlations
+  correlations_finite <- cor_vec[is.finite(cor_vec)]
+  cor_df <- data.frame(correlation = correlations_finite)
+
+  h <- ggplot(cor_df, aes(x=correlation)) +
+    geom_histogram(bins = 30, color = "black", fill = "white") +
+    xlab("Correlation") +
+    ylab("Frequency") +
+    ggtitle("Histogram of Correlation Values")
+  show(h)
+
+  #hist(cor_vec, breaks = 100)
+
+  ## MSE
+  MSE_vec <- object$MSE_vec
+  print(mean(MSE_vec))
+  print(sd(MSE_vec))
+  # Histogram MSE
+  MSE_df <- data.frame(MSE = MSE_vec)
+
+  h <- ggplot(MSE_df, aes(x=MSE)) +
+    geom_histogram(bins = 30, color = "black", fill = "white") +
+    xlab("MSE") +
+    ylab("Frequency") +
+    ggtitle("Histogram of MSE Values")
+  show(h)
+
+  ## Most prevalent Features
+  # Order the features based on their selection frequency
+  coef_matrix <- lasso_k_ob$coef_matrix
+  frequency <- data.frame(Feature = colnames(coef_matrix), Frequency = colSums(coef_matrix != 0) / (n_models))
+  frequency <- frequency[order(frequency$Frequency, decreasing = TRUE),]
+
+  # Bar plot of the selection frequency of the features
+  n_best <- 50
+  h <- ggplot(frequency[1:n_best ,], aes(x = Frequency, y = reorder(Feature, Frequency))) +
+    geom_bar(stat = "identity") +
+    xlab("Selection Frequency") +
+    ylab("Features") +
+    ggtitle("Selection Frequency of Features") +
+    theme(axis.text.y = element_text(angle = 0, hjust = 0))
+  show(h)
+
+  # extract the top features
+  perc_best <- 0.9 # how often they where selected in percentage
+  top_features_with_index = which(colSums(coef_matrix != 0) >= perc_best * n_models)
+  top_feature_names = colnames(coef_matrix)[top_features_with_index]
+  print(top_feature_names)
+
+  num_features_to_keep <- 10 
+  # count the frequency of each feature in coef_matrix
+  counts <- colSums(coef_matrix != 0)
+  # sort the features based on their frequency
+  sorted_features <- names(sort(counts, decreasing = TRUE))
+  print(sorted_features[1:num_features_to_keep])
+}
+```
+
+```{r}
+path <- "/Users/anders/Documents/MASTER/Cancer/model_instances/lk_AllGenesProlif.RData"
+load(path)
+
+report02_out(lasso_k_ob)
 ```

### 2023-01-30 R_codeP01/reports/test01.Rmd
worked on report

--- 2023-01-27 R_codeP01/reports/MS2_report02.Rmd
@@
 
-<!-- ```{r echo=FALSE}  -->
-<!-- knitr::opts_chunk$set(echo=FALSE)  -->
-<!-- ``` -->
-
 ```{r global-options, include=FALSE}
@@
 ```
-# Data
-Two clinical trails on breast cancer (advanced HR+/HER2- and HER2-E breast cancer) using two different drug combination
-## Trail 1
-Two treatments which differ with respect to drug combination 
-- Target: ribociclib and endocrine therapy (letrozole)
-- Chemotherapy: doxorubicin, cyclophosphamide and paclitaxel. 
-approx. 50 patients in each group.
-Endpoints: proliferation score, ROR score
 
-## Trail 2
-The primary objective of this study is to compare two cdk4/6 targeted drugs (Palbociclib, n=36; Abemaciclib, n=3 in combination with endocrine therapy (tamoxifen, fulvestrant or aromatase inhibitors,  I think?)
+```{r}
+report02_out <- function(object){
 
-Endpoints: progression free survival (months), OS?, and status of the two former (dont know what that means)
+  fr <- sum(is.na(object$correlations))/length(object$correlations)
+  cat("Fraction of model fits with no selected genes:", fr, "\n")
+  cat("Correlations mean: ", mean(na.omit(lasso_k_ob$correlations)))
 
-# Major goal
-1. Find best model to predict outcome of cancer treatment with genetic profile as predictive features
-2. Features selection in order to understand cancer biology
+  # Histogram correlations
+  correlations_finite <- lasso_k_ob$correlations[is.finite(lasso_k_ob$correlations)]
+  cor_df <- data.frame(correlation = correlations_finite)
 
-# Major challanges
-Preliminary experiments (on trail 1) showed instability in prediction and feature selection between bootstrap samples og Lasso. I believe this is a classical problem of high-dim data?
-
-# Approch
-Test all thinkable models to see if some is surperior
-
-# Evaluation of models
-Two levels of evaluation is scheduled:
-
-## 1. Comparison of models
-1000 bootstrap models are fitted and then evaluated on the original sample.
-This gives a relative comparison of the various models with respect to data similar to the given data set.
-In addition to Correlation and MSE, frequency of selected features is compared.
-
-## 2. Expected outcome of future patients
-3 strategies are considered:  
-1. Repeated cross-validations (100 rep) \
-2. Bootstrap models with 0.632 (or 0.632?) adjustment \
-3. Test data set from a second trail (This trail have different responses) \
-
-# Models
-## Lasso
-## Post Lasso
-## Ridge
-## Elastic Net
-## Boosting with stumps as base learner
-### - mboost
-### - xgboost
-## Feature selecting ensemble model
-
-# RESULTS
-
-# Lasso
-```{r include=TRUE}
-load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/lb_object_AllGenes01.RData")
-
-# Correlation
-cor_vec <- as.numeric(lb_object[[1]])
-sum(is.na(cor_vec))/length(cor_vec)    # fraction of NA
-mean(cor_vec, na.rm=TRUE)
-median(cor_vec, na.rm=TRUE)
-var(cor_vec, na.rm=TRUE)
-# par(mfrow=c(1,1))
-hist(cor_vec, breaks = 100)
-
+  ggplot(cor_df, aes(x=correlation)) +
+    geom_histogram(bins = 30, color = "black", fill = "white") +
+    xlab("Correlation") +
+    ylab("Frequency") +
+    ggtitle("Histogram of Correlation Values")
+}
 ```
 
-# Post Lasso
-# Ridge
-# Elastic Net
-# Boosting with stumps as base learner
+```{r}
+path <- "/Users/anders/Documents/MASTER/Cancer/model_instances/lk_AllGenesProlif.RData"
+load(path)
+
+report02_out(lasso_k_ob)
+```

### 2023-01-30 R_codeP01/scripts/90_output01.R

@@ -1,0 +1,85 @@
+
+
+path <- "/Users/anders/Documents/MASTER/Cancer/model_instances/lk_AllGenesProlif.RData"
+
+report02_out <- function(){
+  load(path)  
+  cat(sum(is.na(lasso_k_ob$correlations))/length(lasso_k_ob$correlations))
+}
+  
+report02_out()
+
+## ANALYSIS
+sum(is.na(lasso_k_ob$correlations))/length(lasso_k_ob$correlations)    # fraction of NA
+
+## Correlations
+mean(na.omit(lasso_k_ob$correlations))
+mean(lasso_k_ob$correlations, na.rm=TRUE)
+median(lasso_k_ob$correlations, na.rm=TRUE)
+var(lasso_k_ob$correlations, na.rm=TRUE)
+sd(na.omit(lasso_k_ob$correlations))
+
+# Histogram
+correlations_finite <- lasso_k_ob$correlations[is.finite(lasso_k_ob$correlations)]
+cor_df <- data.frame(correlation = correlations_finite)
+
+ggplot(cor_df, aes(x=correlation)) +
+  geom_histogram(bins = 30, color = "black", fill = "white") +
+  xlab("Correlation") +
+  ylab("Frequency") +
+  ggtitle("Histogram of Correlation Values")
+
+## MSE
+mean(lasso_k_ob$MSE_vec)
+sd(lasso_k_ob$MSE_vec)
+# Histogram
+MSE_df <- data.frame(MSE = lasso_k_ob$MSE_vec)
+
+ggplot(MSE_df, aes(x=MSE)) +
+  geom_histogram(bins = 30, color = "black", fill = "white") +
+  xlab("MSE") +
+  ylab("Frequency") +
+  ggtitle("Histogram of MSE Values")
+
+
+## Most prevalent Features
+# Order the features based on their selection frequency
+frequency <- data.frame(Feature = colnames(lasso_k_ob$coef_matrix), Frequency = colSums(lasso_k_ob$coef_matrix != 0) / (repeats * folds))
+frequency <- frequency[order(frequency$Frequency, decreasing = TRUE),]
+frequency[1:5, 1:2]
+
+# Bar plot of the selection frequency of the features
+n_best <- 50
+ggplot(frequency[1:n_best ,], aes(x = Frequency, y = reorder(Feature, Frequency))) +
+  geom_bar(stat = "identity") +
+  xlab("Selection Frequency") +
+  ylab("Features") +
[…]

### 2023-01-30 R_codeP01/reports/MS2_report02.Rmd
Worked on report

--- 2023-01-27 R_codeP01/reports/MS2_report02.Rmd
@@
 
-```{r global-options, include=FALSE}
-knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='Figs/',
-                      echo=FALSE, warning=FALSE, message=FALSE)
-```
 # Data
-Two clinical trails on breast cancer (advanced HR+/HER2- and HER2-E breast cancer) using two different drug combination
-## Trail 1
+One clinical trails on breast cancer (advanced HR+/HER2- and HER2-E breast cancer) using two different drug combination; and a cohorts study (here used as test data set). /
+Both data set have 771 genes. This genes are specifically selected based likely potential role in breast cancer. /
+The gene set is dived into X numbers of "signature genes"; which are thought to represent unities with respect to cancer biology...
+
+## Trail
 Two treatments which differ with respect to drug combination 
@@
 # RESULTS
+```{r global-options, include=FALSE}
+knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='Figs/',
+                      echo=FALSE, warning=FALSE, message=FALSE)
+```
+
+```{r}
+source("/Users/anders/Documents/Master/Cancer/R_codeP01/scripts/90_output01.R")
+```
 
 # Lasso
-```{r include=TRUE}
-load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/lb_object_AllGenes01.RData")
+```{r}
+path <- "/Users/anders/Documents/MASTER/Cancer/model_instances/lk_AllGenesProlif.RData"
+load(path)
 
-# Correlation
-cor_vec <- as.numeric(lb_object[[1]])
-sum(is.na(cor_vec))/length(cor_vec)    # fraction of NA
-mean(cor_vec, na.rm=TRUE)
-median(cor_vec, na.rm=TRUE)
-var(cor_vec, na.rm=TRUE)
-# par(mfrow=c(1,1))
-hist(cor_vec, breaks = 100)
-
+results_lasso <- report02_out(lasso_k_ob)
 ```
 
-# Post Lasso
 # Ridge
@@
 # Boosting with stumps as base learner
+
+# Post Lasso

### 2023-01-30 R_codeP01/scripts/08_boosting02.R

@@ -1,13 +1,13 @@
-#################################################################
-##  Bootstrap  Boosting - using original sample as test set ##
-#################################################################
+######################################################################
+##  mBoost on bootstrap samples - using original sample as test set ##
+######################################################################
 
 ## Boosting using bootstrap sample to train 1000 models
-## Baselearner:
+## Base learners:
 ## - linear
 ## - spline
 ## - btree
-## Cross-validation (5-fold) used for training/tuning lambda and selecting features
+## 
 ## Test against original data sample
 ## output: proliferation.score correlation; SEM; Coefficient of genes
 

### 2023-01-30 R_codeP01/scripts/08_boosting03.R

@@ -1,5 +1,5 @@
 #################################################################
-##  Bootstrap  Boosting - using original sample as test set ##
+##  XGBoost on Bootstrap samples - using original sample as test set ##
 #################################################################
 
 ## Boosting using bootstrap sample to train 1000 models
@@ -7,7 +7,7 @@
 ## - linear
 ## - spline
 ## - btree
-## Cross-validation (5-fold) used for training/tuning lambda and selecting features
+## 
 ## Test against original data sample
 ## output: proliferation.score correlation; SEM; Coefficient of genes
 

### 2023-01-30 R_codeP01/scripts/90_output01.R

@@ -1,85 +1,101 @@
+#################################
+## create outputs for report 2 ##
+#################################
 
+library(ggplot2)
 
-path <- "/Users/anders/Documents/MASTER/Cancer/model_instances/lk_AllGenesProlif.RData"
-
-report02_out <- function(){
-  load(path)  
-  cat(sum(is.na(lasso_k_ob$correlations))/length(lasso_k_ob$correlations))
-}
+report02_out <- function(object){
+  cor_vec <- object$correlations
+  n_models <- length(cor_vec)
+  cat("number of models fitted:", n_models, "\n")
+  fr <- sum(is.na(cor_vec))/n_models
+  cat("Fraction of model fits with no selected genes:", fr, "\n")
+  cat("\n")
   
-report02_out()
+  ## Correlations
+  cat("CORRELATIONS RESULTS", "\n")
+  cor_mean <- mean(na.omit(cor_vec))
+  cat("Mean:", cor_mean, "\n") 
+  cor_median <- median(cor_vec, na.rm=TRUE)
+  cat("Median:", cor_median, "\n")
+  cor_var <- var(cor_vec, na.rm=TRUE)
+  cat("Variance:", cor_var, "\n")
+  cor_sd <- sd(na.omit(cor_vec)) 
+  cat("st.dev.:", cor_sd)
+  
+  # Histogram correlations
+  correlations_finite <- cor_vec[is.finite(cor_vec)]
+  cor_df <- data.frame(correlation = correlations_finite)
+  
+  h <- ggplot(cor_df, aes(x=correlation)) +
+    geom_histogram(bins = 30, color = "black", fill = "white") +
+    xlab("Correlation") +
+    ylab("Frequency") +
+    ggtitle("Histogram of Correlation Values")
+  show(h)
 
-## ANALYSIS
-sum(is.na(lasso_k_ob$correlations))/length(lasso_k_ob$correlations)    # fraction of NA
-
-## Correlations
-mean(na.omit(lasso_k_ob$correlations))
-mean(lasso_k_ob$correlations, na.rm=TRUE)
-median(lasso_k_ob$correlations, na.rm=TRUE)
-var(lasso_k_ob$correlations, na.rm=TRUE)
-sd(na.omit(lasso_k_ob$correlations))
-
-# Histogram
-correlations_finite <- lasso_k_ob$correlations[is.finite(lasso_k_ob$correlations)]
-cor_df <- data.frame(correlation = correlations_finite)
-
-ggplot(cor_df, aes(x=correlation)) +
[…]

### 2023-01-31 R_codeP01/scripts/08_boosting03.R
adapted output of lasso bootstrap

@@ -14,7 +14,7 @@
 library(xgboost)
 library(Matrix)
 
-# linear base learner
+# structure of base learners
 fm01 <- Y ~ CCND1 + CCNE1 + CDKN1A + ESR1 + MYC + RB1
 fm05 <- as.formula(paste("Y", paste(genes, collapse="+"), sep=" ~ "))
 

### 2023-01-31 R_codeP01/scripts/test02.R

@@ -1,17 +1,0 @@
-
-
-
-# Order the features based on their selection frequency
-frequency <- data.frame(Feature = colnames(lasso_k_ob$coef_matrix), Frequency = colSums(lasso_k_ob$coef_matrix != 0) / (repeats * folds))
-frequency <- frequency[order(frequency$Frequency, decreasing = TRUE),]
-frequency[1:3, 1:2]
-
-
-# Create a bar plot of the selection frequency of the features
-ggplot(frequency[1:50,], aes(x = Frequency, y = reorder(Feature, Frequency))) +
-  geom_bar(stat = "identity") +
-  xlab("Selection Frequency") +
-  ylab("Features") +
-  ggtitle("Selection Frequency of Features") +
-  theme(axis.text.y = element_text(angle = 0, hjust = 0))
-

### 2023-02-01 R_codeP01/reports/MS2_report02.Rmd
xgboost w/rep.cv; residuals w/lasso

@@
 <!-- ``` -->
+```{r global-options, include=FALSE}
+knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='Figs/',
+                      echo=FALSE, warning=FALSE, message=FALSE)
+```
+
+```{r}
+# lb_obj_6_prolif.RData
+# lb_obj_771_prolif.RData
+# lb_obj_771_residuals_prolif.RData
+# lb_obj_nodes_prolif.RData
+
+# lb_obj_771_ROR.RData
+#
+# lk_obj_771_prolif.RData
+#
+# bb_obj_6_prolif.RData
+# 
+#
+```
 
@@
 One clinical trails on breast cancer (advanced HR+/HER2- and HER2-E breast cancer) using two different drug combination; and a cohorts study (here used as test data set). /
-Both data set have 771 genes. This genes are specifically selected based likely potential role in breast cancer. /
-The gene set is dived into X numbers of "signature genes"; which are thought to represent unities with respect to cancer biology...
+Both data set have mRNA expression of 771 genes at baseline (prior to treatment). This genes are specifically selected based on their potential roles in breast cancer pathology: /
+The gene set is dived into X numbers of "signature genes"; which are thought to represent functional unities with respect to cancer biology...overview of signatures..
+
+Additionally, both data-set contians clinical data as...
+(how to model in...)
+
+## Respones used
+### Proliferation score
+### Risk of relapse score (ROR)
+### ...
 
@@
 approx. 50 patients in each group.
-Endpoints: proliferation score, ROR score
+Endpoints: proliferation score, ROR score, combined ROR and prolif
 
@@
 # Approch
-Test all thinkable models to see if some is surperior
+Test all thinkable models to see if some is superior
 
@@
 1000 bootstrap models are fitted and then evaluated on the original sample.
-This gives a relative comparison of the various models with respect to data similar to the given data set.
+This gives a relative comparison of the various models with respect to data very similar to the given data set.
 In addition to Correlation and MSE, frequency of selected features is compared.
@@
 3 strategies are considered:  
-1. Repeated cross-validations (100 rep) \
-2. Bootstrap models with 0.632 (or 0.632?) adjustment \
-3. Test data set from a second trail (This trail have different responses) \
+1. Repeated cross-validations (200 rep, 5-fold) \
+2. Bootstrap models with 0.632 (or 0.632?) adjustment (Not done) \
+3. Use the cohort as test data-set (Challenge: This trail have different responses) \
 
@@
 ## Post Lasso
+## Residuals
 ## Ridge
@@
 # RESULTS
-```{r global-options, include=FALSE}
-knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='Figs/',
-                      echo=FALSE, warning=FALSE, message=FALSE)
-```
-
 ```{r}
@@
 # Lasso
+
+## Bootstrap
+### 6 genes -> proliferation score
 ```{r}
-path <- "/Users/anders/Documents/MASTER/Cancer/model_instances/lk_AllGenesProlif.RData"
-load(path)
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_6_prolif.RData")
+l_b_6_p <- report02_out(lb_obj_6_prolif)
+```
+### 6 genes -> ROR_proliferation score
+```{r}
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_6_RORprolif.RData")
+l_b_6_ROR_p <- report02_out(lb_obj_6_RORprolif)
+```
 
-results_lasso <- report02_out(lasso_k_ob)
+### 771 genes -> proliferation score
+```{r}
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_771_prolif.RData")
+l_b_771_p <- report02_out(lb_obj_771_prolif)
+```
+### 771 genes -> ROR-proliferation score
+```{r}
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_771_RORprolif.RData")
+l_b_771_ROR_p <- report02_out(lb_obj_771_RORprolif)
+```
+
+### node values -> proliferation score
+```{r}
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_nodes_prolif.RData")
+l_b_nodes_p <- report02_out(lb_obj_nodes_prolif)
+```
+### node values -> ROR-proliferation score
+```{r}
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_nodes_RORprolif.RData")
+l_b_nodes_ROR_p <- report02_out(lb_obj_nodes_RORprolif)
+```
+
+### Mechnaistic + Residuals -> proliferation score
+```{r}
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_residuals771_prolif.RData")
+l_b_residuals771_p <- report02_out(lb_obj_residuals771_prolif)
+```
+### Mechnaistic + Residuals -> ROR-proliferation score
+```{r}
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_residuals_RORprolif.RData")
+l_b_residuals_ROR_p <- report02_out(lb_obj_residuals_RORprolif)
+```
+
+## Repeated cross-validation
+### 6 genes -> proliferation score
+```{r}
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lc_obj_6_prolif.RData")
+l_c_6_p <- report02_out(lc_obj_6_prolif)
+```
+### 6 genes -> ROR_proliferation score
+```{r}
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lc_obj_6_RORprolif.RData")
+l_c_6_ROR_p <- report02_out(lc_obj_6_RORprolif)
+```
+
+### 771 genes -> proliferation score
+```{r}
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lc_obj_771_prolif.RData")
+l_c_771_p <- report02_out(lc_obj_771_prolif)
+```
+### 771 genes -> ROR-proliferation score
+```{r}
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lc_obj_771_RORprolif.RData")
+l_c_771_ROR_p <- report02_out(lc_obj_771_RORprolif)
+```
+
+### node values -> proliferation score
+```{r}
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lc_obj_nodes_prolif.RData")
+l_c_nodes_p <- report02_out(lc_obj_nodes_prolif)
+```
+### node values -> ROR-proliferation score
+```{r}
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lc_obj_nodes_RORprolif.RData")
+l_c_nodes_ROR_p <- report02_out(lc_obj_nodes_RORprolif)
 ```

### 2023-02-01 R_codeP01/scripts/01_dataclean01.R

@@ -25,7 +25,6 @@ df02 = full_join(df_nodes, df01, by = c(colnames(df01)[1]))
 ## ALL data with added prediction of the Mechanistic model ##
 #############################################################
 
-
 ############################################################
 ## ALL data with added residuals of the Mechanistic model ##
 ############################################################
@@ -43,6 +42,7 @@ df03 <- read_excel(path) |>
 #############
 
 df_6genes_with_output <- function(output){
+  print(output)
   df_genes <- df01 |> select(UniqueID, CCND1, CCNE1, CDKN1A, ESR1, MYC, RB1, timepoint, TrialArmNeo) |>
     filter(timepoint=="SCR") |> 
     filter(TrialArmNeo=="Letro+Ribo")
@@ -55,62 +55,40 @@ df_6genes_with_output <- function(output){
   
   #rename(df_6genes, c("Y") = c(output))
   colnames(df_6genes)[which(names(df_6genes) == output)] <- "Y"
-  print(output)
+  
   df_6genes <- df_6genes |> select(-c(UniqueID, timepoint.x, TrialArmNeo.x, timepoint.y, TrialArmNeo.y))
-  df_6genes <- na.omit(df_6genes)
+  df_6genes <- na.omit(df_6genes) # remove rows with NA
   return(df_6genes)
 }
 
-Proliferation_6genes <- df_6genes_with_output("ProliferationScore")
+prolif_6genes <- df_6genes_with_output("ProliferationScore")
+RORprolif_6genes <- df_6genes_with_output("ROR_P_Subtype_Proliferation")
 
-# Matrices for lasso and XGboost
-X <- as.matrix(Proliferation_6genes |> 
-                 select(CCND1, CCNE1, CDKN1A, ESR1, MYC, RB1))
+
+# Matrices for lasso and XGboost (not needed anymore/done in functions)
+X <- as.matrix(Proliferation_6genes |> select(CCND1, CCNE1, CDKN1A, ESR1, MYC, RB1))
 Y <- as.matrix(select(Proliferation_6genes, Y))
-
-#################
-## NODES DATA  ##
-#################
-
-df_Nodes_with_output <- function(output){
-  df_features <- df02 |>
[…]

### 2023-02-01 R_codeP01/scripts/04_lasso02-a.R

@@ -66,10 +66,7 @@ lasso_cor_boot = function(X, Y, ext.X, ext.Y, n_bootstraps=100){
   #return(list(cor_vec, inds_vec))
 }
 
-# making list object with 
-# 1. correlation  
-# 2. integer values of features selected in each bootstrap model
-# 3. SEM
+
 set.seed(123)
 lb_object <- lasso_cor_boot(X_Z, Y, ext.X_Z, ext.Y = ext.PFS_months, 100)
 

### 2023-02-01 R_codeP01/scripts/04_lasso02-b.R

@@ -1,54 +1,15 @@
-## Repeated cross-validation for testing the Lasso model
-##
-## Test against the fold
+###########################################################
+##  Bootstrap Lasso - using original sample as test set ##
+###########################################################
+
 ## Cross-validation (5-fold) used for training/tuning lambda and selecting features
-## output: selected genes; proliferation.score correlation; SEM
+## output: selected genes; correlation; SEM
 
 ## Post Lasso model is made at the bottom
 
 library(glmnet)
 library(caret)
 library(ggplot2)
-
-###########################################################
-##  Repeated cross validation ##
-###########################################################
-
-# Custom function for repeated k-fold cross validation
-repeated_kfold_cv <- function(df_data, func=lasso_sample, folds=5, repeats=200, method="pearson") {
-  n_models <- repeats * folds
-  print(n_models)
-  cor_vec <- rep(NA, n_models)
-  MSE_vec <- rep(NA, n_models)
-  coef_matrix <- matrix(NA, nrow = n_models, ncol = ncol(df_data[,-1]))
-  colnames(coef_matrix) <- colnames(df_data[, -1])
-  coef_matrix_row_index <- 1
-  
-  # Repeat the cross-validation process
-  for (i in 1:repeats) {
-    # Create the folds for evaluating the performance
-    kf <- caret::createFolds(df_data[,1], k = folds, list = TRUE, returnTrain = TRUE)
-    # Loop through the folds
-    for (j in 1:folds) {
-      # Get the training and testing data
-      train_data <- df_data[kf[[j]],]
-      test_data <- df_data[-kf[[j]],]
-      
-      # Fit the function on the training data and get results
-      fit <- func(train_data)
-      
-      coef_matrix[coef_matrix_row_index, ] <- coef(fit, s = "lambda.min")[-1]
-      
-      pred = predict(fit, newx = as.matrix(test_data)[,-1], type = "response", s = "lambda.min")  
[…]

### 2023-02-01 R_codeP01/scripts/07_residuals01-a.R

@@ -54,7 +54,7 @@ ob_ <- lasso_bootstrap_residuals(X, Y, pred_mech, TRUE)
 cbind(ob_[[4]], pred_mech, Y)
 
 # 1000 bootstrap fits
-lasso_boot = function(X, Y, pred_mech, n_bootstraps=1000){
+lasso_boot_residuals = function(X, Y, pred_mech, n_bootstraps=1000){
   # run many bootstraps
   # output: - vector with correlations 
   #         - vector with selected features as integers values wrt to X

### 2023-02-01 R_codeP01/scripts/07_residuals01-b.R

@@ -1,57 +1,15 @@
 ###########################################################
-## Repeated cross-validation for testing the Lasso model ##
+## Residual + Mech model by bootstrap samples - using original sample as test set ##
 ###########################################################
-##
-## Test against the fold
+
 ## Cross-validation (5-fold) used for training/tuning lambda and selecting features
-## output: selected genes; proliferation.score correlation; SEM
+## output: selected genes; correlation; SEM
 
 ## Post Lasso model is made at the bottom
 
 library(glmnet)
 library(caret)
 library(ggplot2)
-
-###########################################################
-##  Repeated cross validation ##
-###########################################################
-
-# Function: repeated k-fold cross validation
-lasso_rep_cv <- function(df_data, func=lasso_sample, folds=5, repeats=200, method="pearson") {
-  n_models <- repeats * folds
-  print(n_models)
-  cor_vec <- rep(NA, n_models)
-  MSE_vec <- rep(NA, n_models)
-  coef_matrix <- matrix(NA, nrow = n_models, ncol = ncol(df_data[,-1]))
-  colnames(coef_matrix) <- colnames(df_data[, -1])
-  
-  coef_matrix_row_index <- 1
-  
-  # Repeat the cross-validation process
-  for (i in 1:repeats) {
-    # Create the folds for evaluating the performance
-    kf <- caret::createFolds(df_data[,1], k = folds, list = TRUE, returnTrain = TRUE)
-    # Loop through the folds
-    for (j in 1:folds) {
-      # Get the training and testing data
-      train_data <- df_data[kf[[j]],]
-      test_data <- df_data[-kf[[j]],]
-      
-      # Fit the function on the training data and get results
-      fit <- func(train_data)
-      
-      coef_matrix[coef_matrix_row_index, ] <- coef(fit, s = "lambda.min")[-1]
-      
[…]

### 2023-02-01 R_codeP01/scripts/09_xgboost02-b.R

@@ -1,0 +1,238 @@
+#################################################################
+##  XGBoost on Bootstrap samples - using original sample as test set ##
+#################################################################
+
+## Boosting using bootstrap sample to train 1000 models
+## Baselearner:
+## - linear
+## - spline
+## - btree
+## 
+## Test against original data sample
+## output: proliferation.score correlation; SEM; Coefficient of genes
+
+library(xgboost)
+library(Matrix)
+
+# structure of base learners
+fm01 <- Y ~ CCND1 + CCNE1 + CDKN1A + ESR1 + MYC + RB1
+fm05 <- as.formula(paste("Y", paste(genes, collapse="+"), sep=" ~ "))
+
+XGBoost_sample <- function(fm, df_train) {
+  # Convert the dataMatrix to a DMatrix object
+  train_sparse = sparse.model.matrix(object = fm, data = df_train)
+  dtrain = xgb.DMatrix(data = train_sparse, label = df_train$Y)
+
+  # param <- list(eta = 0.1, max_depth = 5)
+   param <- list(booster = "gbtree", 
+                objective = "reg:squarederror", 
+                eval_metric = "rmse", 
+                # nthread = 4, 
+                max_depth = 1, 
+                min_child_weight = 1,
+                tree_method = "hist",   # tree_methods=  exact, approx and hist, depending on the dataset size, memory and time constraints
+                #eta_decay=0.1,
+                eta=0.3)
+ 
+  cv <- xgb.cv(data = dtrain, 
+               params = param, 
+               nrounds = 100, 
+               nfold = 5, 
+               #showsd = T, stratified = T,
+               print_every_n = 10,
+               early_stopping_rounds = 5,
+               verbose = FALSE)
+  
+  n_rounds <- cv$best_iteration
+  
+  xgb_model = xgb.train(data = dtrain,
+                        # The following is needed if to monitor training and validation error
+                        # watchlist = list(train = dtrain, val = dvalidation),
+                        params = param,
+                        nrounds = n_rounds,
+                        verbose = FALSE)
+  
+  return(xgb_model)
[…]

### 2023-02-01 R_codeP01/scripts/09_xgboost03.R

@@ -1,30 +1,35 @@
 #################################################################
-##  XGBoost on Bootstrap samples - using original sample as test set ##
+##  XGBoost on Repeated cross-validation ##
 #################################################################
 
-## Boosting using bootstrap sample to train 1000 models
-## Baselearner:
-## - linear
-## - spline
+## Boosting using 5-fold cross validation to evaluate model
+## Base learners:
 ## - btree
+## - (linear)
+## - (spline)
 ## 
-## Test against original data sample
-## output: proliferation.score correlation; SEM; Coefficient of genes
+## Test against folds
+## output: - vector with correlations 
+##         - matrix with features
+##         - vector with SEM
+##         - (vector with number of rounds used in each model)
 
 library(xgboost)
 library(Matrix)
+library(data.table)
+library(caret)
+library(ggplot2)
 
 # structure of base learners
 fm01 <- Y ~ CCND1 + CCNE1 + CDKN1A + ESR1 + MYC + RB1
 fm05 <- as.formula(paste("Y", paste(genes, collapse="+"), sep=" ~ "))
 
 XGBoost_sample <- function(fm, df_train) {
-  # Convert the dataMatrix to a DMatrix object
-  train_sparse = sparse.model.matrix(object = fm01, data = df_train)
+  # Convert dataframe to dataMatrix to DMatrix object
+  train_sparse = sparse.model.matrix(object = fm, data = df_train)
   dtrain = xgb.DMatrix(data = train_sparse, label = df_train$Y)
 
   # param <- list(eta = 0.1, max_depth = 5)
- 
    param <- list(booster = "gbtree", 
                 objective = "reg:squarederror", 
                 eval_metric = "rmse", 
@@ -48,71 +53,136 @@ XGBoost_sample <- function(fm, df_train) {
   
   xgb_model = xgb.train(data = dtrain,
                         # The following is needed if to monitor training and validation error
-                        # watchlist = list(train = dtrain, 
-                        #                  val = dvalidation),
[…]

### 2023-02-01 R_codeP01/scripts/90_output01.R

@@ -5,7 +5,7 @@
 library(ggplot2)
 
 report02_out <- function(object){
-  cor_vec <- object$correlations
+  cor_vec <- object$cor_vec
   n_models <- length(cor_vec)
   cat("number of models fitted:", n_models, "\n")
   fr <- sum(is.na(cor_vec))/n_models
@@ -36,8 +36,8 @@ report02_out <- function(object){
 
   
   ## MSE
-  MSE_vec <- object$MSE_vec
   cat("MSE RESULTS", "\n")
+  MSE_vec <- object$MSE_vec
   MSE_mean <- mean(na.omit(MSE_vec))
   cat("Mean:", MSE_mean, "\n") 
   MSE_median <- median(MSE_vec, na.rm=TRUE)
@@ -79,7 +79,7 @@ report02_out <- function(object){
   top_features_with_index = which(colSums(coef_matrix != 0) >= perc_best * n_models)
   top_feature_names = colnames(coef_matrix)[top_features_with_index]
   cat("\n")
-  cat("Genes selected 50% or more times:", "\n")
+  cat("Features selected 50% or more times:", "\n")
   cat(top_feature_names, "\n")
   
   num_features_to_keep <- 20 
@@ -88,7 +88,7 @@ report02_out <- function(object){
   # sort the features based on their frequency
   sorted_features <- names(sort(counts, decreasing = TRUE))
   cat("Top 20 featrues:", "\n")
-  cat(sorted_features[1:num_features_to_keep])
+  print(sorted_features[1:num_features_to_keep])
   out <- list(cor_mean=cor_mean,
               cor_median=cor_median,
               cor_var=cor_var,

### 2023-02-02 R_codeP01/scripts/01_dataclean01.R
worked on residuals and xgboost

@@ -1,4 +1,16 @@
-# importing and creating various dataframes and matrices
+############################################################
+## importing and creating various dataframes and matrices ##
+############################################################
+
+# REMEMBER: Standardizing features can be relevant
+# it is extremely important that all PREDICTOR variables are on the same scale. 
+# These regularization methods are sensitive to the size of coefficients by design, 
+# so coefficients on different scales are enormously problematic. 
+# Based on how these data were simulated, we know that our predictors are already on the same scale, 
+# but as good practice, we will center and scale them anyways.
+# Use scale()
+pred <- scale(pred)
+X_Z <- scale(X)
 
 library(tidyverse)
 library(readxl)
@@ -6,14 +18,12 @@ library(readxl)
 ##############################################
 ## ALL DATA as they came original (I think) ##
 ##############################################
-
 path <- "/Users/anders/Documents/MASTER/data/CORALLEEN_02.csv"
 df01 <- read.table(path, header = TRUE, sep = ",", dec = ".")
 
 ##########################################################
 ## ALL DATA with added NODE DATA from MECHANISTIC MODEL ##
 ##########################################################
-
 # Adding node values to all data
 path <- "/Users/anders/Documents/MASTER/data/model_predictors.tsv"
 df_nodes <- read.delim(path)
@@ -24,6 +34,10 @@ df02 = full_join(df_nodes, df01, by = c(colnames(df01)[1]))
 #############################################################
 ## ALL data with added prediction of the Mechanistic model ##
 #############################################################
+path <- "/Users/anders/Documents/Master/data/COR_and_validation_data_with_model_prediction/CORALLEEN_data_with_model_prediction.xlsx"
+# df_03 <- read_excel(path, range = cell_cols("A:V"))
+df03 <- read_excel(path) |> 
+  rename(TrialArmNeo = "Trial Arm Neo")
 
 ############################################################
 ## ALL data with added residuals of the Mechanistic model ##
[…]

### 2023-02-02 R_codeP01/scripts/03_linear_regression01.R

@@ -1,5 +1,10 @@
-## Here bootstrap is the prime focus
-## Predictors: 6 genes, node values, 
+###################################
+## Ordinary linear model
+## AIC
+## Bootstrap
+###################################
+##
+## Predictors: genes (various structures), node values
 ## Output: correlations
 
 ## FORMULAS ##
@@ -62,6 +67,7 @@ abline(lm(df02_LR$sur_ProliferationScore ~ pred03))
 ###############################################################
 # bootstrap sample for train and original sample for testing ##
 ###############################################################
+
 regression_bootstrap <- function(df, formula){
   N = nrow(df)
   

### 2023-02-02 R_codeP01/scripts/03_linear_regression02.R

@@ -1,8 +1,9 @@
-## Linear regression with the 6 genes used in he mechanistic model is tested
+###############################################################################
+## Linear regression with the 6 genes used in he mechanistic model is tested ##
 ## Interaction is tested for the gene products which are known to interact
 
 # Bootstrap and Repeated Cross-validation is used to evaluate performance
-## Output: mean MSE; 95% confidence interval; histogram/plot
+## Output: MSE; 95% confidence interval; histogram/plot; correlations
 
 ##########################################################################
 
@@ -26,20 +27,22 @@ fm03 <- Y ~ CDKN1A + ESR1 + MYC + ESR1:MYC + CDKN1A:MYC
 fm04 <- Y ~ cyclinD1 + cyclinD1Palbo + p21 + cyclinD1p21 + cMyc + cyclinEp21 + Rb1 + ppRb1
 
 
-# Function to fit linear regression model and calculate MSE on all the data
+# Function to fit linear regression model and calculate MSE or correlation on all the data
 linear_regression_mse <- function(data, indices, formula) {
   d <- data[indices,]  # allows boot to select sample
   fit <- lm(formula, data = d)
   y_predict <- predict(fit, newdata = data)
   mse <- mean((data$Y - y_predict)^2)
-  return(mse)
+  cor <- cor(data$Y, y_predict)
+  #return(mse)
+  return(cor)
 }
 
 # Make the results reproducible
-set.seed(1234)
+set.seed(123)
 # Perform bootstrap with 1000 iterations
 b <- boot(data=data_in, statistic=linear_regression_mse, R = 1000, formula=fm01)
-b <- boot(data=data_in, statistic=linear_regression_mse, R = 1000, formula=fm02)
+b <- boot(data=prolif_6genes, statistic=linear_regression_mse, R = 1000, formula=fm02)
 b <- boot(data=data_in, statistic=linear_regression_mse, R = 1000, formula=fm03)
 
 b <- boot(data=Nodes_Proliferation, statistic=linear_regression_mse, R = 1000, formula=fm04)

### 2023-02-02 R_codeP01/scripts/04_lasso01.R

@@ -1,12 +1,11 @@
+############################################################################
 ## Various testing of lasso on 6 genes and nodes (depending on input dataframe)
 # 1. simple lasso with glmnet
 # 2. cross-validation to select features
 # 3. LOO-cross validation to tests model
 # 4. LOO-cross + 5-fold cross validation to test model
 ##############################################################################
-
 library(glmnet)
-
 
 # standard lasso
 lasso01 <- glmnet(X, Y)
@@ -25,7 +24,6 @@ show(variables)
 
 # Using LOO cross-validation for testing 
 # going through all observations with LOO as test set,
-
 lasso_loo <- function(X, Y, lambda.min=TRUE){
   pred_values <- NULL
   for(i in 1:nrow(X)){

### 2023-02-02 R_codeP01/scripts/07_residual_xgboost_rc03.R

@@ -1,0 +1,321 @@
+#################################################################
+##  XGBoost on Repeated cross-validation ##
+#################################################################
+
+## Boosting using 5-fold cross validation to evaluate model
+## Base learners:
+## - btree
+## - (linear)
+## - (spline)
+## 
+## Test against folds
+## output: - vector with correlations 
+##         - matrix with features
+##         - vector with SEM
+##         - (vector with number of rounds used in each model)
+
+library(xgboost)
+library(Matrix)
+library(data.table)
+library(caret)
+library(ggplot2)
+
+# structure of base learners
+fm01 <- Y ~ CCND1 + CCNE1 + CDKN1A + ESR1 + MYC + RB1
+fm05 <- as.formula(paste("Y", paste(genes, collapse="+"), sep=" ~ "))
+
+XGBoost_sample <- function(fm, df_train) {
+  # Convert dataframe to dataMatrix to DMatrix object
+  train_sparse = sparse.model.matrix(object = fm, data = df_train)
+  dtrain = xgb.DMatrix(data = train_sparse, label = df_train$Y)
+
+  # param <- list(eta = 0.1, max_depth = 5)
+   param <- list(booster = "gbtree", 
+                objective = "reg:squarederror", 
+                eval_metric = "rmse", 
+                # nthread = 4, 
+                max_depth = 1, 
+                min_child_weight = 1,
+                tree_method = "hist",   # tree_methods=  exact, approx and hist, depending on the dataset size, memory and time constraints
+                #eta_decay=0.1,
+                eta=0.3)
+ 
+  cv <- xgb.cv(data = dtrain, 
+               params = param, 
+               nrounds = 100, 
+               nfold = 5, 
+               #showsd = T, stratified = T,
+               print_every_n = 10,
+               early_stopping_rounds = 5,
+               verbose = FALSE)
+  
+  n_rounds <- cv$best_iteration
+  
+  xgb_model = xgb.train(data = dtrain,
+                        # The following is needed if to monitor training and validation error
[…]

### 2023-02-02 R_codeP01/scripts/07_residuals_lasso_boot01.R

@@ -48,8 +48,6 @@ lasso_res_boot <- function(df_train, df_test, pred_mech, additive=TRUE, func=las
     coef_matrix[i, ] <- coef(fit, s = "lambda.min")[-1]
 
     pred_res <- predict(fit, newx = as.matrix(df_test)[,-1], type = "response", s = "lambda.min") 
-    #pred <- pred_mech + pred_res
-    pred <- pred_mech * pred_res
     
     if (additive==TRUE){pred <- pred_mech + pred_res}
     else{pred <- pred_mech * pred_res}
@@ -62,11 +60,14 @@ lasso_res_boot <- function(df_train, df_test, pred_mech, additive=TRUE, func=las
   }
   return(list(cor_vec=cor_vec, coef_matrix=coef_matrix, MSE_vec=MSE_vec))
 }
-set.seed(123)
+
 t_ <- lasso_res_boot(prolif_6genes, prolif_6genes, pred_mech, additive=F, func=lasso_sample, method="pearson", n_bootstraps=10)
 mean(t_$cor_vec)
 sd(t_$cor_vec)
 
+# The predictions of the mechanistic model is scales by a linear model to be more similar to the proliferation scores
+# But the relationship between mechnistic prediction and proliferation score is not fully linear
+pred_mech <- df_771genes_mech_pred.scaled_prolif$model_prediction
 
 # RUN: lb_obj_residuals6_prolif
 set.seed(123)

### 2023-02-07 R_codeP01/scripts/30_ensemble_gs02.R
Problmes with ensemble model and rep-cross

@@ -12,6 +12,8 @@ signature_char <- function(words){
   return(character_matrix)
 }
 
+
+
 ## Immune Infiltration
 words <- c("CD8A	HLA.DRB1	PSMB10	CCL5	APOE	CD27	CD274	CD276	CHIT1	CLEC5A	CMKLR1	COLEC12	CXCL5	CXCL9	CXCR6	CYBB	GZMA	GZMB	GZMH	GZMM	HLA.E	IDO1	LAG3	MARCO	MSR1	NKG7	PDCD1	PDCD1LG2	SIGIRR	SPN	STAT1	TIGIT	ZNF205")
 char_immune_inf <- signature_char(words)
@@ -32,3 +34,4 @@ char_antigen_present <- signature_char(words)
 words <- c("ADCY9	ADD1	ANXA9	BORCS7	CDCA8	DDX39A	DNAJC12	EIF3B	ELOVL2	ESR1	HEMK1	IFT140	ITPR1	MAPT	NAT1	PFDN2	PGR	PTGER3	SCUBE2	SERBP1	SHMT2	SYTL4	TBC1D9	TCEAL1	TFF1	TLE3	WDR77")
 char_ER_signaling <- signature_char(words)
 
+split_words <- strsplit(words, "\t")

### 2023-02-07 R_codeP01/scripts/33_ensemble_stack_01.R

@@ -14,16 +14,78 @@ library(ggplot2)
 ##  Repeated cross validation ##
 ###########################################################
 
+
+
+
+t <- lasso_rep_cv(prolif_771genes, folds=2, repeats=2, method="pearson")
+
+# Function: repeated k-fold cross validation
+lasso_rep_cv <- function(df_data, folds=5, repeats=1, method="pearson") {
+  n_models <- repeats * folds
+  print(n_models)
+  cor_vec <- rep(NA, n_models)
+  MSE_vec <- rep(NA, n_models)
+  coef_matrix <- matrix(NA, nrow = n_models, ncol = ncol(df_data[,-1]))
+  #colnames(coef_matrix) <- colnames(df_data[, -1])
+  
+  count <- 1
+  # Repeat the cross-validation process
+  for (i in 1:repeats) {
+    # Create the folds for evaluating the performance
+    kf_1 <- caret::createFolds(df_data[,1], k = folds, list = TRUE, returnTrain = TRUE)
+    # Loop through the folds
+    for (j in 1:folds) {
+      # Get the training and testing data
+      train_data <- df_data[kf_1[[j]],]
+      test_data <- df_data[-kf_1[[j]],]
+
+      # Split into training and prediction set
+      ind <- sample.int(2, nrow(train_data), replace=TRUE, prob=c(0.8, 0.2))
+      train0 <- train_data[ind==1,]
+      pred0 <- train_data[ind==2,]
+      
+      # Partition feature space for lasso
+      X_prolif <- as.matrix(train0[c(char_prolif)])
+      X_immune_inf <- as.matrix(train0[c(char_immune_inf)])
+      X_ER_singaling <- as.matrix(train0[c(char_ER_signaling)])
+    
+      fit_prolif <- cv.glmnet(X_prolif, train0$Y, nfolds=5)
+      fit_immune_inf <- cv.glmnet(X_immune_inf, train0$Y, nfolds=5)
+      fit_ER_singaling <- cv.glmnet(X_ER_singaling, train0$Y, nfolds=5)
+      
+      pred_prolif = predict(fit_prolif, newx = as.matrix(pred0[c(char_prolif)]), type = "response", s = "lambda.min")
+      pred_immune = predict(fit_immune_inf, newx = as.matrix(pred0[c(char_immune_inf)]), type = "response", s = "lambda.min")
[…]

### 2023-02-08 R_codeP01/scripts/33_ensemble_stack_02.R
Ensemble script is running

@@ -1,0 +1,151 @@
+###################################################################
+## Repeated cross-validation for testing the Stacking - Ensemble models ##
+###################################################################
+##
+## Test against the fold
+## Cross-validation (5-fold) used for training/tuning lambda and selecting features
+## output: selected genes; proliferation.score correlation; SEM
+
+library(caret)
+library(glmnet)
+library(ggplot2)
+
+###########################################################
+##  Repeated cross validation ##
+###########################################################
+
+
+
+
+t <- lasso_rep_cv(prolif_771genes, folds=2, repeats=2, method="pearson")
+
+# Function: repeated k-fold cross validation
+lasso_rep_cv <- function(df_data, folds=5, repeats=1, method="pearson") {
+  n_models <- repeats * folds
+  print(n_models)
+  cor_vec <- rep(NA, n_models)
+  MSE_vec <- rep(NA, n_models)
+  coef_matrix <- matrix(NA, nrow = n_models, ncol = ncol(df_data[,-1]))
+  #colnames(coef_matrix) <- colnames(df_data[, -1])
+  
+  count <- 1
+  # Repeat the cross-validation process
+  for (i in 1:repeats) {
+    # Create the folds for evaluating the performance
+    kf_1 <- caret::createFolds(df_data[,1], k = folds, list = TRUE, returnTrain = TRUE)
+    # Loop through the folds
+    for (j in 1:folds) {
+      # Get the training and testing data
+      train_data <- df_data[kf_1[[j]],]
+      test_data <- df_data[-kf_1[[j]],]
+
+      # # Split into training and prediction set
+      # ind <- sample.int(2, nrow(train_data), replace=TRUE, prob=c(0.8, 0.2))
+      # train0 <- train_data[ind==1,]
+      # pred0 <- train_data[ind==2,]
+      
+      # Partition feature space for lasso
+      X_prolif <- as.matrix(train_data[c(char_prolif)])
+      X_immune_inf <- as.matrix(train_data[c(char_immune_inf)])
+      X_ER_singaling <- as.matrix(train_data[c(char_ER_signaling)])
+    
+      fit_prolif <- cv.glmnet(X_prolif, train_data$Y, nfolds=5)
+      fit_immune_inf <- cv.glmnet(X_immune_inf, train_data$Y, nfolds=5)
[…]

### 2023-02-08 R_codeP01/reports/MS2_report02.Rmd
worked on rapport

@@
 # Data
-One clinical trails on breast cancer (advanced HR+/HER2- and HER2-E breast cancer) using two different drug combination; and a cohorts study (here used as test data set). /
-Both data set have mRNA expression of 771 genes at baseline (prior to treatment). This genes are specifically selected based on their potential roles in breast cancer pathology: /
-The gene set is dived into X numbers of "signature genes"; which are thought to represent functional unities with respect to cancer biology...overview of signatures..
+One clinical trails on breast cancer (advanced HR+/HER2- and HER2-E breast cancer) using two different drug combination; and a cohorts study (here used as test data set).  
+Both data set have mRNA expression of 771 genes at baseline (prior to treatment). This genes are specifically selected based on their potential roles in breast cancer pathology:  
+The gene set is dived into 25 sets of "signature genes"; which are thought to represent functional unities with respect to cancer biology.
+Often signaling pathways.
+Furthermore, 8 immune cells are represented with specific genes.
+These sets are substantially smaller then the signature genes; which I presume leads to some issue in modeling (as for clinicla data - see next sentence).
 
-Additionally, both data-set contians clinical data as...
-(how to model in...)
+Additionally, both data-set contains clinical data; which up to now is not used in any models.
+If included they maybe should have a higher weight or be implemented differently from a sole gene.
+Maybe in a stacked ensemble model as signature.
 
@@
 ### Proliferation score
+A score based on expression level of some of the genes. Range: -1.1366 to 0.8511
 ### Risk of relapse score (ROR)
-### ...
+A score based on expression level of some of the genes. Range: -8.035678 to 75.13174
+### Risk of relapse score with proliferaton score (ROR-Prolif)
+A combined score based on expression level of more genes. Range: 1 to 97 (1-100).
+
+The two scores involving ROR also have categorical variants containing: \ 
+low, medium, high
+
+### Progression free survival (PFS)
+This is the outcome used in the clinical cohort.
+Here i have used correlation with the scores described above.
+Spearman can maybe be used.
+Another approach is to use the above scores to divide the patient in to two groups and see if the two groups show clearly separable PFS over time (basically lock at the graphs).
+The differentiation into two groups is done base on best values from a ROC curve.
 
@@
 # Approch
-Test all thinkable models to see if some is superior
+Test all thinkable models in a search for superior models
 
 # Evaluation of models
-Two levels of evaluation is scheduled:
+Two levels of evaluation is considered:
 
-## 1. Relative comparison of models
+## 1. Relative comparison of the different models
 1000 bootstrap models are fitted and then evaluated on the original sample.
@@
 ### - xgboost
-## Feature selecting ensemble model
+## Stacking using different features in the base models
 

### 2023-02-09 R_codeP01/reports/MS2_report02.Rmd
worked with residual

@@
 Furthermore, 8 immune cells are represented with specific genes.
-These sets are substantially smaller then the signature genes; which I presume leads to some issue in modeling (as for clinicla data - see next sentence).
+These sets are substantially smaller then the signature genes; which I presume leads to some issue in modeling (as for clinical data too - see next sentence).
 

### 2023-02-09 R_codeP01/scripts/07_residuals_lasso_boot01.R

@@ -61,7 +61,7 @@ lasso_res_boot <- function(df_train, df_test, pred_mech, additive=TRUE, func=las
   return(list(cor_vec=cor_vec, coef_matrix=coef_matrix, MSE_vec=MSE_vec))
 }
 
-t_ <- lasso_res_boot(prolif_6genes, prolif_6genes, pred_mech, additive=F, func=lasso_sample, method="pearson", n_bootstraps=10)
+t_ <- lasso_res_boot(prolif_6genes, prolif_6genes, pred_mech, additive=T, func=lasso_sample, method="pearson", n_bootstraps=10)
 mean(t_$cor_vec)
 sd(t_$cor_vec)
 
@@ -71,7 +71,7 @@ pred_mech <- df_771genes_mech_pred.scaled_prolif$model_prediction
 
 # RUN: lb_obj_residuals6_prolif
 set.seed(123)
-lb_obj_residuals6_prolif  <- lasso_res_boot(prolif_6genes, prolif_6genes, pred_mech, additive=F, lasso_sample, method="pearson", n_bootstraps=1000)
+lb_obj_residuals6_prolif  <- lasso_res_boot(prolif_6genes, prolif_6genes, pred_mech, additive=T, lasso_sample, method="pearson", n_bootstraps=1000)
 head(lb_obj_residuals6_prolif$coef_matrix)[,1:6]
 save(lb_obj_residuals6_prolif, file="/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_residuals6_prolif.RData")
 load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_residuals6_prolif.RData")

### 2023-02-09 R_codeP01/scripts/33_ensemble_stack_02.R

@@ -15,10 +15,6 @@ library(ggplot2)
 ###########################################################
 
 
-
-
-t <- lasso_rep_cv(prolif_771genes, folds=2, repeats=2, method="pearson")
-
 # Function: repeated k-fold cross validation
 lasso_rep_cv <- function(df_data, folds=5, repeats=1, method="pearson") {
   n_models <- repeats * folds
@@ -60,29 +56,34 @@ lasso_rep_cv <- function(df_data, folds=5, repeats=1, method="pearson") {
        # stack predictions
       pred_y_L0 <- cbind(train_data$Y, pred_prolif, pred_immune, pred_ER_signal)
       colnames(pred_y_L0) <- c("Y", "pred_prolif", "pred_immune", "pred_ER_signal")
-      # fit meta-model
-      fm <- as.formula(Y ~ pred_prolif+pred_immune+pred_ER_signal)
-      meta_model <- lm(fm, data = as.data.frame(pred_y_L0))
       
+      # fit linear meta-model
+      fm <- Y ~ pred_prolif + pred_immune + pred_ER_signal
+      # meta_model01 <- lm(fm, data = as.data.frame(pred_y_L0))
+      # print(summary(meta_model01))
+      # fit lasso meta-model
+      meta_model02 <- cv.glmnet(pred_y_L0[, 2:4], train_data$Y, nfolds=5)
+      
+      ####################################################################
+      ## test part
+      ####################################################################
       # prediction from level 0 using test data
       test_pred_prolif = predict(fit_prolif, newx = as.matrix(test_data[c(char_prolif)]), type = "response", s = "lambda.min")
       test_pred_immune = predict(fit_immune_inf, newx = as.matrix(test_data[c(char_immune_inf)]), type = "response", s = "lambda.min")
       test_pred_ER_signal = predict(fit_ER_singaling, newx = as.matrix(test_data[c(char_ER_signaling)]), type = "response", s = "lambda.min")
       
       # stack predictions
-      pred_y_L1 <- cbind(test_data$Y, test_pred_prolif, test_pred_immune, test_pred_ER_signal)
-      colnames(pred_y_L1) <- c("Y", "pred_prolif", "pred_immune", "pred_ER_signal")
+      pred_y_L1 <- cbind(test_pred_prolif, test_pred_immune, test_pred_ER_signal)
[…]

### 2023-02-09 R_codeP01/scripts/90_output01.R

@@ -21,7 +21,7 @@ report02_out <- function(object){
   cor_var <- var(cor_vec, na.rm=TRUE)
   cat("Variance:", cor_var, "\n")
   cor_sd <- sd(na.omit(cor_vec)) 
-  cat("st.dev.:", cor_sd)
+  cat("st.dev.:", cor_sd, "\n")
   
   # Histogram correlations
   correlations_finite <- cor_vec[is.finite(cor_vec)]

### 2023-02-10 R_codeP01/reports/MS2_report02.Rmd
report working

@@
 ```{r}
+## INPUT (features):
+# genes, demographics, clinical
+
+## OUTPUT (response):
+# proliferation score
+# ROR score
+# ROR: low, mid, high
+# ROR+prolif score
+# ROR+prolif: low, mid, high
+# others? e.g.: Cellularity_perc, Ki67_perc, Positive_lymph_nodes ...
+
+## OBJECTS:
 # lb_obj_6_prolif.RData
 # lb_obj_771_prolif.RData
+# lb_obj_residuals_6_prolif.RData
 # lb_obj_771_residuals_prolif.RData
@@
 
-# lb_obj_771_ROR.RData
+# lb_obj_6_ROR_prolif.RData
+# lb_obj_771_ROR_prolif.RData
+# lb_obj_771_residuals_ROR_prolif.RData
+# similar objects with logistic regression on low vs (mid+high)
+
+# lc_obj_6_prolif.RData
+# lc_obj_771_prolif.RData
+# lc_obj_771_residuals_prolif.RData
+# lc_obj_nodes_prolif.RData
 #
-# lk_obj_771_prolif.RData
+# lc_obj_6_ROR_prolif.RData
+# lc_obj_771_ROR_prolif.RData
+# lc_obj_771_residuals_ROR_prolif.RData
+# similar objects with logistic regression on low vs (mid+high)
+# ...
+# rb_obj_6_prolif.RData
+#
+# eb_obj_6_prolif.RData
 #
@@
 # 
+# bc_obj_6_prolif.RData
 #
+# pb_obj_6_prolif.RData
+#
+# sb_obj_6_prolif.RData
+#
+# cb_obj_6_prolif.RData
+
 ```
@@
 
-# Models
+# RESULTS
+
+# Results of individual modles:
+
+# Models tested
 ## Lasso
@@
 ### - xgboost
+## PCA feature engineering
 ## Stacking using different features in the base models 
-
-# RESULTS
+## Synergistic learning
 ```{r}
@@
 
-# Lasso
-
-## Bootstrap
+# Lasso - Bootstrap
 ### 6 genes -> proliferation score
@@
 
-### Mechnaistic + Residuals -> proliferation score
+### Mechanistic + Residuals -> proliferation score (additive)
 ```{r}
-load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_residuals771_prolif.RData")
-l_b_residuals771_p <- report02_out(lb_obj_residuals771_prolif)
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_residuals_771_prolif.RData")
+l_b_residuals_771_p_a <- report02_out(lb_obj_residuals_771_prolif)
 ```
-### Mechnaistic + Residuals -> ROR-proliferation score
+### Mechanistic + Residuals -> proliferation score (multiplicative)
 ```{r}
-load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_residuals_RORprolif.RData")
-l_b_residuals_ROR_p <- report02_out(lb_obj_residuals_RORprolif)
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_residuals_771_prolif.RData")
+l_b_residuals_771_p_m <- report02_out(lb_obj_residuals_771_prolif)
+```
+### Mechnaistic + Residuals -> ROR-proliferation score (additive)
+```{r}
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_residuals_771_RORprolif.RData")
+l_b_residuals_ROR_p_a <- report02_out(lb_obj_residuals_771_RORprolif)
+```
+### Mechnaistic + Residuals -> ROR-proliferation score (multiplicative)
+```{r}
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_residuals_771_RORprolif.RData")
+l_b_residuals_ROR_p_m <- report02_out(lb_obj_residuals_771_RORprolif)
 ```
 
-## Repeated cross-validation
+# Summery results: lasso proliferation score (bootstrap) 
+```{r}
+library(knitr)
+data_table <- data.frame(
+  Model = c("lasso 6 genes", "lasso 771 genes", "Nodes", "Residual additive", "Residual multiplicative"),
+  cor_mean = c(l_b_6_p$cor_mean, l_b_771_p$cor_mean, l_b_nodes_p$cor_mean, l_b_residuals_771_p_a$cor_mean, l_b_residuals_771_p_m$cor_mean),
+  sd_cor = c(l_b_6_p$cor_sd, l_b_771_p$cor_sd, l_b_nodes_p$cor_sd, l_b_residuals_771_p_a$cor_sd, l_b_residuals_771_p_m$cor_sd),
+  MSE_mean = c(l_b_6_p$MSE_mean, l_b_771_p$MSE_mean, l_b_nodes_p$MSE_mean, l_b_residuals_771_p_a$MSE_mean, l_b_residuals_771_p_m$MSE_mean),
+  MSE_sd = c(l_b_6_p$MSE_sd, l_b_771_p$MSE_sd, l_b_nodes_p$MSE_sd, l_b_residuals_771_p_a$MSE_sd, l_b_residuals_771_p_m$MSE_sd)
+)
+kable(data_table)
+```
+
+# Summery results: lasso ROR+proliferation score (bootstrap) 
+```{r}
+data_table <- data.frame(
+  Model = c("lasso 6 genes", "lasso 771 genes", "Nodes", "Residual additive", "Residual multiplicative"),
+  cor_mean = c(l_b_6_ROR_p$cor_mean, l_b_771_ROR_p$cor_mean, l_b_nodes_ROR_p$cor_mean, l_b_residuals_ROR_p_a$cor_mean, l_b_residuals_ROR_p_m$cor_mean),
+  sd_cor = c(l_b_6_ROR_p$cor_sd, l_b_771_ROR_p$cor_sd, l_b_nodes_ROR_p$cor_sd, l_b_residuals_ROR_p_a$cor_sd, l_b_residuals_ROR_p_m$cor_sd),
+  MSE_mean = c(l_b_6_ROR_p$MSE_mean, l_b_771_ROR_p$MSE_mean, l_b_nodes_ROR_p$MSE_mean, l_b_residuals_ROR_p_a$MSE_mean, l_b_residuals_ROR_p_m$MSE_mean),
+  MSE_sd = c(l_b_6_ROR_p$MSE_sd, l_b_771_ROR_p$MSE_sd, l_b_nodes_ROR_p$MSE_sd, l_b_residuals_ROR_p_a$MSE_sd, l_b_residuals_ROR_p_m$MSE_sd)
+)
+kable(data_table)
+```
+
+## Lasso - Repeated cross-validation
+200 repeats of five fold cross-validation \ 
 ### 6 genes -> proliferation score
@@
 
+### Mechanistic + Residuals -> proliferation score (additive)
+```{r}
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_residuals_771_prolif.RData")
+l_b_residuals_771_p_a <- report02_out(lb_obj_residuals_771_prolif)
+```
+### Mechanistic + Residuals -> proliferation score (multiplicative)
+```{r}
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_residuals_771_prolif.RData")
+l_b_residuals_771_p_m <- report02_out(lb_obj_residuals_771_prolif)
+```
+### Mechnaistic + Residuals -> ROR-proliferation score (additive)
+```{r}
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_residuals_771_RORprolif.RData")
+l_b_residuals_ROR_p_a <- report02_out(lb_obj_residuals_771_RORprolif)
+```
+### Mechnaistic + Residuals -> ROR-proliferation score (multiplicative)
+```{r}
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_residuals_771_RORprolif.RData")
+l_b_residuals_ROR_p_m <- report02_out(lb_obj_residuals_771_RORprolif)
+```
+
+# Summery results: lasso proliferation score (bootstrap) 
+```{r}
+library(knitr)
+data_table <- data.frame(
+  Model = c("lasso 6 genes", "lasso 771 genes", "Nodes", "Residual additive", "Residual multiplicative"),
+  cor_mean = c(l_b_6_p$cor_mean, l_b_771_p$cor_mean, l_b_nodes_p$cor_mean, l_b_residuals_771_p_a$cor_mean, l_b_residuals_771_p_m$cor_mean),
+  sd_cor = c(l_b_6_p$cor_sd, l_b_771_p$cor_sd, l_b_nodes_p$cor_sd, l_b_residuals_771_p_a$cor_sd, l_b_residuals_771_p_m$cor_sd),
+  MSE_mean = c(l_b_6_p$MSE_mean, l_b_771_p$MSE_mean, l_b_nodes_p$MSE_mean, l_b_residuals_771_p_a$MSE_mean, l_b_residuals_771_p_m$MSE_mean),
+  MSE_sd = c(l_b_6_p$MSE_sd, l_b_771_p$MSE_sd, l_b_nodes_p$MSE_sd, l_b_residuals_771_p_a$MSE_sd, l_b_residuals_771_p_m$MSE_sd)
+)
+kable(data_table)
+```
+
+# Summery results: lasso ROR+proliferation score (bootstrap) 
+```{r}
+data_table <- data.frame(
+  Model = c("lasso 6 genes", "lasso 771 genes", "Nodes", "Residual additive", "Residual multiplicative"),
+  cor_mean = c(l_b_6_ROR_p$cor_mean, l_b_771_ROR_p$cor_mean, l_b_nodes_ROR_p$cor_mean, l_b_residuals_ROR_p_a$cor_mean, l_b_residuals_ROR_p_m$cor_mean),
+  sd_cor = c(l_b_6_ROR_p$cor_sd, l_b_771_ROR_p$cor_sd, l_b_nodes_ROR_p$cor_sd, l_b_residuals_ROR_p_a$cor_sd, l_b_residuals_ROR_p_m$cor_sd),
+  MSE_mean = c(l_b_6_ROR_p$MSE_mean, l_b_771_ROR_p$MSE_mean, l_b_nodes_ROR_p$MSE_mean, l_b_residuals_ROR_p_a$MSE_mean, l_b_residuals_ROR_p_m$MSE_mean),
+  MSE_sd = c(l_b_6_ROR_p$MSE_sd, l_b_771_ROR_p$MSE_sd, l_b_nodes_ROR_p$MSE_sd, l_b_residuals_ROR_p_a$MSE_sd, l_b_residuals_ROR_p_m$MSE_sd)
+)
+kable(data_table)
+```
+
 # Ridge
@@
 # Post Lasso
+
+# Summery of results
+## Lasso proliferation score (bootstrap) 
+```{r}
+data_table <- data.frame(
+  Model = c("lasso 6 genes", "lasso 771 genes", "Nodes", "Residual additive", "Residual multiplicative"),
+  cor_mean = c(l_b_6_p$cor_mean, l_b_771_p$cor_mean, l_b_nodes_p$cor_mean, l_b_residuals_771_p_a$cor_mean, l_b_residuals_771_p_m$cor_mean),
+  sd_cor = c(l_b_6_p$cor_sd, l_b_771_p$cor_sd, l_b_nodes_p$cor_sd, l_b_residuals_771_p_a$cor_sd, l_b_residuals_771_p_m$cor_sd),
+  MSE_mean = c(l_b_6_p$MSE_mean, l_b_771_p$MSE_mean, l_b_nodes_p$MSE_mean, l_b_residuals_771_p_a$MSE_mean, l_b_residuals_771_p_m$MSE_mean),
+  MSE_sd = c(l_b_6_p$MSE_sd, l_b_771_p$MSE_sd, l_b_nodes_p$MSE_sd, l_b_residuals_771_p_a$MSE_sd, l_b_residuals_771_p_m$MSE_sd)
+)
+kable(data_table)
+```

### 2023-02-10 R_codeP01/scripts/01_dataclean01.R

@@ -61,7 +61,7 @@ df_6genes_with_output <- function(output){
     filter(timepoint=="SCR") |> 
     filter(TrialArmNeo=="Letro+Ribo")
   
-  df_output <- df01 |> select(c(UniqueID, output, timepoint, TrialArmNeo)) |>
+  df_output <- df01 |> select(c(UniqueID, all_of(output), timepoint, TrialArmNeo)) |>
     filter(timepoint=="SUR") |> 
     filter(TrialArmNeo=="Letro+Ribo")
   
@@ -119,7 +119,7 @@ df_genes_with_output <- function(df, predictors, output){
 }
 
 prolif_771genes <- df_genes_with_output(df01, all_genes, "ProliferationScore")
-RORprolif_771genes <- df_genes_with_output(df01, all_genes, "ROR_P_Subtype_Proliferation")
+ROR_prolif_771genes <- df_genes_with_output(df01, all_genes, "ROR_P_Subtype_Proliferation")
 
 head(prolif_771genes[,1:5])
 lastcol <- ncol(prolif_771genes)
@@ -181,12 +181,12 @@ df_genes_with_mech.pred_and_output <- function(df, predictors, output){
     filter(timepoint=="SCR") |> 
     filter(TrialArmNeo=="Letro+Ribo")
   
-  df_SUR <- df |> select(c(UniqueID, timepoint, TrialArmNeo, output, model_prediction)) |>
+  df_SUR <- df |> select(c(UniqueID, timepoint, TrialArmNeo, all_of(output), model_prediction)) |>
     filter(timepoint=="SUR") |> 
     filter(TrialArmNeo=="Letro+Ribo")
   
-  df_out <- full_join(df_SUR, df_genes, by = "UniqueID") |> 
-    select(-UniqueID)
+  df_out <- full_join(df_SUR, df_genes, by = "UniqueID") |>               # join the two time points
+    select(-UniqueID)                                                     # remove UniqueID
   
   df_out <- df_out |> 
     select(- c(timepoint.x, TrialArmNeo.x, timepoint.y, TrialArmNeo.y))  # remove unnecessary columns
@@ -220,6 +220,10 @@ df_771genes_mech_pred.scaled_prolif <- df_771genes_mech_pred_prolif |>
 
 # check if data looks the same
 hist(df_771genes_mech_pred.scaled_prolif$model_prediction)
+
+# extracting prediction of mechanistic model
[…]

### 2023-02-10 R_codeP01/scripts/07_residual03.R

@@ -1,0 +1,255 @@
+###########################################################
+## Repeated cross-validation for testing the Lasso model ##
+###########################################################
+##
+## Test against the fold
+## Cross-validation (5-fold) used for training/tuning lambda and selecting features
+## output: selected genes; proliferation.score correlation; SEM
+
+## Post Lasso model is made at the bottom
+
+library(glmnet)
+library(caret)
+library(ggplot2)
+
+###########################################################
+##  Repeated cross validation ##
+###########################################################
+
+# Function: repeated k-fold cross validation
+lasso_residual_rep_cv <- function(df_data, func=lasso_sample, folds=5, repeats=200, method="pearson") {
+  n_models <- repeats * folds
+  print(n_models)
+  cor_vec <- rep(NA, n_models)
+  MSE_vec <- rep(NA, n_models)
+  coef_matrix <- matrix(NA, nrow = n_models, ncol = ncol(df_data[,-1]))
+  colnames(coef_matrix) <- colnames(df_data[, -1])
+  
+  coef_matrix_row_index <- 1
+  
+  # calculating the residuals
+  if (additive==TRUE){res <- df_data$Y - pred_mech}
+  else{res <- df_data$Y / pred_mech}
+  
+  # Repeat the cross-validation process
+  for (i in 1:repeats) {
+    # Create the folds for evaluating the performance
+    kf <- caret::createFolds(df_data[,1], k = folds, list = TRUE, returnTrain = TRUE)
+    # Loop through the folds
+    for (j in 1:folds) {
+      # Get the training and testing data
+      train_data <- df_data[kf[[j]],]
+      test_data <- df_data[-kf[[j]],]
+      
+      # Fit the function on the training data and get results
+      fit <- func(train_data)
+      
+      coef_matrix[coef_matrix_row_index, ] <- coef(fit, s = "lambda.min")[-1]
+      
+      pred = predict(fit, newx = as.matrix(test_data)[,-1], type = "response", s = "lambda.min")  
[…]

### 2023-02-10 R_codeP01/scripts/07_residuals_lasso_boot01.R

@@ -52,6 +52,8 @@ lasso_res_boot <- function(df_train, df_test, pred_mech, additive=TRUE, func=las
     if (additive==TRUE){pred <- pred_mech + pred_res}
     else{pred <- pred_mech * pred_res}
     
+    pred <- as.matrix(pred)
+    
     cor_vec[i] <- suppressWarnings(cor(pred, df_test$Y, method = method))
     MSE_vec[i] <- mean((df_test$Y - pred)^2)
     # cor_vec[i]  <- suppressWarnings(cor(pred, df_test[,1], method = method))
@@ -61,53 +63,80 @@ lasso_res_boot <- function(df_train, df_test, pred_mech, additive=TRUE, func=las
   return(list(cor_vec=cor_vec, coef_matrix=coef_matrix, MSE_vec=MSE_vec))
 }
 
-t_ <- lasso_res_boot(prolif_6genes, prolif_6genes, pred_mech, additive=T, func=lasso_sample, method="pearson", n_bootstraps=10)
+t_ <- lasso_res_boot(prolif_6genes, prolif_6genes, pred_mech, additive=T, func=lasso_sample, method="pearson", n_bootstraps=1)
 mean(t_$cor_vec)
 sd(t_$cor_vec)
 
 # The predictions of the mechanistic model is scales by a linear model to be more similar to the proliferation scores
-# But the relationship between mechnistic prediction and proliferation score is not fully linear
+# But the relationship between mechanistic prediction and proliferation score is not fully linear
 pred_mech <- df_771genes_mech_pred.scaled_prolif$model_prediction
 
 # RUN: lb_obj_residuals6_prolif
+# Here just testing if I can use the df01 directly:
+df_prolif_6genes <- select(df_771genes_mech_pred.scaled_prolif, -model_prediction)
+df_prolif_6genes <- select(df_prolif_6genes, c(Y, CCND1, CCNE1, CDKN1A, ESR1, MYC, RB1))
 set.seed(123)
-lb_obj_residuals6_prolif  <- lasso_res_boot(prolif_6genes, prolif_6genes, pred_mech, additive=T, lasso_sample, method="pearson", n_bootstraps=1000)
[…]

### 2023-02-11 R_codeP01/reports/MS2_report02.Rmd
cv residuals

@@
 ```{r}
-load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_residuals_771_prolif.RData")
-l_b_residuals_771_p_a <- report02_out(lb_obj_residuals_771_prolif)
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lc_obj_residuals_771_prolif.RData")
+lc_residuals_771_p_a <- report02_out(lc_obj_residuals_771_p_a)
 ```
@@
 ```{r}
-load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_residuals_771_prolif.RData")
-l_b_residuals_771_p_m <- report02_out(lb_obj_residuals_771_prolif)
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lc_obj_residuals_771_prolif.RData")
+lc_residuals_771_p_m <- report02_out(lc_obj_residuals_771_prolif)
 ```
@@
 ```{r}
-load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_residuals_771_RORprolif.RData")
-l_b_residuals_ROR_p_a <- report02_out(lb_obj_residuals_771_RORprolif)
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lc_obj_residuals_771_RORprolif.RData")
+lc_residuals_ROR_p_a <- report02_out(lc_obj_residuals_771_RORprolif)
 ```
@@
 ```{r}
-load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_residuals_771_RORprolif.RData")
-l_b_residuals_ROR_p_m <- report02_out(lb_obj_residuals_771_RORprolif)
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lc_obj_residuals_771_RORprolif.RData")
+lc_residuals_ROR_p_m <- report02_out(lc_obj_residuals_771_RORprolif)
 ```

### 2023-02-11 R_codeP01/scripts/07_residual03.R

@@ -17,7 +17,7 @@ library(ggplot2)
 ###########################################################
 
 # Function: repeated k-fold cross validation
-lasso_residual_rep_cv <- function(df_data, func=lasso_sample, folds=5, repeats=200, method="pearson") {
+lasso_residual_rep_cv <- function(df_data, pred_mech, additive=TRUE, func=lasso_sample, folds=5, repeats=200, method="pearson") {
   n_models <- repeats * folds
   print(n_models)
   cor_vec <- rep(NA, n_models)
@@ -27,9 +27,15 @@ lasso_residual_rep_cv <- function(df_data, func=lasso_sample, folds=5, repeats=2
   
   coef_matrix_row_index <- 1
   
+  pred_mech <- as.matrix(pred_mech)
+  
   # calculating the residuals
   if (additive==TRUE){res <- df_data$Y - pred_mech}
   else{res <- df_data$Y / pred_mech}
+  
+  # create df with training data and update the training data with residuals instead of Y
+  df_train_res <- df_data
+  df_train_res$Y <- res
   
   # Repeat the cross-validation process
   for (i in 1:repeats) {
@@ -37,16 +43,24 @@ lasso_residual_rep_cv <- function(df_data, func=lasso_sample, folds=5, repeats=2
     kf <- caret::createFolds(df_data[,1], k = folds, list = TRUE, returnTrain = TRUE)
     # Loop through the folds
     for (j in 1:folds) {
-      # Get the training and testing data
-      train_data <- df_data[kf[[j]],]
+      # Get the training and testing data: here picked from two different df
+      train_data_res <- df_train_res[kf[[j]],]
       test_data <- df_data[-kf[[j]],]
       
+      test_pred_mech <- pred_mech[-kf[[j]]]
+      
       # Fit the function on the training data and get results
-      fit <- func(train_data)
+      fit <- func(train_data_res)
       
       coef_matrix[coef_matrix_row_index, ] <- coef(fit, s = "lambda.min")[-1]
       
[…]

### 2023-02-11 R_codeP01/reports/MS2_report02.Rmd
elastic net boot and rc

--- 2023-02-10 R_codeP01/reports/MS2_report02.Rmd
@@
 source("/Users/anders/Documents/Master/Cancer/R_codeP01/scripts/90_output01.R")
+source("/Users/anders/Documents/Master/Cancer/R_codeP01/scripts/90_output_ridge_01.R")
 ```
@@
 ```{r}
-load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_residuals_771_prolif.RData")
-l_b_residuals_771_p_a <- report02_out(lb_obj_residuals_771_prolif)
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_residuals_771_prolif_a.RData")
+l_b_residuals_771_p_a <- report02_out(lb_obj_residuals_771_prolif_a)
 ```
@@
 ```{r}
-load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_residuals_771_prolif.RData")
-l_b_residuals_771_p_m <- report02_out(lb_obj_residuals_771_prolif)
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_residuals_771_prolif_m.RData")
+l_b_residuals_771_p_m <- report02_out(lb_obj_residuals_771_prolif_m)
 ```
@@
 ```{r}
-load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_residuals_771_RORprolif.RData")
-l_b_residuals_ROR_p_a <- report02_out(lb_obj_residuals_771_RORprolif)
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_residuals_771_RORprolif_a.RData")
+l_b_residuals_ROR_p_a <- report02_out(lb_obj_residuals_771_RORprolif_a)
 ```
@@
 ```{r}
-load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_residuals_771_RORprolif.RData")
-l_b_residuals_ROR_p_m <- report02_out(lb_obj_residuals_771_RORprolif)
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_residuals_771_RORprolif_m.RData")
+l_b_residuals_ROR_p_m <- report02_out(lb_obj_residuals_771_RORprolif_m)
 ```
 
-# Summery results: lasso proliferation score (bootstrap) 
+### Summery results: lasso proliferation score (bootstrap) 
 ```{r}
@@
 
-# Summery results: lasso ROR+proliferation score (bootstrap) 
+### Summery results: lasso ROR+proliferation score (bootstrap) 
 ```{r}
@@
 ```{r}
-load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_residuals_771_prolif.RData")
-l_b_residuals_771_p_a <- report02_out(lb_obj_residuals_771_prolif)
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lc_obj_residuals_771_p_a.RData")
+l_c_residuals_771_p_a <- report02_out(lc_obj_residuals_771_p_a)
 ```
@@
 ```{r}
-load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_residuals_771_prolif.RData")
-l_b_residuals_771_p_m <- report02_out(lb_obj_residuals_771_prolif)
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lc_obj_residuals_771_p_m.RData")
+l_c_residuals_771_p_m <- report02_out(lc_obj_residuals_771_p_m)
 ```
@@
 ```{r}
-load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_residuals_771_RORprolif.RData")
-l_b_residuals_ROR_p_a <- report02_out(lb_obj_residuals_771_RORprolif)
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lc_obj_residuals_771_ROR_p_a.RData")
+l_c_residuals_ROR_p_a <- report02_out(lc_obj_residuals_771_ROR_p_a)
 ```
@@
 ```{r}
-load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_residuals_771_RORprolif.RData")
-l_b_residuals_ROR_p_m <- report02_out(lb_obj_residuals_771_RORprolif)
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lc_obj_residuals_771_ROR_p_m.RData")
+l_c_residuals_ROR_p_m <- report02_out(lc_obj_residuals_771_ROR_p_m)
 ```
 
-# Summery results: lasso proliferation score (bootstrap) 
+### Summery results: lasso proliferation score (repeated cross-validation) 
 ```{r}
@@
   Model = c("lasso 6 genes", "lasso 771 genes", "Nodes", "Residual additive", "Residual multiplicative"),
-  cor_mean = c(l_b_6_p$cor_mean, l_b_771_p$cor_mean, l_b_nodes_p$cor_mean, l_b_residuals_771_p_a$cor_mean, l_b_residuals_771_p_m$cor_mean),
-  sd_cor = c(l_b_6_p$cor_sd, l_b_771_p$cor_sd, l_b_nodes_p$cor_sd, l_b_residuals_771_p_a$cor_sd, l_b_residuals_771_p_m$cor_sd),
-  MSE_mean = c(l_b_6_p$MSE_mean, l_b_771_p$MSE_mean, l_b_nodes_p$MSE_mean, l_b_residuals_771_p_a$MSE_mean, l_b_residuals_771_p_m$MSE_mean),
-  MSE_sd = c(l_b_6_p$MSE_sd, l_b_771_p$MSE_sd, l_b_nodes_p$MSE_sd, l_b_residuals_771_p_a$MSE_sd, l_b_residuals_771_p_m$MSE_sd)
+  cor_mean = c(l_c_6_p$cor_mean, l_c_771_p$cor_mean, l_c_nodes_p$cor_mean, l_c_residuals_771_p_a$cor_mean, l_c_residuals_771_p_m$cor_mean),
+  sd_cor = c(l_c_6_p$cor_sd, l_c_771_p$cor_sd, l_c_nodes_p$cor_sd, l_c_residuals_771_p_a$cor_sd, l_c_residuals_771_p_m$cor_sd),
+  MSE_mean = c(l_c_6_p$MSE_mean, l_b_771_p$MSE_mean, l_c_nodes_p$MSE_mean, l_c_residuals_771_p_a$MSE_mean, l_c_residuals_771_p_m$MSE_mean),
+  MSE_sd = c(l_c_6_p$MSE_sd, l_c_771_p$MSE_sd, l_c_nodes_p$MSE_sd, l_c_residuals_771_p_a$MSE_sd, l_c_residuals_771_p_m$MSE_sd)
 )
@@
 
-# Summery results: lasso ROR+proliferation score (bootstrap) 
+### Summery results: lasso ROR+proliferation score (repeated cross-validation) 
 ```{r}
@@
   Model = c("lasso 6 genes", "lasso 771 genes", "Nodes", "Residual additive", "Residual multiplicative"),
-  cor_mean = c(l_b_6_ROR_p$cor_mean, l_b_771_ROR_p$cor_mean, l_b_nodes_ROR_p$cor_mean, l_b_residuals_ROR_p_a$cor_mean, l_b_residuals_ROR_p_m$cor_mean),
-  sd_cor = c(l_b_6_ROR_p$cor_sd, l_b_771_ROR_p$cor_sd, l_b_nodes_ROR_p$cor_sd, l_b_residuals_ROR_p_a$cor_sd, l_b_residuals_ROR_p_m$cor_sd),
-  MSE_mean = c(l_b_6_ROR_p$MSE_mean, l_b_771_ROR_p$MSE_mean, l_b_nodes_ROR_p$MSE_mean, l_b_residuals_ROR_p_a$MSE_mean, l_b_residuals_ROR_p_m$MSE_mean),
-  MSE_sd = c(l_b_6_ROR_p$MSE_sd, l_b_771_ROR_p$MSE_sd, l_b_nodes_ROR_p$MSE_sd, l_b_residuals_ROR_p_a$MSE_sd, l_b_residuals_ROR_p_m$MSE_sd)
+  cor_mean = c(l_c_6_ROR_p$cor_mean, l_c_771_ROR_p$cor_mean, l_c_nodes_ROR_p$cor_mean, l_c_residuals_ROR_p_a$cor_mean, l_c_residuals_ROR_p_m$cor_mean),
+  sd_cor = c(l_c_6_ROR_p$cor_sd, l_c_771_ROR_p$cor_sd, l_c_nodes_ROR_p$cor_sd, l_c_residuals_ROR_p_a$cor_sd, l_c_residuals_ROR_p_m$cor_sd),
+  MSE_mean = c(l_c_6_ROR_p$MSE_mean, l_c_771_ROR_p$MSE_mean, l_c_nodes_ROR_p$MSE_mean, l_c_residuals_ROR_p_a$MSE_mean, l_c_residuals_ROR_p_m$MSE_mean),
+  MSE_sd = c(l_c_6_ROR_p$MSE_sd, l_c_771_ROR_p$MSE_sd, l_c_nodes_ROR_p$MSE_sd, l_c_residuals_ROR_p_a$MSE_sd, l_c_residuals_ROR_p_m$MSE_sd)
 )
@@
 
-# Ridge
-# Elastic Net
+# Ridge bootstrap
+### 771 genes -> proliferation score
+```{r}
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/r_b_obj_771_p.RData")
+r_b_771_p <- report02_out_ridge(r_b_obj_771_p)
+```
+### 771 genes -> ROR-proliferation score
+```{r}
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/r_b_obj_771_ROR_p.RData")
+r_b_771_ROR_p <- report02_out_ridge(r_b_obj_771_ROR_p)
+```
+
+# Ridge repeated cross-validation
+### 771 genes -> proliferation score
+```{r}
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/r_c_obj_771_prolif.RData")
+r_c_771_p <- report02_out_ridge(r_c_obj_771_prolif)
+```
+### 771 genes -> ROR-proliferation score
+```{r}
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/r_c_obj_771_RORprolif.RData")
+r_c_771_ROR_p <- report02_out_ridge(r_c_obj_771_RORprolif)
+```
+
+### Summery results: ridge 771 genes bootstrap and repeated cross-validation
+```{r}
+data_table <- data.frame(
+  Model = c("prolif boot", "ROR-prolif boot", "prolif rep cross-val", "ROR-prolif rep cross-val"),
+  cor_mean = c(r_b_771_p$cor_mean, r_b_771_ROR_p$cor_mean, r_c_771_p$cor_mean, r_c_771_ROR_p$cor_mean),
+  sd_cor = c(r_b_771_p$cor_sd, r_b_771_ROR_p$cor_sd, r_c_771_p$cor_sd, r_c_771_ROR_p$cor_sd),
+  MSE_mean = c(r_b_771_p$MSE_mean, r_b_771_ROR_p$MSE_mean, r_c_771_p$MSE_mean, r_c_771_ROR_p$MSE_mean),
+  MSE_sd = c(r_b_771_p$MSE_sd, r_b_771_ROR_p$MSE_sd, r_c_771_p$MSE_sd, r_c_771_ROR_p$MSE_sd)
+)
+kable(data_table)
+```
+
+# Elastic Net - bootstrap
+### 771 genes -> proliferation score
+```{r}
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/e_b_obj_771_p.RData")
+e_b_771_p <- report02_out_ridge(e_b_obj_771_p)
+```
+### 771 genes -> ROR-proliferation score
+```{r}
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/e_b_obj_771_ROR_p.RData")
+e_b_771_ROR_p <- report02_out_ridge(e_b_obj_771_ROR_p)
+```
+
+# Elastic Net: cross-validation
+### 771 genes -> proliferation score
+```{r}
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/e_c_obj_771_prolif.RData")
+e_c_771_p <- report02_out_ridge(e_c_obj_771_prolif)
+```
+### 771 genes -> ROR-proliferation score
+```{r}
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/e_c_obj_771_RORprolif.RData")
+e_c_771_ROR_p <- report02_out_ridge(e_c_obj_771_RORprolif)
+```
+
+### Summery results: elastic net 771 genes bootstrap and repeated cross-validation
+```{r}
+data_table <- data.frame(
+  Model = c("prolif boot", "ROR-prolif boot", "prolif rep cross-val", "ROR-prolif rep cross-val"),
+  cor_mean = c(e_b_771_p$cor_mean, e_b_771_ROR_p$cor_mean, e_c_771_p$cor_mean, e_c_771_ROR_p$cor_mean),
+  sd_cor = c(e_b_771_p$cor_sd, e_b_771_ROR_p$cor_sd, e_c_771_p$cor_sd, e_c_771_ROR_p$cor_sd),
+  MSE_mean = c(e_b_771_p$MSE_mean, e_b_771_ROR_p$MSE_mean, e_c_771_p$MSE_mean, e_c_771_ROR_p$MSE_mean),
+  MSE_sd = c(e_b_771_p$MSE_sd, e_b_771_ROR_p$MSE_sd, e_c_771_p$MSE_sd, e_c_771_ROR_p$MSE_sd)
+)
+kable(data_table)
+```
+
 # Boosting with stumps as base learner

### 2023-02-11 R_codeP01/scripts/01_dataclean01.R

@@ -129,9 +129,12 @@ head(prolif_771genes[, (lastcol-5): lastcol])
 dfA03 <- Proliferation_ALLgenes |> 
   select(- c(timepoint.x, TrialArmNeo.x, timepoint.y, TrialArmNeo.y))
 
-# Matrices for glmnet (not in use anymore)
-X <- as.matrix(Proliferation_ALLgenes |> select(all_of(genes)))
-Y <- as.matrix(select(Proliferation_ALLgenes, Y))
+# Matrices for glmnet
+X <- as.matrix(prolif_771genes |> select(all_of(genes)))
+Y <- as.matrix(select(prolif_771genes, Y))
+
+X <- as.matrix(ROR_prolif_771genes |> select(all_of(genes)))
+Y <- as.matrix(select(ROR_prolif_771genes, Y))
 
 
 #################

### 2023-02-11 R_codeP01/scripts/04_lasso03.R

@@ -1,251 +1,0 @@
-###########################################################
-## Repeated cross-validation for testing the Lasso model ##
-###########################################################
-##
-## Test against the fold
-## Cross-validation (5-fold) used for training/tuning lambda and selecting features
-## output: selected genes; proliferation.score correlation; SEM
-
-## Post Lasso model is made at the bottom
-
-library(glmnet)
-library(caret)
-library(ggplot2)
-
-###########################################################
-##  Repeated cross validation ##
-###########################################################
-
-# Function: repeated k-fold cross validation
-lasso_rep_cv <- function(df_data, func=lasso_sample, folds=5, repeats=200, method="pearson") {
-  n_models <- repeats * folds
-  print(n_models)
-  cor_vec <- rep(NA, n_models)
-  MSE_vec <- rep(NA, n_models)
-  coef_matrix <- matrix(NA, nrow = n_models, ncol = ncol(df_data[,-1]))
-  colnames(coef_matrix) <- colnames(df_data[, -1])
-  
-  coef_matrix_row_index <- 1
-  
-  # Repeat the cross-validation process
-  for (i in 1:repeats) {
-    # Create the folds for evaluating the performance
-    kf <- caret::createFolds(df_data[,1], k = folds, list = TRUE, returnTrain = TRUE)
-    # Loop through the folds
-    for (j in 1:folds) {
-      # Get the training and testing data
-      train_data <- df_data[kf[[j]],]
-      test_data <- df_data[-kf[[j]],]
-      
-      # Fit the function on the training data and get results
-      fit <- func(train_data)
-      
-      coef_matrix[coef_matrix_row_index, ] <- coef(fit, s = "lambda.min")[-1]
-      
-      pred = predict(fit, newx = as.matrix(test_data)[,-1], type = "response", s = "lambda.min")  
-      cor_vec[coef_matrix_row_index]  <- suppressWarnings(cor(pred, test_data[,1], method=method))
[…]

### 2023-02-11 R_codeP01/scripts/04_lasso_rc_03.R

@@ -1,0 +1,251 @@
+###########################################################
+## Repeated cross-validation for testing the Lasso model ##
+###########################################################
+##
+## Test against the fold
+## Cross-validation (5-fold) used for training/tuning lambda and selecting features
+## output: selected genes; proliferation.score correlation; SEM
+
+## Post Lasso model is made at the bottom
+
+library(glmnet)
+library(caret)
+library(ggplot2)
+
+###########################################################
+##  Repeated cross validation ##
+###########################################################
+
+# Function: repeated k-fold cross validation
+lasso_rep_cv <- function(df_data, func=lasso_sample, folds=5, repeats=200, method="pearson") {
+  n_models <- repeats * folds
+  print(n_models)
+  cor_vec <- rep(NA, n_models)
+  MSE_vec <- rep(NA, n_models)
+  coef_matrix <- matrix(NA, nrow = n_models, ncol = ncol(df_data[,-1]))
+  colnames(coef_matrix) <- colnames(df_data[, -1])
+  
+  coef_matrix_row_index <- 1
+  
+  # Repeat the cross-validation process
+  for (i in 1:repeats) {
+    # Create the folds for evaluating the performance
+    kf <- caret::createFolds(df_data[,1], k = folds, list = TRUE, returnTrain = TRUE)
+    # Loop through the folds
+    for (j in 1:folds) {
+      # Get the training and testing data
+      train_data <- df_data[kf[[j]],]
+      test_data <- df_data[-kf[[j]],]
+      
+      # Fit the function on the training data and get results
+      fit <- func(train_data)
+      
+      coef_matrix[coef_matrix_row_index, ] <- coef(fit, s = "lambda.min")[-1]
+      
+      pred = predict(fit, newx = as.matrix(test_data)[,-1], type = "response", s = "lambda.min")  
+      cor_vec[coef_matrix_row_index]  <- suppressWarnings(cor(pred, test_data[,1], method=method))
[…]

### 2023-02-11 R_codeP01/scripts/05_ridge01.R

@@ -1,383 +1,0 @@
-## Ridge using bootstrap sample to train 1000 models
-## Cross-validation (5-fold) used for training/tuning lambda and selecting features
-## Test against original data sample and leave-out bootstrap sample
-## output: proliferation.score correlation; MSE; coefficients of best model in each bootstrap
-
-library(glmnet)
-
-##########################################################
-##  Bootstrap  Ridge - using original sample as test set ##
-##########################################################
-
-
-ridge_bootstrap_sample <- function(X, Y, ext.X, ext.Y, lambda.min=TRUE, method="pearson"){
-  # one bootstrap sample
-  # output: 
-  # 1. correlation between prediction and full input sample  (pearson or spearman should be set)
-  # 2. Coefficients of variables 
-  # 3. MSE
-  n = length(Y)
-  
-  int <- sample.int(n, size = n, replace = TRUE)
-  X_train = X[int,]
-  Y_train = Y[int]
-  
-  fit.cv <- cv.glmnet(X_train, Y_train, nfolds=5, alpha=0)
-  
-  co <- as.vector(coef(fit.cv, s = "lambda.min")) # as.vector makes an easier object to work with
-  
-  if (lambda.min == TRUE) {
-    pred_values = predict(fit.cv, newx = ext.X, type = "response", s = "lambda.min")      
-  }
-  if (lambda.min == FALSE) {
-    pred_values = predict(fit.cv, newx = ext.X, type = "response", s = "lambda.1se")      
-  }
-  cor <- suppressWarnings(cor(pred_values, ext.Y, method = method))
-  MSE <- mean((ext.Y - pred_values)^2)
-  return(list(cor=cor, co=co, MSE=MSE))
-}
-
-ridge_bootstrap_sample(X, Y, X, Y, TRUE)$cor
-
-
-# 1000 bootstrap fits
-ridge_boot = function(X, Y, ext.X, ext.Y, n_bootstraps=1000, method = "pearson") {
-  # run many bootstraps
-  # output: - vector with correlations 
-  #         - matrix with features coefficients
-  #         - vector with SEM
-  cor_vec <- rep(NA, n_bootstraps)
-  co_matrix <- matrix(NA, nrow = dim(X)[2], ncol = n_bootstraps)
-  rownames(co_matrix) <- colnames(X) 
-  MSE_vec <- rep(NA, n_bootstraps)
-  
[…]

### 2023-02-11 R_codeP01/scripts/05_ridge_boot_01.R

@@ -1,0 +1,236 @@
+## Ridge using bootstrap sample to train 1000 models
+## Cross-validation (5-fold) used for training/tuning lambda and selecting features
+## Test against original data sample and leave-out bootstrap sample
+## output: proliferation.score correlation; MSE; coefficients of best model in each bootstrap
+
+library(glmnet)
+
+##########################################################
+##  Bootstrap  Ridge - using original sample as test set ##
+##########################################################
+
+
+ridge_bootstrap_sample <- function(X, Y, ext.X, ext.Y, lambda.min=TRUE, method="pearson"){
+  # one bootstrap sample
+  # output: 
+  # 1. correlation between prediction and full input sample  (pearson or spearman should be set)
+  # 2. Coefficients of variables 
+  # 3. MSE
+  n = length(Y)
+  
+  int <- sample.int(n, size = n, replace = TRUE)
+  X_train = X[int,]
+  Y_train = Y[int]
+  
+  fit.cv <- cv.glmnet(X_train, Y_train, nfolds=5, alpha=0)
+  
+  co <- as.vector(coef(fit.cv, s = "lambda.min")) # as.vector makes an easier object to work with
+  
+  if (lambda.min == TRUE) {
+    pred_values = predict(fit.cv, newx = ext.X, type = "response", s = "lambda.min")      
+  }
+  if (lambda.min == FALSE) {
+    pred_values = predict(fit.cv, newx = ext.X, type = "response", s = "lambda.1se")      
+  }
+  cor <- suppressWarnings(cor(pred_values, ext.Y, method = method))
+  MSE <- mean((ext.Y - pred_values)^2)
+  return(list(cor=cor, co=co, MSE=MSE))
+}
+
+ridge_bootstrap_sample(X, Y, X, Y, TRUE)$cor
+
+
+ridge_boot = function(X, Y, ext.X, ext.Y, n_bootstraps=1000, method = "pearson") {
+  # run many bootstraps
+  # output: - vector with correlations 
+  #         - matrix with features coefficients
+  #         - vector with SEM
+  cor_vec <- rep(NA, n_bootstraps)
+  co_matrix <- matrix(NA, nrow = dim(X)[2], ncol = n_bootstraps)
[…]

### 2023-02-11 R_codeP01/scripts/05_rigde_rc_03.R

@@ -1,0 +1,240 @@
+###########################################################
+## Repeated cross-validation for testing the Ridge model ##
+###########################################################
+##
+## Test against the fold
+## Cross-validation (5-fold) used for training/tuning lambda and selecting features
+## output: selected genes; proliferation.score correlation; SEM
+
+## Post Lasso model is made at the bottom
+
+library(glmnet)
+library(caret)
+library(ggplot2)
+
+###########################################################
+##  Repeated cross validation ##
+###########################################################
+
+# Function: repeated k-fold cross validation
+ridge_rep_cv <- function(df_data, func=ridge_sample, folds=5, repeats=200, method="pearson") {
+  n_models <- repeats * folds
+  print(n_models)
+  cor_vec <- rep(NA, n_models)
+  MSE_vec <- rep(NA, n_models)
+  coef_matrix <- matrix(NA, nrow = n_models, ncol = ncol(df_data[,-1]))
+  colnames(coef_matrix) <- colnames(df_data[, -1])
+  
+  coef_matrix_row_index <- 1
+  
+  # Repeat the cross-validation process
+  for (i in 1:repeats) {
+    # Create the folds for evaluating the performance
+    kf <- caret::createFolds(df_data[,1], k = folds, list = TRUE, returnTrain = TRUE)
+    # Loop through the folds
+    for (j in 1:folds) {
+      # Get the training and testing data
+      train_data <- df_data[kf[[j]],]
+      test_data <- df_data[-kf[[j]],]
+      
+      # Fit the function on the training data and get results
+      fit <- func(train_data)
+      
+      coef_matrix[coef_matrix_row_index, ] <- coef(fit, s = "lambda.min")[-1]
+      
+      pred = predict(fit, newx = as.matrix(test_data)[,-1], type = "response", s = "lambda.min")  
+      cor_vec[coef_matrix_row_index]  <- suppressWarnings(cor(pred, test_data[,1], method=method))
+      MSE_vec[coef_matrix_row_index] <- mean((pred - test_data[,1])^2)
+      
[…]

### 2023-02-11 R_codeP01/scripts/06_elastic02.R

@@ -1,140 +1,0 @@
-#################################################################
-##  Bootstrap  Elastic Net - using original sample as test set ##
-#################################################################
-
-## Elastic Net using bootstrap sample to train 1000 models
-## Cross-validation (5-fold) used for training/tuning lambda and selecting features
-## Test against original data sample
-## output: proliferation.score correlation; SEM; Coefficient of genes
-
-library(glmnet)
-
-
-elastic_bootstrap_sample <- function(X, Y, ext.X, ext.Y, lambda.min=TRUE, method="pearson"){
-  # one bootstrap sample
-  # output: 
-  # 1. correlation between prediction and full input sample  (pearson or spearman should be set)
-  # 2. Coefficients of variables 
-  # 3. MSE
-  n = length(Y)
-  
-  int <- sample.int(n, size = n, replace = TRUE)
-  X_train = X[int,]
-  Y_train = Y[int]
-  
-  alphas = seq(0, 1, by=0.1)
-  
-  # To store results
-  fit.cv <- list()
-  cvm = rep(0, length(alphas))
-  
-  # run elastic net with cross-validation and alpha search
-  for (i in 1:length(alphas)){
-    fit.cv[[i]] <- cv.glmnet(X_train, Y_train, alpha = alphas[i], nfolds = 5)
-    cvm[i] <- min(fit.cv[[i]]$cvm)
-  }
-  
-  opt.idx <- which.min(cvm)
-  fit.cv <- fit.cv[[opt.idx]]
-  
-  co <- as.vector(coef(fit.cv, s="lambda.min"))
-  
-  if (lambda.min == TRUE) {
-    pred_values = predict(fit.cv, newx = ext.X, type = "response", s = "lambda.min")      
-  }
-  if (lambda.min == FALSE) {
-    pred_values = predict(fit.cv, newx = ext.X, type = "response", s = "lambda.1se")      
-  }
-  cor <- suppressWarnings(cor(pred_values, ext.Y, method = method))
-  MSE <- mean((ext.Y - pred_values)^2)
-  return(list(cor=cor, co=co, MSE=MSE))
-}
-
-elastic_bootstrap_sample(X, Y, X, Y, TRUE)$cor
-
-
-# 1000 bootstrap fits
[…]

### 2023-02-11 R_codeP01/scripts/06_elastic_boot_02.R

@@ -1,0 +1,164 @@
+#################################################################
+##  Bootstrap  Elastic Net - using original sample as test set ##
+#################################################################
+
+## Elastic Net using bootstrap sample to train 1000 models
+## Cross-validation (5-fold) used for training/tuning lambda and selecting features
+## Test against original data sample
+## output: proliferation.score correlation; SEM; Coefficient of genes
+
+library(glmnet)
+
+
+elastic_bootstrap_sample <- function(X, Y, ext.X, ext.Y, lambda.min=TRUE, method="pearson"){
+  # one bootstrap sample
+  # output: 
+  # 1. correlation between prediction and full input sample  (pearson or spearman should be set)
+  # 2. Coefficients of variables 
+  # 3. MSE
+  n = length(Y)
+  
+  int <- sample.int(n, size = n, replace = TRUE)
+  X_train = X[int,]
+  Y_train = Y[int]
+  
+  alphas = seq(0, 1, by=0.1)
+  
+  # To store results
+  fit.cv <- list()
+  cvm = rep(0, length(alphas))
+  
+  # run elastic net with cross-validation and alpha search
+  for (i in 1:length(alphas)){
+    fit.cv[[i]] <- cv.glmnet(X_train, Y_train, alpha = alphas[i], nfolds = 5)
+    cvm[i] <- min(fit.cv[[i]]$cvm)
+  }
+  
+  opt.idx <- which.min(cvm)
+  fit.cv <- fit.cv[[opt.idx]]
+  
+  co <- as.vector(coef(fit.cv, s="lambda.min"))
+  
+  if (lambda.min == TRUE) {
+    pred_values = predict(fit.cv, newx = ext.X, type = "response", s = "lambda.min")      
+  }
+  if (lambda.min == FALSE) {
+    pred_values = predict(fit.cv, newx = ext.X, type = "response", s = "lambda.1se")      
+  }
+  cor <- suppressWarnings(cor(pred_values, ext.Y, method = method))
+  MSE <- mean((ext.Y - pred_values)^2)
+  return(list(cor=cor, co=co, MSE=MSE))
+}
+
[…]

### 2023-02-11 R_codeP01/scripts/06_elastic_rc_03.R

@@ -1,0 +1,282 @@
+###########################################################
+## Repeated cross-validation for testing the Lasso model ##
+###########################################################
+##
+## Test against the fold
+## Cross-validation (5-fold) used for training/tuning lambda and selecting features
+## output: selected genes; proliferation.score correlation; SEM
+
+## Post Lasso model is made at the bottom
+
+library(glmnet)
+library(caret)
+library(ggplot2)
+
+###########################################################
+##  Repeated cross validation ##
+###########################################################
+
+
+# Elastic base function returning a trained object
+# elastic_sample <- function(train_data){
+#   X_ <- as.matrix(train_data |> select(-1))
+#   Y_ <- as.matrix(train_data |>  select(1))
+#   # NB: NEED TO LOOK INTO the SETTINGS of Lasso
+#   # fit.cv <- cv.glmnet(X_, Y_, family = "gaussian", alpha = 1, standardize = TRUE, nlambda = 100, nfolds = 5)
+#   fit.cv <- cv.glmnet(X_, Y_, nfolds = 5)
+#   return(fit.cv)
+# }
+
+elastic_sample <- function(train_data, test_data, lambda.min=TRUE, method="pearson"){
+  # one bootstrap sample
+  # output: 
+  # 1. correlation between prediction and full input sample  (pearson or spearman should be set)
+  # 2. Coefficients of variables 
+  # 3. MSE
+  X_ <- as.matrix(train_data |> select(-1))
+  Y_ <- as.matrix(train_data |> select(1))
+  
+  ext.X <- as.matrix(test_data |> select(-1))
+  ext.Y <- as.matrix(test_data |> select(1))
+  
+  n = length(Y_)
+  
+  int <- sample.int(n, size = n, replace = TRUE)
+  X_train = X_[int,]
+  Y_train = Y_[int]
+  
+  alphas = seq(0, 1, by=0.1)
+  
+  # To store results
+  fit.cv <- list()
+  cvm = rep(0, length(alphas))
+  
+  # run elastic net with cross-validation and alpha search
+  for (i in 1:length(alphas)){
[…]

### 2023-02-11 R_codeP01/scripts/07_residual03.R

@@ -1,253 +1,0 @@
-###########################################################
-## Repeated cross-validation for testing the Lasso model ##
-###########################################################
-##
-## Test against the fold
-## Cross-validation (5-fold) used for training/tuning lambda and selecting features
-## output: selected genes; proliferation.score correlation; SEM
-
-## Post Lasso model is made at the bottom
-
-library(glmnet)
-library(caret)
-library(ggplot2)
-
-###########################################################
-##  Repeated cross validation ##
-###########################################################
-
-# Function: repeated k-fold cross validation
-lasso_residual_rep_cv <- function(df_data, pred_mech, additive=TRUE, func=lasso_sample, folds=5, repeats=200, method="pearson") {
-  n_models <- repeats * folds
-  print(n_models)
-  cor_vec <- rep(NA, n_models)
-  MSE_vec <- rep(NA, n_models)
-  coef_matrix <- matrix(NA, nrow = n_models, ncol = ncol(df_data[,-1]))
-  colnames(coef_matrix) <- colnames(df_data[, -1])
-  
-  coef_matrix_row_index <- 1
-  
-  pred_mech <- as.matrix(pred_mech)
-  
-  # calculating the residuals
-  if (additive==TRUE){res <- df_data$Y - pred_mech}
-  else{res <- df_data$Y / pred_mech}
-  
-  # create df with training data and update the training data with residuals instead of Y
-  df_train_res <- df_data
-  df_train_res$Y <- res
-  
-  # Repeat the cross-validation process
-  for (i in 1:repeats) {
-    # Create the folds for evaluating the performance
-    kf <- caret::createFolds(df_data[,1], k = folds, list = TRUE, returnTrain = TRUE)
-    # Loop through the folds
-    for (j in 1:folds) {
-      # Get the training and testing data: here picked from two different df
-      train_data_res <- df_train_res[kf[[j]],]
-      test_data <- df_data[-kf[[j]],]
-      
-      test_pred_mech <- pred_mech[-kf[[j]]]
-      
[…]

### 2023-02-11 R_codeP01/scripts/07_residual_lasso_rc_03.R

@@ -1,0 +1,253 @@
+###########################################################
+## Repeated cross-validation for testing the Lasso model ##
+###########################################################
+##
+## Test against the fold
+## Cross-validation (5-fold) used for training/tuning lambda and selecting features
+## output: selected genes; proliferation.score correlation; SEM
+
+## Post Lasso model is made at the bottom
+
+library(glmnet)
+library(caret)
+library(ggplot2)
+
+###########################################################
+##  Repeated cross validation ##
+###########################################################
+
+# Function: repeated k-fold cross validation
+lasso_residual_rep_cv <- function(df_data, pred_mech, additive=TRUE, func=lasso_sample, folds=5, repeats=200, method="pearson") {
+  n_models <- repeats * folds
+  print(n_models)
+  cor_vec <- rep(NA, n_models)
+  MSE_vec <- rep(NA, n_models)
+  coef_matrix <- matrix(NA, nrow = n_models, ncol = ncol(df_data[,-1]))
+  colnames(coef_matrix) <- colnames(df_data[, -1])
+  
+  coef_matrix_row_index <- 1
+  
+  pred_mech <- as.matrix(pred_mech)
+  
+  # calculating the residuals
+  if (additive==TRUE){res <- df_data$Y - pred_mech}
+  else{res <- df_data$Y / pred_mech}
+  
+  # create df with training data and update the training data with residuals instead of Y
+  df_train_res <- df_data
+  df_train_res$Y <- res
+  
+  # Repeat the cross-validation process
+  for (i in 1:repeats) {
+    # Create the folds for evaluating the performance
+    kf <- caret::createFolds(df_data[,1], k = folds, list = TRUE, returnTrain = TRUE)
+    # Loop through the folds
+    for (j in 1:folds) {
+      # Get the training and testing data: here picked from two different df
+      train_data_res <- df_train_res[kf[[j]],]
+      test_data <- df_data[-kf[[j]],]
+      
+      test_pred_mech <- pred_mech[-kf[[j]]]
+      
[…]

### 2023-02-11 R_codeP01/scripts/07_residual_xgboost_rc03.R

@@ -1,321 +1,0 @@
-#################################################################
-##  XGBoost on Repeated cross-validation ##
-#################################################################
-
-## Boosting using 5-fold cross validation to evaluate model
-## Base learners:
-## - btree
-## - (linear)
-## - (spline)
-## 
-## Test against folds
-## output: - vector with correlations 
-##         - matrix with features
-##         - vector with SEM
-##         - (vector with number of rounds used in each model)
-
-library(xgboost)
-library(Matrix)
-library(data.table)
-library(caret)
-library(ggplot2)
-
-# structure of base learners
-fm01 <- Y ~ CCND1 + CCNE1 + CDKN1A + ESR1 + MYC + RB1
-fm05 <- as.formula(paste("Y", paste(genes, collapse="+"), sep=" ~ "))
-
-XGBoost_sample <- function(fm, df_train) {
-  # Convert dataframe to dataMatrix to DMatrix object
-  train_sparse = sparse.model.matrix(object = fm, data = df_train)
-  dtrain = xgb.DMatrix(data = train_sparse, label = df_train$Y)
-
-  # param <- list(eta = 0.1, max_depth = 5)
-   param <- list(booster = "gbtree", 
-                objective = "reg:squarederror", 
-                eval_metric = "rmse", 
-                # nthread = 4, 
-                max_depth = 1, 
-                min_child_weight = 1,
-                tree_method = "hist",   # tree_methods=  exact, approx and hist, depending on the dataset size, memory and time constraints
-                #eta_decay=0.1,
-                eta=0.3)
- 
-  cv <- xgb.cv(data = dtrain, 
-               params = param, 
-               nrounds = 100, 
-               nfold = 5, 
-               #showsd = T, stratified = T,
-               print_every_n = 10,
-               early_stopping_rounds = 5,
-               verbose = FALSE)
-  
-  n_rounds <- cv$best_iteration
-  
-  xgb_model = xgb.train(data = dtrain,
-                        # The following is needed if to monitor training and validation error
[…]

### 2023-02-11 R_codeP01/scripts/07_residuals_lasso_boot01.R

@@ -75,6 +75,7 @@ pred_mech <- df_771genes_mech_pred.scaled_prolif$model_prediction
 # Here just testing if I can use the df01 directly:
 df_prolif_6genes <- select(df_771genes_mech_pred.scaled_prolif, -model_prediction)
 df_prolif_6genes <- select(df_prolif_6genes, c(Y, CCND1, CCNE1, CDKN1A, ESR1, MYC, RB1))
+
 set.seed(123)
 lb_obj_residuals_6_prolif  <- lasso_res_boot(df_prolif_6genes, df_prolif_6genes, pred_mech, additive=T, lasso_sample, method="pearson", n_bootstraps=1000)
 head(lb_obj_residuals_6_prolif$coef_matrix)[,1:6]
@@ -124,7 +125,7 @@ sd(lb_obj_residuals_771_RORprolif_a$cor_vec)
 
 # RUN: lb_obj_residuals_771_RORprolif_m (multiplicative)
 set.seed(123)
-lb_obj_residuals_771_RORprolif_m  <- lasso_res_boot(ROR_prolif_771genes, ROR_prolif_771genes, pred_mech, additive=T, lasso_sample, method="pearson", n_bootstraps=1000)
+lb_obj_residuals_771_RORprolif_m  <- lasso_res_boot(ROR_prolif_771genes, ROR_prolif_771genes, pred_mech, additive=F, lasso_sample, method="pearson", n_bootstraps=1000)
 head(lb_obj_residuals_771_RORprolif_m$coef_matrix)[,1:8]
 save(lb_obj_residuals_771_RORprolif_m, file="/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_residuals_771_RORprolif_m.RData")
 load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_residuals_771_RORprolif_m.RData")

### 2023-02-11 R_codeP01/scripts/90_output_ridge_01.R

@@ -1,0 +1,69 @@
+#################################
+## create outputs for report 2 ##
+#################################
+
+library(ggplot2)
+
+report02_out_ridge <- function(object){
+  cor_vec <- object$cor_vec
+  n_models <- length(cor_vec)
+  cat("number of models fitted:", n_models, "\n")
+  fr <- sum(is.na(cor_vec))/n_models
+  cat("Fraction of model fits with no selected genes:", fr, "\n")
+  cat("\n")
+  
+  ## Correlations
+  cat("CORRELATIONS RESULTS", "\n")
+  cor_mean <- mean(na.omit(cor_vec))
+  cat("Mean:", cor_mean, "\n") 
+  cor_median <- median(cor_vec, na.rm=TRUE)
+  cat("Median:", cor_median, "\n")
+  cor_var <- var(cor_vec, na.rm=TRUE)
+  cat("Variance:", cor_var, "\n")
+  cor_sd <- sd(na.omit(cor_vec)) 
+  cat("st.dev.:", cor_sd, "\n")
+  
+  # Histogram correlations
+  correlations_finite <- cor_vec[is.finite(cor_vec)]
+  cor_df <- data.frame(correlation = correlations_finite)
+  
+  h <- ggplot(cor_df, aes(x=correlation)) +
+    geom_histogram(bins = 30, color = "black", fill = "white") +
+    xlab("Correlation") +
+    ylab("Frequency") +
+    ggtitle("Histogram of Correlation Values")
+  show(h)
+  
+  ## MSE
+  cat("MSE RESULTS", "\n")
+  MSE_vec <- object$MSE_vec
+  MSE_mean <- mean(na.omit(MSE_vec))
+  cat("Mean:", MSE_mean, "\n") 
+  MSE_median <- median(MSE_vec, na.rm=TRUE)
+  cat("Median:", MSE_median, "\n")
+  MSE_var <- var(MSE_vec, na.rm=TRUE)
+  cat("Variance:", MSE_var, "\n")
+  MSE_sd <- sd(na.omit(MSE_vec)) 
+  cat("st.dev.:", MSE_sd)
+  
+  
+  # Histogram MSE
+  MSE_df <- data.frame(MSE = MSE_vec)
+  
+  h <- ggplot(MSE_df, aes(x=MSE)) +
+    geom_histogram(bins = 30, color = "black", fill = "white") +
+    xlab("MSE") +
+    ylab("Frequency") +
+    ggtitle("Histogram of MSE Values")
+  show(h)
[…]

### 2023-02-13 R_codeP01/reports/MS2_report02.Rmd
elastic

@@
 
-# Summery of results
+# Summery of all results
 ## Lasso proliferation score (bootstrap) 

### 2023-02-13 R_codeP01/scripts/01_dataclean01.R

@@ -98,7 +98,7 @@ length(genes)
 
 df_genes_with_output <- function(df, predictors, output){
   print(output)
-  print(length(genes))
+  print(length(predictors))
   features <- c("UniqueID", "timepoint", "TrialArmNeo", predictors)
   
   df_genes <- df |> select(all_of(features)) |>
@@ -111,7 +111,7 @@ df_genes_with_output <- function(df, predictors, output){
 
   df_out <- full_join(df_output, df_genes, by = "UniqueID")
   
-  colnames(df_out)[which(names(df_out) == output)] <- "Y"
+  colnames(df_out)[which(names(df_out) == all_of(output))] <- "Y"
   
   df_out <- df_out |> select(-c(UniqueID, timepoint.x, TrialArmNeo.x, timepoint.y, TrialArmNeo.y)) # remove unnecessary columns
   df_out <- na.omit(df_out) # remove rows with missing values
@@ -130,10 +130,10 @@ dfA03 <- Proliferation_ALLgenes |>
   select(- c(timepoint.x, TrialArmNeo.x, timepoint.y, TrialArmNeo.y))
 
 # Matrices for glmnet
-X <- as.matrix(prolif_771genes |> select(all_of(genes)))
+X <- as.matrix(prolif_771genes |> select(all_of(all_genes)))
 Y <- as.matrix(select(prolif_771genes, Y))
 
-X <- as.matrix(ROR_prolif_771genes |> select(all_of(genes)))
+X <- as.matrix(ROR_prolif_771genes |> select(all_of(all_genes)))
 Y <- as.matrix(select(ROR_prolif_771genes, Y))
 
 

### 2023-02-13 R_codeP01/scripts/06_elastic_boot_02.R

@@ -9,7 +9,6 @@
 
 library(glmnet)
 
-
 elastic_bootstrap_sample <- function(X, Y, ext.X, ext.Y, lambda.min=TRUE, method="pearson"){
   # one bootstrap sample
   # output: 

### 2023-02-13 R_codeP01/scripts/06_elastic_rc_03.R

@@ -79,8 +79,8 @@ elastic_rep_cv <- function(df_data, func=elastic_sample, folds=5, repeats=200, m
   print(n_models)
   cor_vec <- rep(NA, n_models)
   MSE_vec <- rep(NA, n_models)
-  co_matrix <- matrix(NA, nrow = n_models, ncol = ncol(df_data[,-1]))
-  colnames(co_matrix) <- colnames(df_data[, -1])
+  coef_matrix <- matrix(NA, nrow = n_models, ncol = ncol(df_data[,-1]))
+  colnames(coef_matrix) <- colnames(df_data[, -1])
   
   coef_matrix_row_index <- 1
   
@@ -97,14 +97,14 @@ elastic_rep_cv <- function(df_data, func=elastic_sample, folds=5, repeats=200, m
       # Run elastic net function and get results
       out <- func(train_data, test_data, lambda.min=TRUE, method="pearson")
       cor_vec[coef_matrix_row_index] <- out$cor
-      co_matrix[coef_matrix_row_index,] <- out$co[-1]
+      coef_matrix[coef_matrix_row_index,] <- out$co[-1]
       MSE_vec[coef_matrix_row_index] <- out$MSE
       
       cat(coef_matrix_row_index, "")
       coef_matrix_row_index <- coef_matrix_row_index + 1
     }
   }
-  return(list(cor_vec=cor_vec, co_matrix=co_matrix, MSE_vec=MSE_vec))
+  return(list(cor_vec=cor_vec, coef_matrix=coef_matrix, MSE_vec=MSE_vec))
 }
 
 # Set repeats and folds of the cross-validations
@@ -136,7 +136,7 @@ load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/e_c_obj_771_prol
 
 # RUN: e_c_obj_771_RORprolif
 set.seed(123)
-e_c_obj_771_RORprolif <- elastic_rep_cv(RORprolif_771genes, func=elastic_sample, folds, repeats, method="pearson")
+e_c_obj_771_RORprolif <- elastic_rep_cv(ROR_prolif_771genes, func=elastic_sample, folds, repeats, method="pearson")
 head(e_c_obj_771_RORprolif$coef_matrix)[,1:6]
 save(e_c_obj_771_RORprolif, file="/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/e_c_obj_771_RORprolif.RData")
[…]

### 2023-02-13 R_codeP01/scripts/09_xgboost02-b.R

@@ -13,10 +13,12 @@
 
 library(xgboost)
 library(Matrix)
+library(data.table)
+
 
 # structure of base learners
 fm01 <- Y ~ CCND1 + CCNE1 + CDKN1A + ESR1 + MYC + RB1
-fm05 <- as.formula(paste("Y", paste(genes, collapse="+"), sep=" ~ "))
+fm05 <- as.formula(paste("Y", paste(all_genes, collapse="+"), sep=" ~ "))
 
 XGBoost_sample <- function(fm, df_train) {
   # Convert the dataMatrix to a DMatrix object
@@ -59,7 +61,7 @@ XGBoost_sample <- function(fm, df_train) {
 t_ <- XGBoost_sample(fm01, Proliferation_6genes)
 
 # 1000 bootstrap fits
-XGboost_boot = function(fm, df_train, df_test, method="pearson", n_bootstraps=10){
+xgboost_boot = function(fm, df_train, df_test, method="pearson", n_bootstraps=1000){
   # run many bootstraps
   # output: - vector with correlations 
   #         - matrix with features
@@ -84,12 +86,9 @@ XGboost_boot = function(fm, df_train, df_test, method="pearson", n_bootstraps=10
     
     # Extract feature importance
     feature_importance <- data.table(xgb.importance(colnames(df_train), model = xgb_model))
-    print(feature_importance[,1:2])
+
     # Sum up the feature importance
     coef_matrix[i, feature_importance$Feature] <- 1
-    print(coef_matrix)
-
-    #coef_matrix[i, ] <- coef(fit, s = "lambda.min")[-1]
 
     pred = predict(object = xgb_model, newdata = d_validation)
     cor_vec[i] <- suppressWarnings(cor(pred, df_test$Y, method = method))
@@ -99,9 +98,26 @@ XGboost_boot = function(fm, df_train, df_test, method="pearson", n_bootstraps=10
     cat(i, "")
   }  
   #return(list(cor_vec=cor_vec, coef_matrix=coef_matrix, MSE_vec=MSE_vec, n_rounds_vec=n_rounds_vec))
-  return(list(cor_vec=cor_vec, MSE_vec=MSE_vec, n_rounds_vec=n_rounds_vec, 
-              coef_matrix=coef_matrix))
[…]

### 2023-02-13 R_codeP01/scripts/31_ensamble_block01.R

@@ -1,20 +1,28 @@
 #################################################################
 ##  Blocks for ensemble models ##
 #################################################################
-##
-## Base functions returning predicted values
 ## input: - train data
-##        - test data
-##        - formula defining the signatures if necessary
+##        - formula defining the signatures
 ## output: perdition Y
 
 library(xgboost)
+library(glmnet)
 library(Matrix)
 library(data.table)
 
+lasso_block <- function(train_data, test_data){
+  X_ <- as.matrix(train_data |> select(-1))
+  Y_ <- as.matrix(train_data |>  select(1))
+  # NB: NEED TO LOOK INTO the SETTINGS of Lasso
+  # fit.cv <- cv.glmnet(X_, Y_, family = "gaussian", alpha = 1, standardize = TRUE, nlambda = 100, nfolds = 5)
+  fit.cv <- cv.glmnet(X_, Y_, nfolds = 5)
+  pred = predict(fit.cv, newx = as.matrix(test_data)[,-1], type = "response", s = "lambda.min")
+  return(pred)
+}
 
 
-XGBoost_sample <- function(fm, df_train, test_data) {
+
+XGBoost_block <- function(fm, df_train) {
   # Convert dataframe to dataMatrix to DMatrix object
   train_sparse = sparse.model.matrix(object = fm, data = df_train)
   dtrain = xgb.DMatrix(data = train_sparse, label = df_train$Y)

### 2023-02-13 R_codeP01/scripts/09_xgboost02-b.R
som small corrections

@@ -110,12 +110,12 @@ head(xg_b_obj_771_p$coef_matrix)[,1:6]
 save(xg_b_obj_771_p, file="/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/xg_b_obj_771_p.RData")
 load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/xg_b_obj_771_p.RData")
 
-# RUN: e_b_obj_771_ROR_p
+# RUN: xg_b_obj_771_ROR_p
 set.seed(123)
-e_b_obj_771_ROR_p <- xgboost_boot(fm=fm05, ROR_prolif_771genes, ROR_prolif_771genes, method="pearson", n_bootstraps=1000)
-head(e_b_obj_771_ROR_p$coef_matrix)[,1:6]
-save(e_b_obj_771_ROR_p, file="/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/e_b_obj_771_ROR_p.RData")
-load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/e_b_obj_771_ROR_p.RData")
+xg_b_obj_771_ROR_p <- xgboost_boot(fm=fm05, ROR_prolif_771genes, ROR_prolif_771genes, method="pearson", n_bootstraps=1000)
+head(xg_b_obj_771_ROR_p$coef_matrix)[,1:6]
+save(xg_b_obj_771_ROR_p, file="/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/xg_b_obj_771_ROR_p.RData")
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/xg_b_obj_771_ROR_p.RData")
 
 
 

### 2023-02-13 R_codeP01/scripts/09_xgboost03.R

@@ -125,7 +125,7 @@ folds = 5
 
 # RUN: xc_obj_6_prolif
 set.seed(123)
-xc_obj_6_prolif <- lasso_rep_cv(prolif_6genes, func=lasso_sample, folds, repeats, method="pearson")
+xc_obj_6_prolif <- _rep_cv(prolif_6genes, func=, folds, repeats, method="pearson")
 head(xc_obj_6_prolif$coef_matrix)[,1:6]
 save(xc_obj_6_prolif, file="/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/xc_obj_6_prolif.RData")
 load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/xc_obj_6_prolif.RData")
@@ -134,7 +134,7 @@ sd(xc_obj_6_prolif$cor_vec)
 
 # RUN: xc_obj_6_RORprolif
 set.seed(123)
-xc_obj_6_RORprolif <- lasso_rep_cv(RORprolif_6genes, func=lasso_sample, folds, repeats, method="pearson")
+xc_obj_6_RORprolif <- _rep_cv(RORprolif_6genes, func=, folds, repeats, method="pearson")
 head(xc_obj_6_RORprolif$coef_matrix)[,1:6]
 save(xc_obj_6_RORprolif, file="/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/xc_obj_6_RORprolif.RData")
 load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/xc_obj_6_RORprolif.RData")
@@ -142,28 +142,28 @@ mean(xc_obj_6_RORprolif$cor_vec)
 sd(xc_obj_6_RORprolif$cor_vec)
 
 
-# RUN: xc_obj_771_prolif
+# RUN: xg_c_obj_771_prolif
 set.seed(123)
-xc_obj_771_prolif <- lasso_rep_cv(prolif_771genes, func=lasso_sample, folds, repeats, method="pearson")
-head(xc_obj_771_prolif$coef_matrix)[,1:8]
-save(xc_obj_771_prolif, file="/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/xc_obj_771_prolif.RData")
-load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/xc_obj_771_prolif.RData")
-mean(xc_obj_771_prolif$cor_vec)
[…]

### 2023-02-14 R_codeP01/reports/MS2_report02.Rmd
PCA and Staking olmoat finised

--- 2023-02-11 R_codeP01/reports/MS2_report02.Rmd
@@
 
-# Boosting with stumps as base learner
+# Boosting with stumps as base learner - bootstrap
+### 771 genes -> proliferation score
+```{r}
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/xg_b_obj_771_p.RData")
+xg_b_771_p <- report02_out_ridge(xg_b_obj_771_p)
+```
+### 771 genes -> ROR-proliferation score
+```{r}
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/xg_b_obj_771_ROR_p.RData")
+xg_b_771_ROR_p <- report02_out_ridge(xg_b_obj_771_ROR_p)
+```
+
+# Boosting with stumps as base learner cross-validation
+### 771 genes -> proliferation score
+```{r}
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/xg_c_obj_771_prolif.RData")
+xg_c_771_p <- report02_out_ridge(xg_c_obj_771_prolif)
+```
+### 771 genes -> ROR-proliferation score
+```{r}
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/xg_c_obj_771_RORprolif.RData")
+xg_c_771_ROR_p <- report02_out_ridge(xg_c_obj_771_RORprolif)
+```
+
+### Summery results: Boosting with stumps 771 genes bootstrap and repeated cross-validation
+```{r}
+data_table <- data.frame(
+  Model = c("prolif boot", "ROR-prolif boot", "prolif rep cross-val", "ROR-prolif rep cross-val"),
+  cor_mean = c(xg_b_771_p$cor_mean, xg_b_771_ROR_p$cor_mean, xg_c_771_p$cor_mean, xg_c_771_ROR_p$cor_mean),
+  sd_cor = c(xg_b_771_p$cor_sd, xg_b_771_ROR_p$cor_sd, xg_c_771_p$cor_sd, xg_c_771_ROR_p$cor_sd),
+  MSE_mean = c(xg_b_771_p$MSE_mean, xg_b_771_ROR_p$MSE_mean, xg_c_771_p$MSE_mean, xg_c_771_ROR_p$MSE_mean),
+  MSE_sd = c(xg_b_771_p$MSE_sd, xg_b_771_ROR_p$MSE_sd, xg_c_771_p$MSE_sd, xg_c_771_ROR_p$MSE_sd)
+)
+kable(data_table)
+```
 
 # Post Lasso
+not done
 
-# Summery of results
-## Lasso proliferation score (bootstrap) 
+# Summery of all results
+### Summery results: lasso proliferation score (bootstrap) 
 ```{r}
+library(knitr)
 data_table <- data.frame(
@@
 ```
+### Summery results: lasso ROR+proliferation score (bootstrap) 
+```{r}
+data_table <- data.frame(
+  Model = c("lasso 6 genes", "lasso 771 genes", "Nodes", "Residual additive", "Residual multiplicative"),
+  cor_mean = c(l_b_6_ROR_p$cor_mean, l_b_771_ROR_p$cor_mean, l_b_nodes_ROR_p$cor_mean, l_b_residuals_ROR_p_a$cor_mean, l_b_residuals_ROR_p_m$cor_mean),
+  sd_cor = c(l_b_6_ROR_p$cor_sd, l_b_771_ROR_p$cor_sd, l_b_nodes_ROR_p$cor_sd, l_b_residuals_ROR_p_a$cor_sd, l_b_residuals_ROR_p_m$cor_sd),
+  MSE_mean = c(l_b_6_ROR_p$MSE_mean, l_b_771_ROR_p$MSE_mean, l_b_nodes_ROR_p$MSE_mean, l_b_residuals_ROR_p_a$MSE_mean, l_b_residuals_ROR_p_m$MSE_mean),
+  MSE_sd = c(l_b_6_ROR_p$MSE_sd, l_b_771_ROR_p$MSE_sd, l_b_nodes_ROR_p$MSE_sd, l_b_residuals_ROR_p_a$MSE_sd, l_b_residuals_ROR_p_m$MSE_sd)
+)
+kable(data_table)
+```
+### Summery results: lasso proliferation score (repeated cross-validation) 
+```{r}
+library(knitr)
+data_table <- data.frame(
+  Model = c("lasso 6 genes", "lasso 771 genes", "Nodes", "Residual additive", "Residual multiplicative"),
+  cor_mean = c(l_c_6_p$cor_mean, l_c_771_p$cor_mean, l_c_nodes_p$cor_mean, l_c_residuals_771_p_a$cor_mean, l_c_residuals_771_p_m$cor_mean),
+  sd_cor = c(l_c_6_p$cor_sd, l_c_771_p$cor_sd, l_c_nodes_p$cor_sd, l_c_residuals_771_p_a$cor_sd, l_c_residuals_771_p_m$cor_sd),
+  MSE_mean = c(l_c_6_p$MSE_mean, l_b_771_p$MSE_mean, l_c_nodes_p$MSE_mean, l_c_residuals_771_p_a$MSE_mean, l_c_residuals_771_p_m$MSE_mean),
+  MSE_sd = c(l_c_6_p$MSE_sd, l_c_771_p$MSE_sd, l_c_nodes_p$MSE_sd, l_c_residuals_771_p_a$MSE_sd, l_c_residuals_771_p_m$MSE_sd)
+)
+kable(data_table)
+```
+### Summery results: lasso ROR+proliferation score (repeated cross-validation) 
+```{r}
+data_table <- data.frame(
+  Model = c("lasso 6 genes", "lasso 771 genes", "Nodes", "Residual additive", "Residual multiplicative"),
+  cor_mean = c(l_c_6_ROR_p$cor_mean, l_c_771_ROR_p$cor_mean, l_c_nodes_ROR_p$cor_mean, l_c_residuals_ROR_p_a$cor_mean, l_c_residuals_ROR_p_m$cor_mean),
+  sd_cor = c(l_c_6_ROR_p$cor_sd, l_c_771_ROR_p$cor_sd, l_c_nodes_ROR_p$cor_sd, l_c_residuals_ROR_p_a$cor_sd, l_c_residuals_ROR_p_m$cor_sd),
+  MSE_mean = c(l_c_6_ROR_p$MSE_mean, l_c_771_ROR_p$MSE_mean, l_c_nodes_ROR_p$MSE_mean, l_c_residuals_ROR_p_a$MSE_mean, l_c_residuals_ROR_p_m$MSE_mean),
+  MSE_sd = c(l_c_6_ROR_p$MSE_sd, l_c_771_ROR_p$MSE_sd, l_c_nodes_ROR_p$MSE_sd, l_c_residuals_ROR_p_a$MSE_sd, l_c_residuals_ROR_p_m$MSE_sd)
+)
+kable(data_table)
+```
+
+### Summery results: ridge 771 genes bootstrap and repeated cross-validation
+```{r}
+data_table <- data.frame(
+  Model = c("prolif boot", "ROR-prolif boot", "prolif rep cross-val", "ROR-prolif rep cross-val"),
+  cor_mean = c(r_b_771_p$cor_mean, r_b_771_ROR_p$cor_mean, r_c_771_p$cor_mean, r_c_771_ROR_p$cor_mean),
+  sd_cor = c(r_b_771_p$cor_sd, r_b_771_ROR_p$cor_sd, r_c_771_p$cor_sd, r_c_771_ROR_p$cor_sd),
+  MSE_mean = c(r_b_771_p$MSE_mean, r_b_771_ROR_p$MSE_mean, r_c_771_p$MSE_mean, r_c_771_ROR_p$MSE_mean),
+  MSE_sd = c(r_b_771_p$MSE_sd, r_b_771_ROR_p$MSE_sd, r_c_771_p$MSE_sd, r_c_771_ROR_p$MSE_sd)
+)
+kable(data_table)
+```
+### Summery results: elastic net 771 genes bootstrap and repeated cross-validation
+```{r}
+data_table <- data.frame(
+  Model = c("prolif boot", "ROR-prolif boot", "prolif rep cross-val", "ROR-prolif rep cross-val"),
+  cor_mean = c(e_b_771_p$cor_mean, e_b_771_ROR_p$cor_mean, e_c_771_p$cor_mean, e_c_771_ROR_p$cor_mean),
+  sd_cor = c(e_b_771_p$cor_sd, e_b_771_ROR_p$cor_sd, e_c_771_p$cor_sd, e_c_771_ROR_p$cor_sd),
+  MSE_mean = c(e_b_771_p$MSE_mean, e_b_771_ROR_p$MSE_mean, e_c_771_p$MSE_mean, e_c_771_ROR_p$MSE_mean),
+  MSE_sd = c(e_b_771_p$MSE_sd, e_b_771_ROR_p$MSE_sd, e_c_771_p$MSE_sd, e_c_771_ROR_p$MSE_sd)
+)
+kable(data_table)
+```
+### Summery results: Boosting with stumps 771 genes bootstrap and repeated cross-validation
+```{r}
+data_table <- data.frame(
+  Model = c("prolif boot", "ROR-prolif boot", "prolif rep cross-val", "ROR-prolif rep cross-val"),
+  cor_mean = c(xg_b_771_p$cor_mean, xg_b_771_ROR_p$cor_mean, xg_c_771_p$cor_mean, xg_c_771_ROR_p$cor_mean),
+  sd_cor = c(xg_b_771_p$cor_sd, xg_b_771_ROR_p$cor_sd, xg_c_771_p$cor_sd, xg_c_771_ROR_p$cor_sd),
+  MSE_mean = c(xg_b_771_p$MSE_mean, xg_b_771_ROR_p$MSE_mean, xg_c_771_p$MSE_mean, xg_c_771_ROR_p$MSE_mean),
+  MSE_sd = c(xg_b_771_p$MSE_sd, xg_b_771_ROR_p$MSE_sd, xg_c_771_p$MSE_sd, xg_c_771_ROR_p$MSE_sd)
+)
+kable(data_table)
+```

### 2023-02-14 R_codeP01/scripts/09_xgboost03.R

@@ -67,12 +67,13 @@ XGBoost_sample(fm01, prolif_6genes)
 XGboost_rep_cv = function(fm, df_data, folds=5, repeats=200, method="pearson"){
   n_models <- repeats * folds
   print(n_models)
+  print(dim(df_data))
   
   cor_vec <- rep(NA, n_models)
   MSE_vec <- rep(NA, n_models)
   n_rounds_vec <- integer(length = n_models)
   
-  coef_matrix <- matrix(NA, nrow = n_models, ncol = ncol(df_data)-1)
+  coef_matrix <- matrix(NA, nrow = n_models, ncol = (ncol(df_data)-1))
   colnames(coef_matrix) <- colnames(df_data[, -1])
   
   coef_matrix_row_index <- 1
@@ -115,7 +116,7 @@ XGboost_rep_cv = function(fm, df_data, folds=5, repeats=200, method="pearson"){
   return(list(cor_vec=cor_vec, MSE_vec=MSE_vec, coef_matrix=coef_matrix, n_rounds_vec=n_rounds_vec))
 }
 
-bb_object_t <- XGboost_rep_cv(fm01, prolif_6genes, folds=5, repeats=2)
+bb_object_t <- XGboost_rep_cv(fm05, prolif_771genes, folds=5, repeats=2)
 bb_object_t
 
 
@@ -144,7 +145,7 @@ sd(xc_obj_6_RORprolif$cor_vec)
 
 # RUN: xg_c_obj_771_prolif
 set.seed(123)
-xg_c_obj_771_prolif <- XGBoost_rep_cv(prolif_771genes, folds, repeats, method="pearson")
+xg_c_obj_771_prolif <- XGboost_rep_cv(fm05, prolif_771genes, folds, repeats, method="pearson")
 head(xg_c_obj_771_prolif$coef_matrix)[,1:8]
 save(xg_c_obj_771_prolif, file="/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/xg_c_obj_771_prolif.RData")
 load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/xg_c_obj_771_prolif.RData")
@@ -153,7 +154,7 @@ sd(xg_c_obj_771_prolif$cor_vec)
 
 # RUN: xg_c_obj_771_RORprolif
 set.seed(123)
[…]

### 2023-02-14 R_codeP01/scripts/32_ensemble_PCA_02.R

@@ -1,7 +1,7 @@
 ###################################################################
 ## Repeated cross-validation for testing the PCA-Ensemble models ##
 ###################################################################
-##
+##THERE IS NEWER VERSION OF THIS CODE (but this workes)
 ## Test against the fold
 ## Cross-validation (5-fold) used for training/tuning lambda and selecting features
 ## output: selected genes; proliferation.score correlation; SEM
@@ -19,7 +19,7 @@ library(stringr)
 ##  Repeated cross validation ##
 ###########################################################
 
-pca_results <- function(name, characters, data, percentage=0.9){
+pca_components<- function(name, characters, data, percentage=0.9){
   sign_data <-  data[, characters]
   pca_results <- prcomp(sign_data, scale = TRUE, center=TRUE) # create PCA object
   # Get the number of components that explain at least 90 % of the variance
@@ -39,6 +39,30 @@ lasso_sample <- function(train_data){
   fit.cv <- cv.glmnet(X_, Y_, nfolds = 5)
   return(fit.cv)
 }
+
+# PCA's:
+
+char_list <- list(imm_inf_ = char_immune_inf,
+                  prolif_ = char_prolif,
+                  ER_sing_ = char_ER_signaling,
+                  anti_pres_ = char_antigen_present,
+                  angiogen_ = char_angiogenesis
+                  )
+
+
+pca_as_features <- function(named_list, df_data, percentage=0.9){
+  df_Y_PCA <- data.frame(Y=df_data[,1])
+  for (key in names(named_list)) {
+    char_matrix <- named_list[[key]]
+    df_ <- pca_components(key, char_matrix, data=df_data, percentage=0.9)
+    df_Y_PCA <- cbind(df_Y_PCA, df_)
+
+  }
+  return(df_Y_PCA)
+}
+t <-pca_as_features(char_list, prolif_771genes)
+
+
 
 # Function: repeated k-fold cross validation
 lasso_PCA_rep_cv <- function(df_data, folds=5, repeats=1, method="pearson") {

### 2023-02-14 R_codeP01/scripts/32_ensemble_PCA_03.R

@@ -1,0 +1,124 @@
+###################################################################
+## Repeated cross-validation for testing the PCA-Ensemble models ##
+###################################################################
+##
+## Test against the fold
+## Cross-validation (5-fold) used for training/tuning lambda and selecting features
+## output: selected genes; proliferation.score correlation; SEM
+
+## Post Lasso model is made at the bottom
+library(stats)
+library(caret)
+library(glmnet)
+library(ggplot2)
+library(dplyr)
+library(stringr)
+
+
+###########################################################
+##  Repeated cross validation ##
+###########################################################
+
+pca_components<- function(name, characters, data, percentage=0.9){
+  sign_data <-  data[, characters]
+  pca_results <- prcomp(sign_data, scale = TRUE, center=TRUE) # create PCA object
+  # Get the number of components that explain at least 90 % of the variance
+  n_components <- sum(pca_results$sdev^2 / sum(pca_results$sdev^2) >= (1-percentage))
+  # Extract the first n_components principal components
+  df_important_pca <- data.frame(pca_results$x[, 1:n_components])
+  colnames(df_important_pca) <- c(paste0(name, 1:n_components))
+  return(df_important_pca)
+}
+
+# Lasso base function returning a trained object
+lasso_sample <- function(train_data){
+  X_ <- as.matrix(train_data |> select(-1))
+  Y_ <- as.matrix(train_data |>  select(1))
+  # NB: NEED TO LOOK INTO the SETTINGS of Lasso
+  # fit.cv <- cv.glmnet(X_, Y_, family = "gaussian", alpha = 1, standardize = TRUE, nlambda = 100, nfolds = 5)
+  fit.cv <- cv.glmnet(X_, Y_, nfolds = 5)
+  return(fit.cv)
+}
+
+# PCA's:
+char_list <- list(imm_inf_ = char_immune_inf,
+                  prolif_ = char_prolif,
+                  ER_sing_ = char_ER_signaling,
+                  anti_pres_ = char_antigen_present,
+                  angiogen_ = char_angiogenesis
+                  )
[…]

### 2023-02-14 R_codeP01/scripts/33_ensemble_stack_02.R

@@ -1,7 +1,7 @@
 ###################################################################
 ## Repeated cross-validation for testing the Stacking - Ensemble models ##
 ###################################################################
-##
+## EXIST NEWER VAERSION
 ## Test against the fold
 ## Cross-validation (5-fold) used for training/tuning lambda and selecting features
 ## output: selected genes; proliferation.score correlation; SEM

### 2023-02-14 R_codeP01/scripts/33_ensemble_stack_03.R

@@ -1,0 +1,168 @@
+###################################################################
+## Repeated cross-validation for testing the Stacking - Ensemble models ##
+###################################################################
+##
+## Test against the fold
+## Cross-validation (5-fold) used for training/tuning lambda and selecting features
+## output: selected genes; proliferation.score correlation; SEM
+
+library(caret)
+library(glmnet)
+library(ggplot2)
+
+
+# Name list og gene signature sets 
+char_list <- list(imm_inf_ = char_immune_inf,
+                  prolif_ = char_prolif,
+                  ER_sing_ = char_ER_signaling,
+                  anti_pres_ = char_antigen_present,
+                  angiogen_ = char_angiogenesis
+)
+
+# function to calculate new feature set from level 0 learners
+level_0_model <- function(named_list, train_data){
+  pred_y_L0 <- data.frame(Y=train_data$Y)
+  fits <- list()
+  
+  for (key in names(named_list)) {
+    char_matrix <- named_list[[key]]
+    X_ <- as.matrix(train_data[c(char_matrix)])
+    fit_ <- cv.glmnet(X_, train_data$Y, nfolds=5)
+    pred_ = predict(fit_, newx = X_, type = "response", s = "lambda.min")
+    colnames(pred_) <- key
+    pred_y_L0 <- cbind(pred_y_L0, pred_)
+    
+    fits[[key]] <- fit_
+
+  }
+  return(list(pred_y_L0=pred_y_L0, fits=fits))
+}
+t <-level_0(char_list, prolif_771genes)
+class(t)
+
+# function to calculate predictions of the level 0 models
+level_0_test <- function(named_list, test_data, fits){
+  pred_test_L0 <- data.frame(Y=test_data$Y)
+  
+  for (key in names(named_list)) {
+    char_matrix <- named_list[[key]]
+    X_ <- as.matrix(test_data[c(char_matrix)])
+    fit_ <- fits[[key]]
+    test_pred = predict(fit_, newx = X_, type = "response", s = "lambda.min")
+    colnames(test_pred) <- key
+    pred_test_L0[key] <- test_pred
+  }
+  return(pred_test_L0)
+}
+
+t1 <- level_0_test(char_list, prolif_771genes, t$fit)
+
+
+# Function: repeated k-fold cross validation
+lasso_rep_cv <- function(df_data, named_list, folds=5, repeats=1, method="pearson") {
+  n_models <- repeats * folds
+  print(n_models)
[…]

### 2023-03-22 R_codeP01/scripts/40_iterative_06.R
working with syntetic data on iterative

@@ -86,7 +86,7 @@ elastic_net_interaction <- function(x_df, y, groups, alpha = 0.5, lambda_seq = N
     obj_diff <- c(obj_diff, mean(abs(new_betas - betas)))
     # print(mean(abs(new_betas - betas)))
     
-    if (mean(abs(new_beta_main - beta_main)) < tol && mean(abs(new_betas[-(1:ncol(x))] - betas[-(1:ncol(x))])) < tol*100) {  # Only check convergence for the betas without interaction terms
+    if (max(abs(new_beta_main - beta_main)) < tol ) {  # Only check convergence for the betas without interaction terms
       converged <- TRUE
     } else {
       beta_main <- new_beta_main
@@ -107,7 +107,6 @@ elastic_net_interaction <- function(x_df, y, groups, alpha = 0.5, lambda_seq = N
   named_beta_interaction <- setNames(beta_interaction, interaction_names)
   
   return(list(obj_diff=obj_diff, beta_main = named_beta_main, beta_interaction = named_beta_interaction, iterations = iter, best_lambda = best_lambda))
-  # return(list(beta_main = beta_main, beta_interaction = beta_interaction, iterations = iter, best_lambda = best_lambda))
 }
 
 # Create a synthetic dataset with some interaction effect

### 2023-03-22 R_codeP01/scripts/40_iterative_07.R

@@ -5,7 +5,6 @@ elastic_net_interaction <- function(x_df, y, groups, alpha = 0.5, lambda_seq = N
 
   x <- as.matrix(x_df)
   
-  
   # Create a list of groups, each group containing the column indices of x corresponding to the feature names in char_list
   groups <- lapply(char_list, function(char_group) {
     sapply(char_group, function(feature_name) which(colnames(x_df) == feature_name))
@@ -69,11 +68,18 @@ elastic_net_interaction <- function(x_df, y, groups, alpha = 0.5, lambda_seq = N
 
     new_beta_main <- new_betas[1:ncol(x)]
     obj_diff <- c(obj_diff, mean(abs(new_betas - betas)))
-
     
-    if (mean(abs(new_beta_main - beta_main)) < tol && mean(abs(new_betas[-(1:ncol(x))] - betas[-(1:ncol(x))])) < tol*100) {  # Only check convergence for the betas without interaction terms
-      converged <- TRUE
-    } else {
+    if (!any(new_beta_main != 0))
+      stop("Warning: all beta manins are zero!")
+    
+    beta_main0 <- beta_main[beta_main != 0]
+    new_beta_main0 <- new_beta_main[new_beta_main != 0]
+    
+    # if (mean(abs(new_beta_main - beta_main)) < tol && mean(abs(new_betas[-(1:ncol(x))] - betas[-(1:ncol(x))])) < tol*100) {  # Only check convergence for the betas without interaction terms
+    if (max(abs(new_beta_main0 - beta_main0)) < tol ) {  # Only check convergence for the betas without interaction terms
+        converged <- TRUE
+    } 
+    else {
       beta_main <- new_beta_main
       betas <- new_betas  # Update betas only if not converged
     }
@@ -95,10 +101,66 @@ elastic_net_interaction <- function(x_df, y, groups, alpha = 0.5, lambda_seq = N
   # return(list(beta_main = beta_main, beta_interaction = beta_interaction, iterations = iter, best_lambda = best_lambda))
 }
 
+
+
 # Create a synthetic dataset with some interaction effect
 set.seed(42)
 n <- 100
 p <- 20
+
+X_df <- matrix(rnorm(n * p), n, p)
+colnames(X_df) <- paste0("X", 1:p)
+
[…]

### 2023-03-22 R_codeP01/scripts/40_iterative_07_zz2.R

@@ -72,13 +72,29 @@ elastic_net_interaction <- function(x_df, y, groups, alpha = 0.5, lambda_seq = N
 
     new_beta_main <- new_betas[1:ncol(x)]
     
-    best_lambda_idx <- which(fit_with_interactions$lambda == best_lambda)
-    dev_glmnet_curr <-  (1 - fit_with_interactions$glmnet$dev.ratio[best_lambda_idx]) * fit_with_interactions$glmnet$nulldev
-    obj_dev <- abs(dev_glmnet_curr - dev_glmnet)/dev_glmnet_curr
-    if ( obj_dev < tol ) {  # Only check convergence for the betas without interaction terms
+    # best_lambda_idx <- which(fit_with_interactions$lambda == best_lambda)
+    # dev_glmnet_curr <-  (1 - fit_with_interactions$glmnet$dev.ratio[best_lambda_idx]) * fit_with_interactions$glmnet$nulldev
+    # obj_dev <- abs(dev_glmnet_curr - dev_glmnet)/dev_glmnet_curr
+    # if ( obj_dev < tol ) {  # Only check convergence for the betas without interaction terms
+    #   converged <- TRUE
+    # } else {
+    #   dev_glmnet <- dev_glmnet_curr
+    #   beta_main <- new_beta_main
+    #   betas <- new_betas  # Update betas only if not converged
+    # }
+    # 
+    if (!any(new_beta_main != 0) && iter > 10)
+      stop("Warning: all beta manins are zero!")
+    
+    beta_main0 <- beta_main[beta_main != 0]
+    new_beta_main0 <- new_beta_main[new_beta_main != 0]
+    
+    # if (mean(abs(new_beta_main - beta_main)) < tol && mean(abs(new_betas[-(1:ncol(x))] - betas[-(1:ncol(x))])) < tol*100) {  # Only check convergence for the betas without interaction terms
+    if (length(beta_main0) > 0 && length(new_beta_main0) > 0) {  # Only check convergence for the betas without interaction terms
+      if (max(abs(new_beta_main0 - beta_main0)) < tol )
       converged <- TRUE
-    } else {
-      dev_glmnet <- dev_glmnet_curr
+    } 
+    else {
       beta_main <- new_beta_main
       betas <- new_betas  # Update betas only if not converged
     }

### 2023-03-22 R_codeP01/reports/MS2_report02.Rmd
PCA in report

@@
 
+# START USING DOMAIN KNOWLEDGE
+
+# PCA on signature gene sets, cross-validation
+### Ridge: 771 genes -> ROR-proliferation score
+```{r}
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/r_pca_c_771_RORprolif.RData")
+r_pca_c_771_RORprolif <- report02_out_ridge(r_pca_c_771_RORprolif)
+```
+
+### Ridge: 771 genes -> ROR-proliferation score + interactions between PCs
+```{r}
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/r_pca_c_interact_771_RORprolif.RData")
+r_pca_c_interact_771_RORprolif <- report02_out_ridge(r_pca_c_interact_771_RORprolif)
+```
+
+### Lasso: 771 genes -> ROR-proliferation score
+```{r}
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/l_pca_c_771_RORprolif.RData")
+l_pca_c_771_RORprolif <- report02_out(l_pca_c_771_RORprolif)
+```
+
+### Lasso: 771 genes -> ROR-proliferation score + interactions between PCs
+```{r}
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/l_pca_c_interact_771_RORprolif.RData")
+l_pca_c_interact_771_RORprolif <- report02_out(l_pca_c_interact_771_RORprolif)
+```
+
+### ElasticNet: 771 genes -> ROR-proliferation score
+```{r}
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/en_pca_c_771_RORprolif.RData")
+en_pca_c_771_RORprolif <- report02_out(en_pca_c_771_RORprolif)
+```
+
+### ElasticNet: 771 genes -> ROR-proliferation score + interactions between PCs
+```{r}
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/en_pca_c_interact_771_RORprolif.RData")
+en_pca_c_interact_771_RORprolif <- report02_out(en_pca_c_interact_771_RORprolif)
+```
+
+LAGE TABELLER HER
+
 # Post Lasso
@@
 ```
+
+### Summery results: Boosting with stumps 771 genes bootstrap and repeated cross-validation
+```{r}
+data_table <- data.frame(
+  Model = c("prolif boot", "ROR-prolif boot", "prolif rep cross-val", "ROR-prolif rep cross-val"),
+  cor_mean = c(xg_b_771_p$cor_mean, xg_b_771_ROR_p$cor_mean, xg_c_771_p$cor_mean, xg_c_771_ROR_p$cor_mean),
+  sd_cor = c(xg_b_771_p$cor_sd, xg_b_771_ROR_p$cor_sd, xg_c_771_p$cor_sd, xg_c_771_ROR_p$cor_sd),
+  MSE_mean = c(xg_b_771_p$MSE_mean, xg_b_771_ROR_p$MSE_mean, xg_c_771_p$MSE_mean, xg_c_771_ROR_p$MSE_mean),
+  MSE_sd = c(xg_b_771_p$MSE_sd, xg_b_771_ROR_p$MSE_sd, xg_c_771_p$MSE_sd, xg_c_771_ROR_p$MSE_sd)
+)
+kable(data_table)
+```

### 2023-03-22 R_codeP01/scripts/01_dataclean01.R

@@ -94,7 +94,7 @@ all_genes <- colnames(df01 |> select(41:811))
 # just for testing with fewer features
 test_genes <- colnames(df01 |> select(41:46))
 
-length(genes)
+length(all_genes)
 
 df_genes_with_output <- function(df, predictors, output){
   print(output)
@@ -124,6 +124,7 @@ ROR_prolif_771genes <- df_genes_with_output(df01, all_genes, "ROR_P_Subtype_Prol
 head(prolif_771genes[,1:5])
 lastcol <- ncol(prolif_771genes)
 head(prolif_771genes[, (lastcol-5): lastcol])
+
 
 # dataframe for caret
 dfA03 <- Proliferation_ALLgenes |> 

### 2023-03-22 R_codeP01/scripts/32_ensemble_PCA_03.R

@@ -86,7 +86,7 @@ t <-pca_as_features_interaction(char_list, prolif_771genes)
 t <-pca_as_features(char_list, prolif_771genes)
 
 
-# Lasso function returning a trained object
+# Lasso function returning a trained object DONT NEED:just change alpha value in elastic net function
 lasso_sample <- function(train_data){
   X_ <- as.matrix(train_data |> select(-1))
   Y_ <- as.matrix(train_data |>  select(1))
@@ -97,23 +97,22 @@ lasso_sample <- function(train_data){
   return(fit.cv)
 }
 
-
 # Elastic Net function returning a trained object
-elastic_net_sample <- function(train_data){
+elastic_net_sample <- function(train_data, alpha){
   X_ <- as.matrix(train_data |> select(-1))
   Y_ <- as.matrix(train_data |>  select(1))
   # Fit the model with elastic net regularization
-  fit.en <- glmnet(X_, Y_, family = "gaussian", alpha = 0.5, standardize = TRUE, nlambda = 100, nfolds = 5)
+  fit.en <- glmnet(X_, Y_, family = "gaussian", alpha=alpha, standardize = TRUE, nlambda = 100, nfolds = 5)
   # Perform cross-validation to select the best model
-  fit.cv <- cv.glmnet(X_, Y_, lambda = fit.en$lambda, alpha = 0.5, nfolds = 5)
+  fit.cv <- cv.glmnet(X_, Y_, lambda = fit.en$lambda, alpha=alpha, nfolds = 5)
   return(fit.cv)
 }
 
-
 # Function: repeated k-fold cross validation: NEED TO select if interaction terms or not
-lasso_PCA_rep_cv <- function(df_data, folds=5, repeats=1, interactions=FALSE, method="pearson", model) {
+PCA_rep_cv <- function(df_data, alpha, folds=5, repeats=1, interactions=FALSE, method="pearson") {
   n_models <- repeats * folds
   print(n_models)
+  print(alpha)
 
   # make df with response Y and the PCA's from the different signatures
   if (interactions){
[…]

### 2023-03-22 R_codeP01/scripts/33_ensemble_stack_04.R

@@ -41,7 +41,7 @@ t <-level_0_model(char_list, prolif_771genes)
 class(t)
 
 # function to calculate predictions of the level 0 models on some test data
-# The only different from the one above is that it takes fited model as argument instead of fiting them in the function
+# The only different from the one above is that it takes fitted model as argument instead of fitting them in the function
 level_0_test <- function(named_list, test_data, fits){
   pred_test_L0 <- data.frame(matrix(nrow = nrow(test_data), ncol = 0))
   
@@ -133,8 +133,9 @@ lasso_rep_cv <- function(df_data, named_list, folds=5, repeats=1, interactions=F
   return(list(cor_vec=cor_vec, coef_matrix=coef_matrix, MSE_vec=MSE_vec))
 }
 
-t3 <- lasso_rep_cv(prolif_771genes, char_list, folds=5, repeats=50, method="pearson")
-t3 <- lasso_rep_cv(prolif_771genes, char_list, folds=5, repeats=50, interactions=TRUE, method="pearson")
+t3 <- lasso_rep_cv(ROR_prolif_771genes, char_list, folds=5, repeats=50, interactions=FALSE, method="pearson")
+t3 <- lasso_rep_cv(ROR_prolif_771genes, char_list, folds=5, repeats=50, interactions=TRUE, method="pearson")
+mean(t3$cor_vec)
 
 set.seed(123)
 reps <- 2

### 2023-03-23 R_codeP01/reports/MS2_report02.Rmd
working on report

@@
 # PCA on signature gene sets, cross-validation
+
 ### Ridge: 771 genes -> ROR-proliferation score
@@
 
-LAGE TABELLER HER
+### Summery results: PCA ROR+proliferation score (repeated cross-validation) 
+```{r}
+data_table <- data.frame(
+  Model = c("ridge", "ridge_interac", "lasso", "lasso_interact", "elastic", "elastic_interact"),
+  cor_mean = c(r_pca_c_771_RORprolif$cor_mean, r_pca_c_interact_771_RORprolif$cor_mean, l_pca_c_771_RORprolif$cor_mean, l_pca_c_interact_771_RORprolif$cor_mean, en_pca_c_771_RORprolif$cor_mean, en_pca_c_interact_771_RORprolif$cor_mean),
+
+  sd_cor = c(r_pca_c_771_RORprolif$cor_sd, r_pca_c_interact_771_RORprolif$cor_sd, l_pca_c_771_RORprolif$cor_sd, l_pca_c_interact_771_RORprolif$cor_sd, en_pca_c_771_RORprolif$cor_sd, en_pca_c_interact_771_RORprolif$cor_sd),
+
+  MSE_mean = c(r_pca_c_771_RORprolif$MSE_mean, r_pca_c_interact_771_RORprolif$MSE_mean, l_pca_c_771_RORprolif$MSE_mean, l_pca_c_interact_771_RORprolif$MSE_mean, en_pca_c_771_RORprolif$MSE_mean, en_pca_c_interact_771_RORprolif$MSE_mean),
+
+  MSE_sd = c(r_pca_c_771_RORprolif$MSE_sd, r_pca_c_interact_771_RORprolif$MSE_sd, l_pca_c_771_RORprolif$MSE_sd, l_pca_c_interact_771_RORprolif$MSE_sd, en_pca_c_771_RORprolif$MSE_sd, en_pca_c_interact_771_RORprolif$MSE_sd)
+)
+kable(data_table)
+```
+
+# Stacking on signature gene sets, cross-validation
+
+### Ridge: 771 genes -> ROR-proliferation score
+```{r}
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/r_stack_c_771_RORprolif.RData")
+r_stack_c_771_RORprolif <- report02_out_ridge(r_stack_c_771_RORprolif)
+```
+
+### Ridge: 771 genes -> ROR-proliferation score + interactions between PCs
+```{r}
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/r_stack_c_interact_771_RORprolif.RData")
+r_stack_c_interact_771_RORprolif <- report02_out_ridge(r_stack_c_interact_771_RORprolif)
+```
+
+### Lasso: 771 genes -> ROR-proliferation score
+```{r}
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/l_stack_c_771_RORprolif.RData")
+l_stack_c_771_RORprolif <- report02_out(l_stack_c_771_RORprolif)
+```
+
+### Lasso: 771 genes -> ROR-proliferation score + interactions between PCs
+```{r}
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/l_stack_c_interact_771_RORprolif.RData")
+l_stack_c_interact_771_RORprolif <- report02_out(l_stack_c_interact_771_RORprolif)
+```
+
+### ElasticNet: 771 genes -> ROR-proliferation score
+```{r}
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/en_stack_c_771_RORprolif.RData")
+en_stack_c_771_RORprolif <- report02_out(en_stack_c_771_RORprolif)
+```
+
+### ElasticNet: 771 genes -> ROR-proliferation score + interactions between PCs
+```{r}
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/en_stack_c_interact_771_RORprolif.RData")
+en_stack_c_interact_771_RORprolif <- report02_out(en_stack_c_interact_771_RORprolif)
+```
+
+### Summery results: Stacking ROR+proliferation score (repeated cross-validation) 
+```{r}
+data_table <- data.frame(
+  Model = c("ridge", "ridge_interac", "lasso", "lasso_interact", "elastic", "elastic_interact"),
+  cor_mean = c(r_stack_c_771_RORprolif$cor_mean, r_stack_c_interact_771_RORprolif$cor_mean, l_stack_c_771_RORprolif$cor_mean, l_stack_c_interact_771_RORprolif$cor_mean, en_stack_c_771_RORprolif$cor_mean, en_stack_c_interact_771_RORprolif$cor_mean),
+
+  sd_cor = c(r_stack_c_771_RORprolif$cor_sd, r_stack_c_interact_771_RORprolif$cor_sd, l_stack_c_771_RORprolif$cor_sd, l_stack_c_interact_771_RORprolif$cor_sd, en_stack_c_771_RORprolif$cor_sd, en_stack_c_interact_771_RORprolif$cor_sd),
+
+  MSE_mean = c(r_stack_c_771_RORprolif$MSE_mean, r_stack_c_interact_771_RORprolif$MSE_mean, l_stack_c_771_RORprolif$MSE_mean, l_stack_c_interact_771_RORprolif$MSE_mean, en_stack_c_771_RORprolif$MSE_mean, en_stack_c_interact_771_RORprolif$MSE_mean),
+
+  MSE_sd = c(r_stack_c_771_RORprolif$MSE_sd, r_stack_c_interact_771_RORprolif$MSE_sd, l_stack_c_771_RORprolif$MSE_sd, l_stack_c_interact_771_RORprolif$MSE_sd, en_stack_c_771_RORprolif$MSE_sd, en_stack_c_interact_771_RORprolif$MSE_sd)
+)
+kable(data_table)
+```
 
@@
 
-### Summery results: Boosting with stumps 771 genes bootstrap and repeated cross-validation
+## Summary using domain knowledge
+
+### Summery results: PCA ROR+proliferation score (repeated cross-validation) 
 ```{r}
 data_table <- data.frame(
-  Model = c("prolif boot", "ROR-prolif boot", "prolif rep cross-val", "ROR-prolif rep cross-val"),
-  cor_mean = c(xg_b_771_p$cor_mean, xg_b_771_ROR_p$cor_mean, xg_c_771_p$cor_mean, xg_c_771_ROR_p$cor_mean),
-  sd_cor = c(xg_b_771_p$cor_sd, xg_b_771_ROR_p$cor_sd, xg_c_771_p$cor_sd, xg_c_771_ROR_p$cor_sd),
-  MSE_mean = c(xg_b_771_p$MSE_mean, xg_b_771_ROR_p$MSE_mean, xg_c_771_p$MSE_mean, xg_c_771_ROR_p$MSE_mean),
-  MSE_sd = c(xg_b_771_p$MSE_sd, xg_b_771_ROR_p$MSE_sd, xg_c_771_p$MSE_sd, xg_c_771_ROR_p$MSE_sd)
+  Model = c("ridge", "ridge_interac", "lasso", "lasso_interact", "elastic", "elastic_interact"),
+  cor_mean = c(r_pca_c_771_RORprolif$cor_mean, r_pca_c_interact_771_RORprolif$cor_mean, l_pca_c_771_RORprolif$cor_mean, l_pca_c_interact_771_RORprolif$cor_mean, en_pca_c_771_RORprolif$cor_mean, en_pca_c_interact_771_RORprolif$cor_mean),
+
+  sd_cor = c(r_pca_c_771_RORprolif$cor_sd, r_pca_c_interact_771_RORprolif$cor_sd, l_pca_c_771_RORprolif$cor_sd, l_pca_c_interact_771_RORprolif$cor_sd, en_pca_c_771_RORprolif$cor_sd, en_pca_c_interact_771_RORprolif$cor_sd),
+
+  MSE_mean = c(r_pca_c_771_RORprolif$MSE_mean, r_pca_c_interact_771_RORprolif$MSE_mean, l_pca_c_771_RORprolif$MSE_mean, l_pca_c_interact_771_RORprolif$MSE_mean, en_pca_c_771_RORprolif$MSE_mean, en_pca_c_interact_771_RORprolif$MSE_mean),
+
+  MSE_sd = c(r_pca_c_771_RORprolif$MSE_sd, r_pca_c_interact_771_RORprolif$MSE_sd, l_pca_c_771_RORprolif$MSE_sd, l_pca_c_interact_771_RORprolif$MSE_sd, en_pca_c_771_RORprolif$MSE_sd, en_pca_c_interact_771_RORprolif$MSE_sd)
 )
@@
 ```
+
+### Summery results: Stacking ROR+proliferation score (repeated cross-validation) 
+```{r}
+data_table <- data.frame(
+  Model = c("ridge", "ridge_interac", "lasso", "lasso_interact", "elastic", "elastic_interact"),
+  cor_mean = c(r_stack_c_771_RORprolif$cor_mean, r_stack_c_interact_771_RORprolif$cor_mean, l_stack_c_771_RORprolif$cor_mean, l_stack_c_interact_771_RORprolif$cor_mean, en_stack_c_771_RORprolif$cor_mean, en_stack_c_interact_771_RORprolif$cor_mean),
+
+  sd_cor = c(r_stack_c_771_RORprolif$cor_sd, r_stack_c_interact_771_RORprolif$cor_sd, l_stack_c_771_RORprolif$cor_sd, l_stack_c_interact_771_RORprolif$cor_sd, en_stack_c_771_RORprolif$cor_sd, en_stack_c_interact_771_RORprolif$cor_sd),
+
+  MSE_mean = c(r_stack_c_771_RORprolif$MSE_mean, r_stack_c_interact_771_RORprolif$MSE_mean, l_stack_c_771_RORprolif$MSE_mean, l_stack_c_interact_771_RORprolif$MSE_mean, en_stack_c_771_RORprolif$MSE_mean, en_stack_c_interact_771_RORprolif$MSE_mean),
+
+  MSE_sd = c(r_stack_c_771_RORprolif$MSE_sd, r_stack_c_interact_771_RORprolif$MSE_sd, l_stack_c_771_RORprolif$MSE_sd, l_stack_c_interact_771_RORprolif$MSE_sd, en_stack_c_771_RORprolif$MSE_sd, en_stack_c_interact_771_RORprolif$MSE_sd)
+)
+kable(data_table)
+```

### 2023-03-23 R_codeP01/scripts/00_packages01.R

@@ -4,11 +4,13 @@ library(tidyverse)
 library(readxl)
 library(tidymodels)
 library(dplyr)
+library(ggplot2)
 
 library(glmnet)
 library(boot)
 library(caret)
 library(mboost)
+
 
 install.packages("grpreg")
 install.packages("sparsegl")

### 2023-03-23 R_codeP01/scripts/01_dataclean01.R

@@ -92,7 +92,7 @@ Y <- as.matrix(select(Proliferation_6genes, Y))
 all_genes <- colnames(df01 |> select(41:811))
 
 # just for testing with fewer features
-test_genes <- colnames(df01 |> select(41:46))
+# test_genes <- colnames(df01 |> select(41:46))
 
 length(all_genes)
 

### 2023-03-23 R_codeP01/scripts/30_signature_genes03.R

@@ -4,6 +4,16 @@
 
 # NB: looks to be the same/or very close to 30_ensembel_01 ???
 
+# Name list og gene signature sets 
+char_list <- list(imm_inf_ = char_immune_inf,
+                  prolif_ = char_prolif,
+                  ER_sing_ = char_ER_signaling,
+                  anti_pres_ = char_antigen_present,
+                  angiogen_ = char_angiogenesis
+                  )
+
+
+
 
 ## Create character matrix from signature genes
 signature_char <- function(words){

### 2023-03-23 R_codeP01/scripts/33_ensemble_stack_04.R

@@ -5,30 +5,17 @@
 ##
 ## Test against the fold
 ## Cross-validation (5-fold) used for training/tuning lambda and selecting features
-## output: selected genes; proliferation.score correlation; SEM
-
-library(caret)
-library(glmnet)
-library(ggplot2)
-
-
-# Name list og gene signature sets 
-char_list <- list(imm_inf_ = char_immune_inf,
-                  prolif_ = char_prolif,
-                  ER_sing_ = char_ER_signaling,
-                  anti_pres_ = char_antigen_present,
-                  angiogen_ = char_angiogenesis
-)
+## output: selected genes (); proliferation.score correlation; SEM
 
 # function to calculate new feature set from level 0 learners
-level_0_model <- function(named_list, train_data){
+level_0_model <- function(named_list, train_data, alpha0){
   pred_L0 <- data.frame(matrix(nrow = nrow(train_data), ncol = 0))
   fits <- list()
   
   for (key in names(named_list)) {
     char_matrix <- named_list[[key]]
     X_ <- as.matrix(train_data[c(char_matrix)])
-    fit_ <- cv.glmnet(X_, train_data$Y, nfolds=5)
+    fit_ <- cv.glmnet(X_, train_data$Y, alpha=alpha0, nfolds=5)
     # here prediction is made using same data as used in learning the model... ?
     pred_ = predict(fit_, newx = X_, type = "response", s = "lambda.min")
     colnames(pred_) <- key
@@ -37,8 +24,8 @@ level_0_model <- function(named_list, train_data){
   }
   return(list(pred_L0=pred_L0, fits=fits))
 }
-t <-level_0_model(char_list, prolif_771genes)
-class(t)
+# t <-level_0_model(char_list, prolif_771genes, )
+# class(t)
 
 # function to calculate predictions of the level 0 models on some test data
 # The only different from the one above is that it takes fitted model as argument instead of fitting them in the function
@@ -55,13 +42,11 @@ level_0_test <- function(named_list, test_data, fits){
   }
   return(pred_test_L0)
 }
-
-t1 <- level_0_test(char_list, prolif_771genes, t$fit)
-
[…]

### 2023-03-23 R_codeP01/reports/MS2_report02_the_real_one.Rmd
finished report 2

--- 2023-03-23 R_codeP01/reports/MS2_report02.Rmd
@@
 These sets are substantially smaller then the signature genes; which I presume leads to some issue in modeling (as for clinical data too - see next sentence).
+In the domain knowledge part at the end 5 signature gene sets are use. Make sense to add more...
 
@@
 
-## Respones used
+## Respones in study -ish
 ### Proliferation score
+
 A score based on expression level of some of the genes. Range: -1.1366 to 0.8511
+
 ### Risk of relapse score (ROR)
-A score based on expression level of some of the genes. Range: -8.035678 to 75.13174
-### Risk of relapse score with proliferaton score (ROR-Prolif)
-A combined score based on expression level of more genes. Range: 1 to 97 (1-100).
 
-The two scores involving ROR also have categorical variants containing: \ 
-low, medium, high
+A combined score based on expression level of genes and some clinical findings. Range: -8.035678 to 75.13174
+
+(only used in combination with proliferation score as described bellow)
+
+### Risk of relapse score with proliferaton score (ROR_Prolif)
+
+A combined score of the two above. Range: 1 to 97 (1-100)
+
+The two scores involving ROR also have categorical variants containing: low, medium, high
+(but not used...)
 
@@
 This gives a relative comparison of the various models with respect to data very similar to the given data set.
-In addition to Correlation and MSE, frequency of selected features is compared.
+Correlation, MSE and frequency of selected features is compared.
 
@@
 3 strategies are considered:
-1. Repeated cross-validations (200 rep, 5-fold) \ 
-2. Bootstrap models with 0.632 (or 0.632?) adjustment (Not done) \ 
-3. Use the cohort as test data-set (Challenge: This trail have different responses) \
+
+1. Repeated cross-validations (200 rep, 5-fold)
+
+2. Bootstrap models with 0.632 (or 0.632?) adjustment (Not done)
+
+3. Use the cohort as test data-set (Challenge: This trail have different responses)
 
 # RESULTS
+## Features tested:
+### 6 genes
+### 771 genes
+### node values of mech model
+### residuals of mech model
+
+## Responses tested:
+### proliferation score
+### combined score including proliferation and ROR
+
+## Models tested:
+### Lasso
+### Ridge
+### Elastic Net
+### Boosting with stumps as base learner
+#### (- mboost)
+#### - xgboost
+### PCA on subsets of genes
+### Stacking using different features in the base models
+### Sparse group lasso (not done)
+### Iterative learning (ongoing)
+### Post Lasso (not done)
 
@@
 
-# Models tested
-## Lasso
-## Post Lasso
-## Residuals
-## Ridge
-## Elastic Net
-## Boosting with stumps as base learner
-### - mboost
-### - xgboost
-## PCA feature engineering
-## Stacking using different features in the base models 
-## Synergistic learning
 ```{r}
@@
 ## Lasso - Repeated cross-validation
-200 repeats of five fold cross-validation \ 
+200 repeats of five fold cross-validation
+
 ### 6 genes -> proliferation score
@@
 
-# PCA on signature gene sets, cross-validation
+# PCA on signature gene sets using repeated cross-validation
 
@@
 
-# Stacking on signature gene sets, cross-validation
+# Stacking on signature gene sets using repeated cross-validation
 
@@
 ```
+
+# Summery most interesting maybe
+Response is just ROR+proliferation score, and only used repeated cross-validation.
+
+```{r}
+data_table <- data.frame(
+  Model = c("Lasso", "Ridge", "ElasticNet", "Boosting", "Residual (lasso/additive)", 
+            "PCA ON GENE SETS", "ridge", "ridge_interac", "lasso", "lasso_interact", "elastic", "elastic_interact", 
+            "STACKING ON GENE SETS", "ridge", "ridge_interac", "lasso", "lasso_interact", "elastic", "elastic_interact"),
+
+  cor_mean = c(
+    l_c_771_ROR_p$cor_mean,
+    r_c_771_ROR_p$cor_mean,
+    e_c_771_ROR_p$cor_mean,
+    xg_c_771_ROR_p$cor_mean,
+    l_c_residuals_ROR_p_a$cor_mean,
+    "",
+    r_pca_c_771_RORprolif$cor_mean, 
+    r_pca_c_interact_771_RORprolif$cor_mean, 
+    l_pca_c_771_RORprolif$cor_mean, 
+    l_pca_c_interact_771_RORprolif$cor_mean, 
+    en_pca_c_771_RORprolif$cor_mean, 
+    en_pca_c_interact_771_RORprolif$cor_mean,
+    "", 
+    r_stack_c_771_RORprolif$cor_mean, 
+    r_stack_c_interact_771_RORprolif$cor_mean, 
+    l_stack_c_771_RORprolif$cor_mean, 
+    l_stack_c_interact_771_RORprolif$cor_mean, 
+    en_stack_c_771_RORprolif$cor_mean,
+    en_stack_c_interact_771_RORprolif$cor_mean),
+
+  sd_cor = c(
+    l_c_771_ROR_p$cor_sd,
+    r_c_771_ROR_p$cor_sd,
+    e_c_771_ROR_p$cor_sd,
+    xg_c_771_ROR_p$cor_sd,
+    l_c_residuals_ROR_p_a$cor_sd,
+    "",
+    r_pca_c_771_RORprolif$cor_sd, 
+    r_pca_c_interact_771_RORprolif$cor_sd, 
+    l_pca_c_771_RORprolif$cor_sd, 
+    l_pca_c_interact_771_RORprolif$cor_sd, 
+    en_pca_c_771_RORprolif$cor_sd, 
+    en_pca_c_interact_771_RORprolif$cor_sd,
+    "",
+    r_stack_c_771_RORprolif$cor_sd, 
+    r_stack_c_interact_771_RORprolif$cor_sd, 
+    l_stack_c_771_RORprolif$cor_sd, 
+    l_stack_c_interact_771_RORprolif$cor_sd, 
+    en_stack_c_771_RORprolif$cor_sd, 
+    en_stack_c_interact_771_RORprolif$cor_sd),
+
+  MSE_mean = c(    
+    l_c_771_ROR_p$MSE_mean,
+    r_c_771_ROR_p$MSE_mean,
+    e_c_771_ROR_p$MSE_mean,
+    xg_c_771_ROR_p$MSE_mean,
+    l_c_residuals_ROR_p_a$MSE_mean,
+    "", 
+    r_pca_c_771_RORprolif$MSE_mean, 
+    r_pca_c_interact_771_RORprolif$MSE_mean, 
+    l_pca_c_771_RORprolif$MSE_mean, 
+    l_pca_c_interact_771_RORprolif$MSE_mean, 
+    en_pca_c_771_RORprolif$MSE_mean, 
+    en_pca_c_interact_771_RORprolif$MSE_mean,
+    "",
+    r_stack_c_771_RORprolif$MSE_mean, 
+    r_stack_c_interact_771_RORprolif$MSE_mean, 
+    l_stack_c_771_RORprolif$MSE_mean,
+    l_stack_c_interact_771_RORprolif$MSE_mean, 
+    en_stack_c_771_RORprolif$MSE_mean, 
+    en_stack_c_interact_771_RORprolif$MSE_mean),
+
+  MSE_sd = c(    
+    l_c_771_ROR_p$MSE_sd,
+    r_c_771_ROR_p$MSE_sd,
+    e_c_771_ROR_p$MSE_sd,
+    xg_c_771_ROR_p$MSE_sd,
+    l_c_residuals_ROR_p_a$MSE_sd,
+    "",
+    r_pca_c_771_RORprolif$MSE_sd, 
+    r_pca_c_interact_771_RORprolif$MSE_sd, 
+    l_pca_c_771_RORprolif$MSE_sd, 
+    l_pca_c_interact_771_RORprolif$MSE_sd, 
+    en_pca_c_771_RORprolif$MSE_sd, 
+    en_pca_c_interact_771_RORprolif$MSE_sd,
+    "",
+    r_stack_c_771_RORprolif$MSE_sd,
+    r_stack_c_interact_771_RORprolif$MSE_sd, 
+    l_stack_c_771_RORprolif$MSE_sd, 
+    l_stack_c_interact_771_RORprolif$MSE_sd, 
+    en_stack_c_771_RORprolif$MSE_sd, 
+    en_stack_c_interact_771_RORprolif$MSE_sd)
+)
+kable(data_table)
+```

### 2023-03-23 R_codeP01/reports/MS2_report02_truncated.Rmd
finished report 2

--- 2023-03-23 R_codeP01/reports/MS2_report02_the_real_one.Rmd
@@
 # Data
-One clinical trails on breast cancer (advanced HR+/HER2- and HER2-E breast cancer) using two different drug combination; and a cohorts study (here used as test data set).  
-Both data set have mRNA expression of 771 genes at baseline (prior to treatment). This genes are specifically selected based on their potential roles in breast cancer pathology:  
+One clinical trails on breast cancer (advanced HR+/HER2-) using two different drug combination
+
+The data set have mRNA expression of 771 genes at baseline (prior to treatment). This genes are specifically selected based on their potential roles in breast cancer pathology:
+
 The gene set is dived into 25 sets of "signature genes"; which are thought to represent functional unities with respect to cancer biology.
@@
 
-Additionally, both data-set contains clinical data; which up to now is not used in any models.
+Additionally, the data-set contains clinical data; which up to now is not used in any models.
 If included they maybe should have a higher weight or be implemented differently from a sole gene.
@@
 
-### Progression free survival (PFS)
-This is the outcome used in the clinical cohort.
-Here i have used correlation with the scores described above.
-Spearman can maybe be used.
-Another approach is to use the above scores to divide the patient in to two groups and see if the two groups show clearly separable PFS over time (basically lock at the graphs).
-The differentiation into two groups is done base on best values from a ROC curve.
-
 ## Trail
@@
 Endpoints: proliferation score, ROR score, combined ROR and prolif
-
-## Cohort
-The primary objective of this study is to compare two cdk4/6 targeted drugs (Palbociclib, n=36; Abemaciclib, n=3 in combination with endocrine therapy (tamoxifen, fulvestrant or aromatase inhibitors,  I think?)
-
-Endpoints: progression free survival (months), OS?, and status of the two former (dont know what that means)
 

### 2023-03-23 R_codeP01/reports/MS2_report02_truncated.Rmd
rapport

@@
 ```{r}
+options(digits=3)
 data_table <- data.frame(
@@
 )
-kable(data_table)
+
+rounded_data_table <- data_table |>
+  mutate_if(is.numeric, round, digits = 3)
+
+kable(rounded_data_table)
 ```

### 2023-03-24 R_codeP01/scripts/00_packages01.R
implemented sparsgel function

@@ -11,10 +11,17 @@ library(boot)
 library(caret)
 library(mboost)
 
+library(sparsgel)
+
+
 
 install.packages("grpreg")
 install.packages("sparsegl")
 
+# Install and load the sparsgel package
+if (!requireNamespace("sparsgel", quietly = TRUE)) {
+  install.packages("sparsgel")
+}
 
 
 

### 2023-03-24 R_codeP01/scripts/34_sparse_gr_01.R

@@ -1,0 +1,187 @@
+###################################################################
+## Repeated cross-validation for testing Sparse-group Lasso with SPARSGEL ##
+###################################################################
+##
+## Test against the fold
+## Cross-validation (5-fold) used for training/tuning lambda and selecting features
+## output: selected genes; proliferation.score correlation; SEM
+
+
+# PCA's:
+char_list <- list(imm_inf_ = char_immune_inf,
+                  prolif_ = char_prolif,
+                  ER_sing_ = char_ER_signaling,
+                  anti_pres_ = char_antigen_present,
+                  angiogen_ = char_angiogenesis
+)
+
+# This function return only the best PC from a given signature gene set
+PC <- function(name, characters, data){
+  sign_data <-  data[, characters]
+  pca_results <- prcomp(sign_data, scale = TRUE, center=TRUE) # create PCA object
+  # Extract the first principal component
+  df_important_pca <- data.frame(pca_results$x[, 1])
+  colnames(df_important_pca) <- paste0(name)
+  return(df_important_pca)
+}
+
+# This function return the PCs based on percentage of variance explained from a given signature gene set
+PCs <- function(name, characters, data, percentage=0.9){
+  sign_data <-  data[, characters]
+  pca_results <- prcomp(sign_data, scale = TRUE, center=TRUE) # create PCA object
+  # Get the number of components that explain at least 90 % of the variance
+  n_components <- sum(pca_results$sdev^2 / sum(pca_results$sdev^2) >= (1-percentage))
+  # Extract the first n_components principal components
+  df_important_pca <- data.frame(pca_results$x[, 1:n_components])
+  colnames(df_important_pca) <- c(paste0(name, 1:n_components))
+  return(df_important_pca)
+}
+
+# Create df from the PCs
+pca_as_features <- function(named_list, df_data, percentage=0.9){
+  df_Y_PCA <- data.frame(Y=df_data[,1])
[…]

### 2023-03-24 R_codeP01/scripts/34_sparse_gr_02.R

@@ -1,0 +1,195 @@
+###################################################################
+## Repeated cross-validation for testing Sparse-group Lasso with SPARSGEL ##
+###################################################################
+##
+## Test against the fold
+## Cross-validation (5-fold) used for training/tuning lambda and selecting features
+## output: selected genes; proliferation.score correlation; SEM
+
+
+# PCA's:
+char_list <- list(imm_inf_ = char_immune_inf,
+                  prolif_ = char_prolif,
+                  ER_sing_ = char_ER_signaling,
+                  anti_pres_ = char_antigen_present,
+                  angiogen_ = char_angiogenesis
+)
+
+
+
+prepare_group_index_vector <- function(df, col_groups) {
+  # Input
+  # df = dataframe containing with predictors and response variable in first column
+  # col_groups = a list of character vectors, where each vector contains the column names belonging to the same group
+  # Output: group assignment vector with 0 where variables where not assign to a specific group
+  
+  # Initialize the group assignment vector
+  group <- rep(0, ncol(df)-1)
+  
+  # Remove the response variable from the dataframe
+  predictor_df <- df[, -1]
+  
+  # Assign group numbers to predictors within choosen groups as defined by col_groups
+  group_number <- 1
+  for (group_cols in col_groups) {
+    for (col in group_cols) {
+      col_index <- which(colnames(predictor_df) == col)
+      group[col_index] <- group_number
+    }
+    group_number <- group_number + 1
+  }
+  
+  return(group)
+}
+
+
+# Sparse Group Lasso function with grouped and ungrouped predictors
+sparse_group_lasso_sparsegl <- function(df, group) {
+  # Input:
+  # df = dataframe containing with predictors and response variable in first column
+  # groups = group assignment vector with zeros for ungrouped predictors
+  
+  # Assign individual groups to ungrouped predictors
[…]

### 2023-03-24 R_codeP01/scripts/40_iterative_07_zz3_bootstrap.R

@@ -1,11 +1,9 @@
 library(glmnet)
 set.seed(123)
 
-synergistic <- function(df, groups, alpha = 0.5, lambda_seq = NULL, nfolds = 5, tol = 1e-4, max_iters = 100) {
-  # Extract predictor matrix and response vector; assuming response variable in first column
-  X <- as.matrix(df[, -1])
-  X <- scale(X)
-  y <- df[, 1]
+elastic_net_interaction <- function(x_df, y, groups, alpha = 0.5, lambda_seq = NULL, nfolds = 5, tol = 1e-4, max_iters = 1000) {
+
+  x <- as.matrix(x_df)
   
   # Create a list of groups, each group containing the column indices of x corresponding to the feature names in char_list
   groups <- lapply(char_list, function(char_group) {
@@ -74,29 +72,22 @@ synergistic <- function(df, groups, alpha = 0.5, lambda_seq = NULL, nfolds = 5, 
 
     new_beta_main <- new_betas[1:ncol(x)]
     
-    # best_lambda_idx <- which(fit_with_interactions$lambda == best_lambda)
-    # dev_glmnet_curr <-  (1 - fit_with_interactions$glmnet$dev.ratio[best_lambda_idx]) * fit_with_interactions$glmnet$nulldev
-    # obj_dev <- abs(dev_glmnet_curr - dev_glmnet)/dev_glmnet_curr
-    # if ( obj_dev < tol ) {  # Only check convergence for the betas without interaction terms
-    #   converged <- TRUE
+    best_lambda_idx <- which(fit_with_interactions$lambda == best_lambda)
+    dev_glmnet_curr <-  (1 - fit_with_interactions$glmnet$dev.ratio[best_lambda_idx]) * fit_with_interactions$glmnet$nulldev
+    obj_dev <- abs(dev_glmnet_curr - dev_glmnet)/dev_glmnet_curr
+    
+    # obj_dev <- abs(new_beta_main - beta_main)
+    # obj_dev <- max(obj_dev)
+    # if (obj_dev == 0) {
+    #   obj_dev <- 1
     # } else {
-    #   dev_glmnet <- dev_glmnet_curr
-    #   beta_main <- new_beta_main
-    #   betas <- new_betas  # Update betas only if not converged
+    #   obj_dev <- mean(abs((new_beta_main - beta_main))[new_beta_main != 0 | beta_main != 0])
     # }
-    # 
-    if (!any(new_beta_main != 0) && iter > 10)
-      stop("Warning: all beta manins are zero!")
[…]

### 2023-03-24 R_codeP01/scripts/34_sparse_gr_02.R
synergistic maybe dont work

@@ -6,8 +6,6 @@
 ## Cross-validation (5-fold) used for training/tuning lambda and selecting features
 ## output: selected genes; proliferation.score correlation; SEM
 
-
-# PCA's:
 char_list <- list(imm_inf_ = char_immune_inf,
                   prolif_ = char_prolif,
                   ER_sing_ = char_ER_signaling,

### 2023-03-24 R_codeP01/scripts/40_iterative_07_zz2.R

@@ -1,11 +1,9 @@
 library(glmnet)
 set.seed(123)
 
-synergistic <- function(df, groups, alpha = 0.5, lambda_seq = NULL, nfolds = 5, tol = 1e-4, max_iters = 100) {
-  # Extract predictor matrix and response vector; assuming response variable in first column
-  X <- as.matrix(df[, -1])
-  X <- scale(X)
-  y <- df[, 1]
+elastic_net_interaction <- function(x_df, y, groups, alpha = 0.5, lambda_seq = NULL, nfolds = 5, tol = 1e-4, max_iters = 100) {
+
+  x <- as.matrix(x_df)
   
   # Create a list of groups, each group containing the column indices of x corresponding to the feature names in char_list
   groups <- lapply(char_list, function(char_group) {

### 2023-03-24 R_codeP01/scripts/40_iterative_syn_02.R

@@ -1,5 +1,3 @@
-
-
 synergistic <- function(df, char_list, alpha = 0.5, lambda_seq = NULL, nfolds = 5, tol = 1e-4, max_iters = 100) {
   # Extract predictor matrix and response vector; assuming response variable in first column
   X <- as.matrix(df[, -1])
@@ -58,14 +56,25 @@ synergistic <- function(df, char_list, alpha = 0.5, lambda_seq = NULL, nfolds = 
       interactions[, i] <- interaction_terms(X, beta_main, group1, group2)
     }
     
+    
+    interactions_sd = apply(interactions, 2, sd)
+    interactions = interactions[, interactions_sd != 0]
+    print(dim(interactions))
     # Make feature matrix with original features and interactions
     X_with_interactions <- cbind(X, interactions)
     
     # Fit model using adaptive elastic-net
-    pf <- betas
+    #pf <- betas
+    
+    pf <- rep(1, ncol(X_with_interactions))
+    print(length(pf))
+    pf[1:ncol(X)] <- betas[1:ncol(X)] 
     pf[pf == 0] <- 1e-2
     pf <- 1 / pf
-    pf[(ncol(X) + 1):length(betas)] <- 0
+    if (ncol(dim(interactions)[2]) > 0) {
+      pf[(ncol(X) + 1):ncol(X_with_interactions)] <- 0
+    }
+    print(length(pf))
     fit_with_interactions <- cv.glmnet(X_with_interactions, y, alpha = alpha, lambda = lambda_seq, nfolds = nfolds, penalty.factor = pf)
     best_lambda <- fit_with_interactions$lambda.min
     
@@ -86,14 +95,15 @@ synergistic <- function(df, char_list, alpha = 0.5, lambda_seq = NULL, nfolds = 
       converged <- TRUE
     } else {
       dev_glmnet <- dev_glmnet_curr
-      beta_main <- new_beta_main
       betas <- new_betas  # Update betas only if not converged
+      beta_main <- new_beta_main
     }
     
     obj_diff <- c(obj_diff, dev_glmnet)
   }
   # betas <- new_betas
-  beta_interaction <- betas[(ncol(X) + 1):length(betas)]
+  # beta_interaction <- betas[(ncol(X) + 1):length(betas)]
+  beta_interaction <- betas[ncol(X) + 1:ncol(interactions)]
   
[…]

### 2023-03-24 R_codeP01/scripts/TIPS.R

@@ -1,0 +1,34 @@
+
+
+
+dat <- list(ROR_prolif_771genes=ROR_prolif_771genes, char_list=char_list, synergistic=synergistic)
+save(dat, file = "dat.RData")
+
+
+a=names(result$beta_main)
+lapply(char_list, function(xx) sum(a %in% as.vector(xx)))
+
+
+sum(a %in% as.vector(char_list$prolif_))
+
+as.vector(char_list$prolif_)
+
+a=names(a)
+a
+# [1] "ALDOA"    "AURKB"    "AXIN2"    "BAIAP2L1" "BBOX1"    "BMP7"     "BMPR1B"  
+# [8] "CACNA1H"  "CD44"     "COL9A3"   "DDX39A"   "DKK1"     "EIF3B"    "EP300"   
+# [15] "EYA1"     "FGF12"    "FOXC1"    "FZD10"    "HBB"      "HDAC5"    "LEF1"    
+# [22] "LIF"      "MLH1"     "MMP3"     "PLAT"     "PMS2"     "PRLR"     "PROM1"   
+# [29] "RBL2"     "RBX1"     "RELN"     "RORB"     "SHMT2"    "SP1"      "TLE3"    
+# [36] "TUBA4A"   "UBE2T"   
+
+sum(a %in% as.vector(char_list$prolif_))
+[1] 5
+
+sum(a %in% as.vector(char_list$ER_sing_))
+[1] 4
+
+
+lapply(char_list, function(xx) sum(a %in% as.vector(xx)))
+
+

### 2023-03-25 R_codeP01/reports/MS2_report0333.Rmd
sparse group lasso on clinical data

--- 2023-02-14 R_codeP01/reports/MS2_report02.Rmd
@@
 # lb_obj_771_prolif.RData
-# lb_obj_residuals_6_prolif.RData
 # lb_obj_771_residuals_prolif.RData
@@
 
-# RESULTS
-
-# Results of individual modles:
-
-# Models tested
+# Models
 ## Lasso
@@
 ### - xgboost
-## PCA feature engineering
 ## Stacking using different features in the base models 
 ## Synergistic learning
+
+# RESULTS
 ```{r}
 source("/Users/anders/Documents/Master/Cancer/R_codeP01/scripts/90_output01.R")
-source("/Users/anders/Documents/Master/Cancer/R_codeP01/scripts/90_output_ridge_01.R")
 ```
 
-# Lasso - Bootstrap
+# Lasso
+
+## Bootstrap
 ### 6 genes -> proliferation score
@@
 
-### Mechanistic + Residuals -> proliferation score (additive)
-```{r}
-load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_residuals_771_prolif_a.RData")
-l_b_residuals_771_p_a <- report02_out(lb_obj_residuals_771_prolif_a)
-```
-### Mechanistic + Residuals -> proliferation score (multiplicative)
-```{r}
-load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_residuals_771_prolif_m.RData")
-l_b_residuals_771_p_m <- report02_out(lb_obj_residuals_771_prolif_m)
-```
-### Mechnaistic + Residuals -> ROR-proliferation score (additive)
-```{r}
-load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_residuals_771_RORprolif_a.RData")
-l_b_residuals_ROR_p_a <- report02_out(lb_obj_residuals_771_RORprolif_a)
-```
-### Mechnaistic + Residuals -> ROR-proliferation score (multiplicative)
-```{r}
-load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_residuals_771_RORprolif_m.RData")
-l_b_residuals_ROR_p_m <- report02_out(lb_obj_residuals_771_RORprolif_m)
-```
-
-### Summery results: lasso proliferation score (bootstrap) 
-```{r}
-library(knitr)
-data_table <- data.frame(
-  Model = c("lasso 6 genes", "lasso 771 genes", "Nodes", "Residual additive", "Residual multiplicative"),
-  cor_mean = c(l_b_6_p$cor_mean, l_b_771_p$cor_mean, l_b_nodes_p$cor_mean, l_b_residuals_771_p_a$cor_mean, l_b_residuals_771_p_m$cor_mean),
-  sd_cor = c(l_b_6_p$cor_sd, l_b_771_p$cor_sd, l_b_nodes_p$cor_sd, l_b_residuals_771_p_a$cor_sd, l_b_residuals_771_p_m$cor_sd),
-  MSE_mean = c(l_b_6_p$MSE_mean, l_b_771_p$MSE_mean, l_b_nodes_p$MSE_mean, l_b_residuals_771_p_a$MSE_mean, l_b_residuals_771_p_m$MSE_mean),
-  MSE_sd = c(l_b_6_p$MSE_sd, l_b_771_p$MSE_sd, l_b_nodes_p$MSE_sd, l_b_residuals_771_p_a$MSE_sd, l_b_residuals_771_p_m$MSE_sd)
-)
-kable(data_table)
-```
-
-### Summery results: lasso ROR+proliferation score (bootstrap) 
-```{r}
-data_table <- data.frame(
-  Model = c("lasso 6 genes", "lasso 771 genes", "Nodes", "Residual additive", "Residual multiplicative"),
-  cor_mean = c(l_b_6_ROR_p$cor_mean, l_b_771_ROR_p$cor_mean, l_b_nodes_ROR_p$cor_mean, l_b_residuals_ROR_p_a$cor_mean, l_b_residuals_ROR_p_m$cor_mean),
-  sd_cor = c(l_b_6_ROR_p$cor_sd, l_b_771_ROR_p$cor_sd, l_b_nodes_ROR_p$cor_sd, l_b_residuals_ROR_p_a$cor_sd, l_b_residuals_ROR_p_m$cor_sd),
-  MSE_mean = c(l_b_6_ROR_p$MSE_mean, l_b_771_ROR_p$MSE_mean, l_b_nodes_ROR_p$MSE_mean, l_b_residuals_ROR_p_a$MSE_mean, l_b_residuals_ROR_p_m$MSE_mean),
-  MSE_sd = c(l_b_6_ROR_p$MSE_sd, l_b_771_ROR_p$MSE_sd, l_b_nodes_ROR_p$MSE_sd, l_b_residuals_ROR_p_a$MSE_sd, l_b_residuals_ROR_p_m$MSE_sd)
-)
-kable(data_table)
-```
-
-## Lasso - Repeated cross-validation
-200 repeats of five fold cross-validation \ 
-### 6 genes -> proliferation score
-```{r}
-load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lc_obj_6_prolif.RData")
-l_c_6_p <- report02_out(lc_obj_6_prolif)
-```
-### 6 genes -> ROR_proliferation score
-```{r}
-load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lc_obj_6_RORprolif.RData")
-l_c_6_ROR_p <- report02_out(lc_obj_6_RORprolif)
-```
-
-### 771 genes -> proliferation score
-```{r}
-load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lc_obj_771_prolif.RData")
-l_c_771_p <- report02_out(lc_obj_771_prolif)
-```
-### 771 genes -> ROR-proliferation score
-```{r}
-load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lc_obj_771_RORprolif.RData")
-l_c_771_ROR_p <- report02_out(lc_obj_771_RORprolif)
-```
-
-### node values -> proliferation score
-```{r}
-load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lc_obj_nodes_prolif.RData")
-l_c_nodes_p <- report02_out(lc_obj_nodes_prolif)
-```
-### node values -> ROR-proliferation score
-```{r}
-load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lc_obj_nodes_RORprolif.RData")
-l_c_nodes_ROR_p <- report02_out(lc_obj_nodes_RORprolif)
-```
-
-### Mechanistic + Residuals -> proliferation score (additive)
-```{r}
-load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lc_obj_residuals_771_p_a.RData")
-l_c_residuals_771_p_a <- report02_out(lc_obj_residuals_771_p_a)
-```
-### Mechanistic + Residuals -> proliferation score (multiplicative)
-```{r}
-load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lc_obj_residuals_771_p_m.RData")
-l_c_residuals_771_p_m <- report02_out(lc_obj_residuals_771_p_m)
-```
-### Mechnaistic + Residuals -> ROR-proliferation score (additive)
-```{r}
-load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lc_obj_residuals_771_ROR_p_a.RData")
-l_c_residuals_ROR_p_a <- report02_out(lc_obj_residuals_771_ROR_p_a)
-```
-### Mechnaistic + Residuals -> ROR-proliferation score (multiplicative)
-```{r}
-load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lc_obj_residuals_771_ROR_p_m.RData")
-l_c_residuals_ROR_p_m <- report02_out(lc_obj_residuals_771_ROR_p_m)
-```
-
-### Summery results: lasso proliferation score (repeated cross-validation) 
-```{r}
-library(knitr)
-data_table <- data.frame(
-  Model = c("lasso 6 genes", "lasso 771 genes", "Nodes", "Residual additive", "Residual multiplicative"),
-  cor_mean = c(l_c_6_p$cor_mean, l_c_771_p$cor_mean, l_c_nodes_p$cor_mean, l_c_residuals_771_p_a$cor_mean, l_c_residuals_771_p_m$cor_mean),
-  sd_cor = c(l_c_6_p$cor_sd, l_c_771_p$cor_sd, l_c_nodes_p$cor_sd, l_c_residuals_771_p_a$cor_sd, l_c_residuals_771_p_m$cor_sd),
-  MSE_mean = c(l_c_6_p$MSE_mean, l_b_771_p$MSE_mean, l_c_nodes_p$MSE_mean, l_c_residuals_771_p_a$MSE_mean, l_c_residuals_771_p_m$MSE_mean),
-  MSE_sd = c(l_c_6_p$MSE_sd, l_c_771_p$MSE_sd, l_c_nodes_p$MSE_sd, l_c_residuals_771_p_a$MSE_sd, l_c_residuals_771_p_m$MSE_sd)
-)
-kable(data_table)
-```
-
-### Summery results: lasso ROR+proliferation score (repeated cross-validation) 
-```{r}
-data_table <- data.frame(
-  Model = c("lasso 6 genes", "lasso 771 genes", "Nodes", "Residual additive", "Residual multiplicative"),
-  cor_mean = c(l_c_6_ROR_p$cor_mean, l_c_771_ROR_p$cor_mean, l_c_nodes_ROR_p$cor_mean, l_c_residuals_ROR_p_a$cor_mean, l_c_residuals_ROR_p_m$cor_mean),
-  sd_cor = c(l_c_6_ROR_p$cor_sd, l_c_771_ROR_p$cor_sd, l_c_nodes_ROR_p$cor_sd, l_c_residuals_ROR_p_a$cor_sd, l_c_residuals_ROR_p_m$cor_sd),
-  MSE_mean = c(l_c_6_ROR_p$MSE_mean, l_c_771_ROR_p$MSE_mean, l_c_nodes_ROR_p$MSE_mean, l_c_residuals_ROR_p_a$MSE_mean, l_c_residuals_ROR_p_m$MSE_mean),
-  MSE_sd = c(l_c_6_ROR_p$MSE_sd, l_c_771_ROR_p$MSE_sd, l_c_nodes_ROR_p$MSE_sd, l_c_residuals_ROR_p_a$MSE_sd, l_c_residuals_ROR_p_m$MSE_sd)
-)
-kable(data_table)
-```
-
-# Ridge bootstrap
-### 771 genes -> proliferation score
-```{r}
-load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/r_b_obj_771_p.RData")
-r_b_771_p <- report02_out_ridge(r_b_obj_771_p)
-```
-### 771 genes -> ROR-proliferation score
-```{r}
-load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/r_b_obj_771_ROR_p.RData")
-r_b_771_ROR_p <- report02_out_ridge(r_b_obj_771_ROR_p)
-```
-
-# Ridge repeated cross-validation
-### 771 genes -> proliferation score
-```{r}
-load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/r_c_obj_771_prolif.RData")
-r_c_771_p <- report02_out_ridge(r_c_obj_771_prolif)
-```
-### 771 genes -> ROR-proliferation score
-```{r}
-load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/r_c_obj_771_RORprolif.RData")
-r_c_771_ROR_p <- report02_out_ridge(r_c_obj_771_RORprolif)
-```
-
-### Summery results: ridge 771 genes bootstrap and repeated cross-validation
-```{r}
-data_table <- data.frame(
-  Model = c("prolif boot", "ROR-prolif boot", "prolif rep cross-val", "ROR-prolif rep cross-val"),
-  cor_mean = c(r_b_771_p$cor_mean, r_b_771_ROR_p$cor_mean, r_c_771_p$cor_mean, r_c_771_ROR_p$cor_mean),
-  sd_cor = c(r_b_771_p$cor_sd, r_b_771_ROR_p$cor_sd, r_c_771_p$cor_sd, r_c_771_ROR_p$cor_sd),
-  MSE_mean = c(r_b_771_p$MSE_mean, r_b_771_ROR_p$MSE_mean, r_c_771_p$MSE_mean, r_c_771_ROR_p$MSE_mean),
-  MSE_sd = c(r_b_771_p$MSE_sd, r_b_771_ROR_p$MSE_sd, r_c_771_p$MSE_sd, r_c_771_ROR_p$MSE_sd)
-)
-kable(data_table)
-```
-
-# Elastic Net - bootstrap
-### 771 genes -> proliferation score
-```{r}
-load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/e_b_obj_771_p.RData")
-e_b_771_p <- report02_out_ridge(e_b_obj_771_p)
-```
-### 771 genes -> ROR-proliferation score
-```{r}
-load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/e_b_obj_771_ROR_p.RData")
-e_b_771_ROR_p <- report02_out_ridge(e_b_obj_771_ROR_p)
-```
-
-# Elastic Net: cross-validation
-### 771 genes -> proliferation score
-```{r}
-load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/e_c_obj_771_prolif.RData")
-e_c_771_p <- report02_out_ridge(e_c_obj_771_prolif)
-```
-### 771 genes -> ROR-proliferation score
-```{r}
-load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/e_c_obj_771_RORprolif.RData")
-e_c_771_ROR_p <- report02_out_ridge(e_c_obj_771_RORprolif)
-```
-
-### Summery results: elastic net 771 genes bootstrap and repeated cross-validation
-```{r}
-data_table <- data.frame(
-  Model = c("prolif boot", "ROR-prolif boot", "prolif rep cross-val", "ROR-prolif rep cross-val"),
-  cor_mean = c(e_b_771_p$cor_mean, e_b_771_ROR_p$cor_mean, e_c_771_p$cor_mean, e_c_771_ROR_p$cor_mean),
-  sd_cor = c(e_b_771_p$cor_sd, e_b_771_ROR_p$cor_sd, e_c_771_p$cor_sd, e_c_771_ROR_p$cor_sd),
-  MSE_mean = c(e_b_771_p$MSE_mean, e_b_771_ROR_p$MSE_mean, e_c_771_p$MSE_mean, e_c_771_ROR_p$MSE_mean),
-  MSE_sd = c(e_b_771_p$MSE_sd, e_b_771_ROR_p$MSE_sd, e_c_771_p$MSE_sd, e_c_771_ROR_p$MSE_sd)
-)
-kable(data_table)
-```
-
-# Boosting with stumps as base learner - bootstrap
-### 771 genes -> proliferation score
-```{r}
-load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/xg_b_obj_771_p.RData")
-xg_b_771_p <- report02_out_ridge(xg_b_obj_771_p)
-```
-### 771 genes -> ROR-proliferation score
-```{r}
-load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/xg_b_obj_771_ROR_p.RData")
-xg_b_771_ROR_p <- report02_out_ridge(xg_b_obj_771_ROR_p)
-```
-
-# Boosting with stumps as base learner cross-validation
-### 771 genes -> proliferation score
-```{r}
-load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/xg_c_obj_771_prolif.RData")
-xg_c_771_p <- report02_out_ridge(xg_c_obj_771_prolif)
-```
-### 771 genes -> ROR-proliferation score
-```{r}
-load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/xg_c_obj_771_RORprolif.RData")
-xg_c_771_ROR_p <- report02_out_ridge(xg_c_obj_771_RORprolif)
-```
-
-### Summery results: Boosting with stumps 771 genes bootstrap and repeated cross-validation
-```{r}
-data_table <- data.frame(
-  Model = c("prolif boot", "ROR-prolif boot", "prolif rep cross-val", "ROR-prolif rep cross-val"),
-  cor_mean = c(xg_b_771_p$cor_mean, xg_b_771_ROR_p$cor_mean, xg_c_771_p$cor_mean, xg_c_771_ROR_p$cor_mean),
-  sd_cor = c(xg_b_771_p$cor_sd, xg_b_771_ROR_p$cor_sd, xg_c_771_p$cor_sd, xg_c_771_ROR_p$cor_sd),
-  MSE_mean = c(xg_b_771_p$MSE_mean, xg_b_771_ROR_p$MSE_mean, xg_c_771_p$MSE_mean, xg_c_771_ROR_p$MSE_mean),
-  MSE_sd = c(xg_b_771_p$MSE_sd, xg_b_771_ROR_p$MSE_sd, xg_c_771_p$MSE_sd, xg_c_771_ROR_p$MSE_sd)
-)
-kable(data_table)
-```
+# Ridge
+# Elastic Net
+# Boosting with stumps as base learner
 
 # Post Lasso
-not done
-
-# Summery of all results
-### Summery results: lasso proliferation score (bootstrap) 
-```{r}
-library(knitr)
-data_table <- data.frame(
-  Model = c("lasso 6 genes", "lasso 771 genes", "Nodes", "Residual additive", "Residual multiplicative"),
-  cor_mean = c(l_b_6_p$cor_mean, l_b_771_p$cor_mean, l_b_nodes_p$cor_mean, l_b_residuals_771_p_a$cor_mean, l_b_residuals_771_p_m$cor_mean),
-  sd_cor = c(l_b_6_p$cor_sd, l_b_771_p$cor_sd, l_b_nodes_p$cor_sd, l_b_residuals_771_p_a$cor_sd, l_b_residuals_771_p_m$cor_sd),
-  MSE_mean = c(l_b_6_p$MSE_mean, l_b_771_p$MSE_mean, l_b_nodes_p$MSE_mean, l_b_residuals_771_p_a$MSE_mean, l_b_residuals_771_p_m$MSE_mean),
-  MSE_sd = c(l_b_6_p$MSE_sd, l_b_771_p$MSE_sd, l_b_nodes_p$MSE_sd, l_b_residuals_771_p_a$MSE_sd, l_b_residuals_771_p_m$MSE_sd)
-)
-kable(data_table)
-```
-### Summery results: lasso ROR+proliferation score (bootstrap) 
-```{r}
-data_table <- data.frame(
-  Model = c("lasso 6 genes", "lasso 771 genes", "Nodes", "Residual additive", "Residual multiplicative"),
-  cor_mean = c(l_b_6_ROR_p$cor_mean, l_b_771_ROR_p$cor_mean, l_b_nodes_ROR_p$cor_mean, l_b_residuals_ROR_p_a$cor_mean, l_b_residuals_ROR_p_m$cor_mean),
-  sd_cor = c(l_b_6_ROR_p$cor_sd, l_b_771_ROR_p$cor_sd, l_b_nodes_ROR_p$cor_sd, l_b_residuals_ROR_p_a$cor_sd, l_b_residuals_ROR_p_m$cor_sd),
-  MSE_mean = c(l_b_6_ROR_p$MSE_mean, l_b_771_ROR_p$MSE_mean, l_b_nodes_ROR_p$MSE_mean, l_b_residuals_ROR_p_a$MSE_mean, l_b_residuals_ROR_p_m$MSE_mean),
-  MSE_sd = c(l_b_6_ROR_p$MSE_sd, l_b_771_ROR_p$MSE_sd, l_b_nodes_ROR_p$MSE_sd, l_b_residuals_ROR_p_a$MSE_sd, l_b_residuals_ROR_p_m$MSE_sd)
-)
-kable(data_table)
-```
-### Summery results: lasso proliferation score (repeated cross-validation) 
-```{r}
-library(knitr)
-data_table <- data.frame(
-  Model = c("lasso 6 genes", "lasso 771 genes", "Nodes", "Residual additive", "Residual multiplicative"),
-  cor_mean = c(l_c_6_p$cor_mean, l_c_771_p$cor_mean, l_c_nodes_p$cor_mean, l_c_residuals_771_p_a$cor_mean, l_c_residuals_771_p_m$cor_mean),
-  sd_cor = c(l_c_6_p$cor_sd, l_c_771_p$cor_sd, l_c_nodes_p$cor_sd, l_c_residuals_771_p_a$cor_sd, l_c_residuals_771_p_m$cor_sd),
-  MSE_mean = c(l_c_6_p$MSE_mean, l_b_771_p$MSE_mean, l_c_nodes_p$MSE_mean, l_c_residuals_771_p_a$MSE_mean, l_c_residuals_771_p_m$MSE_mean),
-  MSE_sd = c(l_c_6_p$MSE_sd, l_c_771_p$MSE_sd, l_c_nodes_p$MSE_sd, l_c_residuals_771_p_a$MSE_sd, l_c_residuals_771_p_m$MSE_sd)
-)
-kable(data_table)
-```
-### Summery results: lasso ROR+proliferation score (repeated cross-validation) 
-```{r}
-data_table <- data.frame(
-  Model = c("lasso 6 genes", "lasso 771 genes", "Nodes", "Residual additive", "Residual multiplicative"),
-  cor_mean = c(l_c_6_ROR_p$cor_mean, l_c_771_ROR_p$cor_mean, l_c_nodes_ROR_p$cor_mean, l_c_residuals_ROR_p_a$cor_mean, l_c_residuals_ROR_p_m$cor_mean),
-  sd_cor = c(l_c_6_ROR_p$cor_sd, l_c_771_ROR_p$cor_sd, l_c_nodes_ROR_p$cor_sd, l_c_residuals_ROR_p_a$cor_sd, l_c_residuals_ROR_p_m$cor_sd),
-  MSE_mean = c(l_c_6_ROR_p$MSE_mean, l_c_771_ROR_p$MSE_mean, l_c_nodes_ROR_p$MSE_mean, l_c_residuals_ROR_p_a$MSE_mean, l_c_residuals_ROR_p_m$MSE_mean),
-  MSE_sd = c(l_c_6_ROR_p$MSE_sd, l_c_771_ROR_p$MSE_sd, l_c_nodes_ROR_p$MSE_sd, l_c_residuals_ROR_p_a$MSE_sd, l_c_residuals_ROR_p_m$MSE_sd)
-)
-kable(data_table)
-```
-
-### Summery results: ridge 771 genes bootstrap and repeated cross-validation
-```{r}
-data_table <- data.frame(
-  Model = c("prolif boot", "ROR-prolif boot", "prolif rep cross-val", "ROR-prolif rep cross-val"),
-  cor_mean = c(r_b_771_p$cor_mean, r_b_771_ROR_p$cor_mean, r_c_771_p$cor_mean, r_c_771_ROR_p$cor_mean),
-  sd_cor = c(r_b_771_p$cor_sd, r_b_771_ROR_p$cor_sd, r_c_771_p$cor_sd, r_c_771_ROR_p$cor_sd),
-  MSE_mean = c(r_b_771_p$MSE_mean, r_b_771_ROR_p$MSE_mean, r_c_771_p$MSE_mean, r_c_771_ROR_p$MSE_mean),
-  MSE_sd = c(r_b_771_p$MSE_sd, r_b_771_ROR_p$MSE_sd, r_c_771_p$MSE_sd, r_c_771_ROR_p$MSE_sd)
-)
-kable(data_table)
-```
-### Summery results: elastic net 771 genes bootstrap and repeated cross-validation
-```{r}
-data_table <- data.frame(
-  Model = c("prolif boot", "ROR-prolif boot", "prolif rep cross-val", "ROR-prolif rep cross-val"),
-  cor_mean = c(e_b_771_p$cor_mean, e_b_771_ROR_p$cor_mean, e_c_771_p$cor_mean, e_c_771_ROR_p$cor_mean),
-  sd_cor = c(e_b_771_p$cor_sd, e_b_771_ROR_p$cor_sd, e_c_771_p$cor_sd, e_c_771_ROR_p$cor_sd),
-  MSE_mean = c(e_b_771_p$MSE_mean, e_b_771_ROR_p$MSE_mean, e_c_771_p$MSE_mean, e_c_771_ROR_p$MSE_mean),
-  MSE_sd = c(e_b_771_p$MSE_sd, e_b_771_ROR_p$MSE_sd, e_c_771_p$MSE_sd, e_c_771_ROR_p$MSE_sd)
-)
-kable(data_table)
-```
-### Summery results: Boosting with stumps 771 genes bootstrap and repeated cross-validation
-```{r}
-data_table <- data.frame(
-  Model = c("prolif boot", "ROR-prolif boot", "prolif rep cross-val", "ROR-prolif rep cross-val"),
-  cor_mean = c(xg_b_771_p$cor_mean, xg_b_771_ROR_p$cor_mean, xg_c_771_p$cor_mean, xg_c_771_ROR_p$cor_mean),
-  sd_cor = c(xg_b_771_p$cor_sd, xg_b_771_ROR_p$cor_sd, xg_c_771_p$cor_sd, xg_c_771_ROR_p$cor_sd),
-  MSE_mean = c(xg_b_771_p$MSE_mean, xg_b_771_ROR_p$MSE_mean, xg_c_771_p$MSE_mean, xg_c_771_ROR_p$MSE_mean),
-  MSE_sd = c(xg_b_771_p$MSE_sd, xg_b_771_ROR_p$MSE_sd, xg_c_771_p$MSE_sd, xg_c_771_ROR_p$MSE_sd)
-)
-kable(data_table)
-```

### 2023-03-25 R_codeP01/reports/MS2_report03_truncated.Rmd
sparse group lasso on clinical data

--- 2023-03-23 R_codeP01/reports/MS2_report02_truncated.Rmd
@@
 ```{r global-options, include=FALSE}
+library(tidyverse)
+library(knitr)
 knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='Figs/',
@@
 ```
+
 ### 6 genes -> ROR_proliferation score
@@
 ```
+
 ### 771 genes -> ROR-proliferation score
@@
 ```
+
 ### node values -> ROR-proliferation score
@@
 ```
+
 ### Mechanistic + Residuals -> proliferation score (multiplicative)
@@
 ```
+
 ### Mechnaistic + Residuals -> ROR-proliferation score (additive)
@@
 ```
+
 ### Mechnaistic + Residuals -> ROR-proliferation score (multiplicative)
@@
 
+### Sparse Group Lasso: 771 genes -> ROR-proliferation score + interactions between PCs
+```{r}
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/sgl_c_771_RORprolif.RData")
+sgl_c_771_RORprolif <- report02_out(sgl_c_771_RORprolif)
+```
+
 # Post Lasso
@@
 library(knitr)
-data_table <- data.frame(
+data_table <- tibble(
   Model = c("lasso 6 genes", "lasso 771 genes", "Nodes", "Residual additive", "Residual multiplicative"),
@@
 )
-kable(data_table)
+data_table |>  mutate(across(where(is.numeric), ~ round(., digits = 3))) |>  kable()
 ```
+
 ### Summery results: lasso ROR+proliferation score (bootstrap) 
 ```{r}
-data_table <- data.frame(
+data_table <- tibble(
   Model = c("lasso 6 genes", "lasso 771 genes", "Nodes", "Residual additive", "Residual multiplicative"),
@@
 )
-kable(data_table)
+data_table |>  mutate(across(where(is.numeric), ~ round(., digits = 3))) |>  kable()
 ```
+
 ### Summery results: lasso proliferation score (repeated cross-validation) 
@@
 )
-kable(data_table)
+data_table |>  mutate(across(where(is.numeric), ~ round(., digits = 3))) |>  kable()
 ```
+
 ### Summery results: lasso ROR+proliferation score (repeated cross-validation) 
 ```{r}
-data_table <- data.frame(
+data_table <- tibble(
   Model = c("lasso 6 genes", "lasso 771 genes", "Nodes", "Residual additive", "Residual multiplicative"),
@@
 )
-kable(data_table)
+data_table |>  mutate(across(where(is.numeric), ~ round(., digits = 3))) |>  kable()
 ```
@@
 ```{r}
-data_table <- data.frame(
+data_table <- tibble(
   Model = c("prolif boot", "ROR-prolif boot", "prolif rep cross-val", "ROR-prolif rep cross-val"),
@@
 )
-kable(data_table)
+data_table |>  mutate(across(where(is.numeric), ~ round(., digits = 3))) |>  kable()
 ```
+
 ### Summery results: elastic net 771 genes bootstrap and repeated cross-validation
 ```{r}
-data_table <- data.frame(
+data_table <- tibble(
   Model = c("prolif boot", "ROR-prolif boot", "prolif rep cross-val", "ROR-prolif rep cross-val"),
@@
 )
-kable(data_table)
+data_table |>  mutate(across(where(is.numeric), ~ round(., digits = 3))) |>  kable()
 ```
+
 ### Summery results: Boosting with stumps 771 genes bootstrap and repeated cross-validation
 ```{r}
-data_table <- data.frame(
+data_table <- tibble(
   Model = c("prolif boot", "ROR-prolif boot", "prolif rep cross-val", "ROR-prolif rep cross-val"),
@@
 ```{r}
-data_table <- data.frame(
+data_table <- tibble(
   Model = c("ridge", "ridge_interac", "lasso", "lasso_interact", "elastic", "elastic_interact"),
@@
 ```{r}
-data_table <- data.frame(
-  Model = c("Lasso", "Ridge", "ElasticNet", "Boosting", "Residual (lasso/additive)", 
+# Create a data frame
+data_table <- tibble(
+  Model = c("Lasso", "Ridge", "ElasticNet", "Boosting", "Residual (lasso/additive)", "Sparse group lasso",
             "PCA ON GENE SETS", "ridge", "ridge_interac", "lasso", "lasso_interact", "elastic", "elastic_interact", 
@@
     l_c_residuals_ROR_p_a$cor_mean,
-    "",
+    sgl_c_771_RORprolif$cor_mean,
+    NA,
     r_pca_c_771_RORprolif$cor_mean, 
@@
     en_pca_c_interact_771_RORprolif$cor_mean,
-    "", 
+    NA, 
     r_stack_c_771_RORprolif$cor_mean, 
@@
     l_c_residuals_ROR_p_a$cor_sd,
-    "",
+    sgl_c_771_RORprolif$cor_sd,
+    NA,
     r_pca_c_771_RORprolif$cor_sd, 
@@
     en_pca_c_interact_771_RORprolif$cor_sd,
-    "",
+    NA,
     r_stack_c_771_RORprolif$cor_sd, 
@@
     l_c_residuals_ROR_p_a$MSE_mean,
-    "", 
+    sgl_c_771_RORprolif$MSE_mean,
+    NA, 
     r_pca_c_771_RORprolif$MSE_mean, 
@@
     en_pca_c_interact_771_RORprolif$MSE_mean,
-    "",
+    NA,
     r_stack_c_771_RORprolif$MSE_mean, 
@@
     l_c_residuals_ROR_p_a$MSE_sd,
-    "",
+    sgl_c_771_RORprolif$MSE_sd,
+    NA,
     r_pca_c_771_RORprolif$MSE_sd, 
@@
     en_pca_c_interact_771_RORprolif$MSE_sd,
-    "",
+    NA,
     r_stack_c_771_RORprolif$MSE_sd,
@@
 )
-kable(data_table)
+
+# Create a custom function to replace NAs with empty strings
+replace_na_with_blank <- function(x) {
+  if (is.numeric(x)) {
+    ifelse(is.na(x), "", round(x, digits = 3))
+  } else {
+    x
+  }
+}
+
+# Apply the custom function to the data_table
+data_table <- data_table %>%
+  mutate(across(everything(), replace_na_with_blank))
+
+data_table %>% kable()
+
+#data_table <- data_table |> mutate(across(where(is.numeric), ~ round(., digits = 3))) 
+#data_table |>  kable()
+
 ```

### 2023-03-25 R_codeP01/scripts/00_packages01.R

@@ -6,6 +6,8 @@ library(tidymodels)
 library(dplyr)
 library(ggplot2)
 
+library(gridExtra)
+
 library(glmnet)
 library(boot)
 library(caret)
@@ -17,6 +19,9 @@ library(sparsgel)
 
 install.packages("grpreg")
 install.packages("sparsegl")
+
+install.packages("gridExtra")
+
 
 # Install and load the sparsgel package
 if (!requireNamespace("sparsgel", quietly = TRUE)) {

### 2023-03-25 R_codeP01/scripts/34_sparse_gr_02.R

@@ -1,6 +1,6 @@
-###################################################################
+############################################################################
 ## Repeated cross-validation for testing Sparse-group Lasso with SPARSGEL ##
-###################################################################
+############################################################################
 ##
 ## Test against the fold
 ## Cross-validation (5-fold) used for training/tuning lambda and selecting features
@@ -11,72 +11,66 @@ char_list <- list(imm_inf_ = char_immune_inf,
                   ER_sing_ = char_ER_signaling,
                   anti_pres_ = char_antigen_present,
                   angiogen_ = char_angiogenesis
-)
+                  )
 
 
-
-prepare_group_index_vector <- function(df, col_groups) {
+prepare_group_index_vector <- function(df, dic_groups) {
   # Input
   # df = dataframe containing with predictors and response variable in first column
   # col_groups = a list of character vectors, where each vector contains the column names belonging to the same group
   # Output: group assignment vector with 0 where variables where not assign to a specific group
   
   # Initialize the group assignment vector
-  group <- rep(0, ncol(df)-1)
+  groups <- rep(0, ncol(df)-1)
   
   # Remove the response variable from the dataframe
   predictor_df <- df[, -1]
   
   # Assign group numbers to predictors within choosen groups as defined by col_groups
   group_number <- 1
-  for (group_cols in col_groups) {
+  for (group_cols in dic_groups) {
     for (col in group_cols) {
       col_index <- which(colnames(predictor_df) == col)
-      group[col_index] <- group_number
+      groups[col_index] <- group_number
     }
     group_number <- group_number + 1
   }
   
-  return(group)
+  return(groups)
 }
 
 
-# Sparse Group Lasso function with grouped and ungrouped predictors
-sparse_group_lasso_sparsegl <- function(df, group) {
[…]

### 2023-03-25 R_codeP01/scripts/40_iterative_syn_01.R

@@ -1,6 +1,6 @@
 
 
-synergistic <- function(df, char_list, alpha = 0.5, lambda_seq = NULL, nfolds = 5, tol = 1e-4, max_iters = 100) {
+synergistic <- function(df, char_list, alpha=0.5, nfolds=5, tol=1e-4, max_iters=100) {
   # Extract predictor matrix and response vector; assuming response variable in first column
   X <- as.matrix(df[, -1])
   X <- scale(X)
@@ -17,7 +17,7 @@ synergistic <- function(df, char_list, alpha = 0.5, lambda_seq = NULL, nfolds = 
   }
   
   # learn betas without interaction terms to get starting beta values, using ridge
-  fit_beta0 <- cv.glmnet(X, y, alpha = 0, lambda = lambda_seq, nfolds = nfolds)
+  fit_beta0 <- cv.glmnet(X, y, alpha = 0, nfolds = nfolds)
   best_lambda <- fit_beta0$lambda.min
   beta_main <- coef(fit_beta0, s = best_lambda)[-1]  # exclude intercept
   
@@ -66,7 +66,7 @@ synergistic <- function(df, char_list, alpha = 0.5, lambda_seq = NULL, nfolds = 
     pf[pf == 0] <- 1e-2
     pf <- 1 / pf
     pf[(ncol(X) + 1):length(betas)] <- 0
-    fit_with_interactions <- cv.glmnet(X_with_interactions, y, alpha = alpha, lambda = lambda_seq, nfolds = nfolds, penalty.factor = pf)
+    fit_with_interactions <- cv.glmnet(X_with_interactions, y, alpha=alpha, nfolds=nfolds, penalty.factor = pf)
     best_lambda <- fit_with_interactions$lambda.min
     
     # Update betas using the new beta values
@@ -104,10 +104,49 @@ synergistic <- function(df, char_list, alpha = 0.5, lambda_seq = NULL, nfolds = 
   })
   named_beta_interaction <- setNames(beta_interaction, interaction_names)
   
-  return(list(obj_diff=obj_diff, beta_main = named_beta_main, beta_interaction = named_beta_interaction, iterations = iter, best_lambda = best_lambda))
+  return(list(model=fit_with_interactions, obj_diff=obj_diff, beta_main = named_beta_main, beta_interaction = named_beta_interaction, iterations = iter, best_lambda = best_lambda))
  }
 
[…]

### 2023-03-25 R_codeP01/scripts/40_iterative_syn_02.R

@@ -56,31 +56,26 @@ synergistic <- function(df, char_list, alpha = 0.5, lambda_seq = NULL, nfolds = 
       interactions[, i] <- interaction_terms(X, beta_main, group1, group2)
     }
     
-    
+    # Remove interactions terms = 0
     interactions_sd = apply(interactions, 2, sd)
-    interactions = interactions[, interactions_sd != 0]
-    print(dim(interactions))
+    interactions_scaled = interactions[, interactions_sd != 0]
+    
     # Make feature matrix with original features and interactions
-    X_with_interactions <- cbind(X, interactions)
+    X_with_interactions <- cbind(X, interactions_scaled)
     
     # Fit model using adaptive elastic-net
-    #pf <- betas
-    
     pf <- rep(1, ncol(X_with_interactions))
-    print(length(pf))
     pf[1:ncol(X)] <- betas[1:ncol(X)] 
     pf[pf == 0] <- 1e-2
     pf <- 1 / pf
-    if (ncol(dim(interactions)[2]) > 0) {
+    if (ncol(interactions_scaled) > 0) {
       pf[(ncol(X) + 1):ncol(X_with_interactions)] <- 0
     }
-    print(length(pf))
     fit_with_interactions <- cv.glmnet(X_with_interactions, y, alpha = alpha, lambda = lambda_seq, nfolds = nfolds, penalty.factor = pf)
     best_lambda <- fit_with_interactions$lambda.min
     
     # Update betas using the new beta values
     new_betas <- as.vector(coef(fit_with_interactions))[-1]  # exclude intercept
-    
     new_beta_main <- new_betas[1:ncol(X)]
     
     best_lambda_idx <- which(fit_with_interactions$lambda == best_lambda)
@@ -101,8 +96,7 @@ synergistic <- function(df, char_list, alpha = 0.5, lambda_seq = NULL, nfolds = 
     
     obj_diff <- c(obj_diff, dev_glmnet)
   }
-  # betas <- new_betas
-  # beta_interaction <- betas[(ncol(X) + 1):length(betas)]
+
   beta_interaction <- betas[ncol(X) + 1:ncol(interactions)]
   
   # make named vectors for beta_main and beta_interaction
@@ -117,7 +111,7 @@ synergistic <- function(df, char_list, alpha = 0.5, lambda_seq = NULL, nfolds = 
[…]

### 2023-03-25 R_codeP01/scripts/90_output01.R

@@ -3,6 +3,7 @@
 #################################
 
 library(ggplot2)
+library(gridExtra)
 
 report02_out <- function(object){
   cor_vec <- object$cor_vec
@@ -19,21 +20,10 @@ report02_out <- function(object){
   cor_median <- median(cor_vec, na.rm=TRUE)
   cat("Median:", cor_median, "\n")
   cor_var <- var(cor_vec, na.rm=TRUE)
-  cat("Variance:", cor_var, "\n")
+  # cat("Variance:", cor_var, "\n")
   cor_sd <- sd(na.omit(cor_vec)) 
   cat("st.dev.:", cor_sd, "\n")
-  
-  # Histogram correlations
-  correlations_finite <- cor_vec[is.finite(cor_vec)]
-  cor_df <- data.frame(correlation = correlations_finite)
-  
-  h <- ggplot(cor_df, aes(x=correlation)) +
-    geom_histogram(bins = 30, color = "black", fill = "white") +
-    xlab("Correlation") +
-    ylab("Frequency") +
-    ggtitle("Histogram of Correlation Values")
-  show(h)
-
+  cat("\n")
   
   ## MSE
   cat("MSE RESULTS", "\n")
@@ -43,26 +33,64 @@ report02_out <- function(object){
   MSE_median <- median(MSE_vec, na.rm=TRUE)
   cat("Median:", MSE_median, "\n")
   MSE_var <- var(MSE_vec, na.rm=TRUE)
-  cat("Variance:", MSE_var, "\n")
+  # cat("Variance:", MSE_var, "\n")
   MSE_sd <- sd(na.omit(MSE_vec)) 
   cat("st.dev.:", MSE_sd)
+  cat("\n")
   
-  
-  # Histogram MSE
-  MSE_df <- data.frame(MSE = MSE_vec)
-  
-  h <- ggplot(MSE_df, aes(x=MSE)) +
-    geom_histogram(bins = 30, color = "black", fill = "white") +
-    xlab("MSE") +
-    ylab("Frequency") +
-    ggtitle("Histogram of MSE Values")
-  show(h)
   
   ## Most prevalent Features
+  
   # Order the features based on their selection frequency
   coef_matrix <- object$coef_matrix
   frequency <- data.frame(Feature = colnames(coef_matrix), Frequency = colSums(coef_matrix != 0) / (n_models))
   frequency <- frequency[order(frequency$Frequency, decreasing = TRUE),]
+  
+  # extract the top features
+  perc_best <- 0.5 # how often they where selected in percentage
[…]

### 2023-03-25 R_codeP01/scripts/TIPS.R

@@ -29,6 +29,6 @@ sum(a %in% as.vector(char_list$ER_sing_))
 [1] 4
 
 
-lapply(char_list, function(xx) sum(a %in% as.vector(xx)))
+
 
 

### 2023-03-26 R_codeP01/reports/MS2_report03_truncated.Rmd
report writing

@@
 # Lasso - Bootstrap
-### 6 genes -> proliferation score
+### 6 genes -> proliferation score (lasso - bootstrap)
 ```{r}
@@
 
-### 6 genes -> ROR_proliferation score
+### 6 genes -> ROR_proliferation score (lasso - bootstrap)
 ```{r}
@@
 
-### 771 genes -> proliferation score
+### 771 genes -> proliferation score (lasso - bootstrap)
 ```{r}
@@
 
-### 771 genes -> ROR-proliferation score
+### 771 genes -> ROR-proliferation score (lasso - bootstrap)
 ```{r}
@@
 
-### node values -> proliferation score
+### node values -> proliferation score (lasso - bootstrap)
 ```{r}
@@
 
-### node values -> ROR-proliferation score
+### node values -> ROR-proliferation score (lasso - bootstrap) 
 ```{r}
@@
 
-### Mechanistic + Residuals -> proliferation score (additive)
+### Mechanistic + Residuals (additive) -> proliferation score  (lasso - bootstrap)
 ```{r}
@@
 
-### Mechanistic + Residuals -> proliferation score (multiplicative)
+### Mechanistic + Residuals (multiplicative) -> proliferation score   (lasso - bootstrap)
 ```{r}
@@
 
-### Mechnaistic + Residuals -> ROR-proliferation score (additive)
+### Mechnaistic + Residuals (additive) -> ROR-proliferation score  (lasso - bootstrap)
 ```{r}
@@
 
-### Mechnaistic + Residuals -> ROR-proliferation score (multiplicative)
+### Mechnaistic + Residuals (multiplicative) -> ROR-proliferation score (lasso - bootstrap)
 ```{r}
@@
 
-### 6 genes -> proliferation score
+### 6 genes -> proliferation score (lasso - repeated cross-validation)
 ```{r}
@@
 ```
-### 6 genes -> ROR_proliferation score
+### 6 genes -> ROR_proliferation score (lasso - repeated cross-validation)
 ```{r}
@@
 
-### 771 genes -> proliferation score
+### 771 genes -> proliferation score (lasso - repeated cross-validation)
 ```{r}
@@
 
-### 771 genes -> ROR-proliferation score
+### 771 genes -> ROR-proliferation score (lasso - repeated cross-validation)
 ```{r}
@@
 
-### node values -> proliferation score
+### node values -> proliferation score (lasso - repeated cross-validation)
 ```{r}
@@
 
-### node values -> ROR-proliferation score
+### node values -> ROR-proliferation score (lasso - repeated cross-validation)
 ```{r}
@@
 
-### Mechanistic + Residuals -> proliferation score (additive)
+### Mechanistic + Residuals (additive) -> proliferation score (lasso - repeated cross-validation)
 ```{r}
@@
 
-### Mechanistic + Residuals -> proliferation score (multiplicative)
+### Mechanistic + Residuals (multiplicative) -> proliferation score (lasso - repeated cross-validation)
 ```{r}
@@
 
-### Mechnaistic + Residuals -> ROR-proliferation score (additive)
+### Mechnaistic + Residuals (additive) -> ROR-proliferation score (lasso - repeated cross-validation)
 ```{r}
@@
 
-### Mechnaistic + Residuals -> ROR-proliferation score (multiplicative)
+### Mechnaistic + Residuals (multiplicative) -> ROR-proliferation score (lasso - repeated cross-validation)
 ```{r}
@@
 # Ridge bootstrap
-### 771 genes -> proliferation score
+### 771 genes -> proliferation score (ridge bootstrap)
 ```{r}
@@
 
-### 771 genes -> ROR-proliferation score
+### 771 genes -> ROR-proliferation score (ridge bootstrap)
 ```{r}
@@
 # Ridge repeated cross-validation
-### 771 genes -> proliferation score
+### 771 genes -> proliferation score (ridge repeated cross-validation)
 ```{r}
@@
 
-### 771 genes -> ROR-proliferation score
+### 771 genes -> ROR-proliferation score (ridge repeated cross-validation)
 ```{r}
-load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/r_c_obj_771_RORprolif.RData")
-r_c_771_ROR_p <- report02_out_ridge(r_c_obj_771_RORprolif)
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/r_c_771_RORprolif.RData")
+r_c_771_ROR_p <- report02_out_ridge(r_c_771_RORprolif)
 ```
@@
 # Elastic Net - bootstrap
-### 771 genes -> proliferation score
+### 771 genes -> proliferation score (elastic Net - bootstrap)
 ```{r}
@@
 
-### 771 genes -> ROR-proliferation score
+### 771 genes -> ROR-proliferation score (elastic Net - bootstrap)
 ```{r}
@@
 # Elastic Net: cross-validation
-### 771 genes -> proliferation score
+### 771 genes -> proliferation score  (elastic Net - repeated cross-validation)
 ```{r}
@@
 
-### 771 genes -> ROR-proliferation score
+### 771 genes -> ROR-proliferation score  (elastic Net - repeated cross-validation)
 ```{r}
@@
 # Boosting with stumps as base learner - bootstrap
-### 771 genes -> proliferation score
+### 771 genes -> proliferation score (boosting - bootstrap)
 ```{r}
@@
 
-### 771 genes -> ROR-proliferation score
+### 771 genes -> ROR-proliferation score  (boosting - bootstrap)
 ```{r}
@@
 # Boosting with stumps as base learner cross-validation
-### 771 genes -> proliferation score
+### 771 genes -> proliferation score  (boosting - rep cross-val)
 ```{r}
@@
 
-### 771 genes -> ROR-proliferation score
+### 771 genes -> ROR-proliferation score   (boosting - rep cross-val)
 ```{r}

### 2023-03-26 R_codeP01/scripts/05_rigde_rc_03.R

@@ -68,37 +68,37 @@ ridge_sample <- function(train_data, alpha=0){
 repeats = 200
 folds = 5
 
-# RUN: r_c_obj_771_prolif
+# RUN: r_c_771_prolif
 set.seed(123)
-r_c_obj_771_prolif <- ridge_rep_cv(prolif_771genes, func=ridge_sample, folds, repeats, method="pearson")
-head(r_c_obj_771_prolif$coef_matrix)[,1:6]
-save(r_c_obj_771_prolif, file="/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/r_c_obj_771_prolif.RData")
-load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/r_c_obj_771_prolif.RData")
+r_c_771_prolif <- ridge_rep_cv(prolif_771genes, func=ridge_sample, folds, repeats, method="pearson")
+head(r_c_771_prolif$coef_matrix)[,1:6]
+save(r_c_771_prolif, file="/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/r_c_771_prolif.RData")
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/r_c_771_prolif.RData")
 
-# RUN: r_c_obj_771_RORprolif
+# RUN: r_c_771_RORprolif
 set.seed(123)
-r_c_obj_771_RORprolif <- lasso_rep_cv(RORprolif_771genes, func=lasso_sample, folds, repeats, method="pearson")
-head(r_c_obj_771_RORprolif$coef_matrix)[,1:6]
-save(r_c_obj_771_RORprolif, file="/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/r_c_obj_771_RORprolif.RData")
-load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/r_c_obj_771_RORprolif.RData")
+r_c_771_RORprolif <- ridge_rep_cv(ROR_prolif_771genes, func=ridge_sample, folds, repeats, method="pearson")
+head(r_c_771_RORprolif$coef_matrix)[,1:6]
+save(r_c_771_RORprolif, file="/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/r_c_771_RORprolif.RData")
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/r_c_771_RORprolif.RData")
[…]

### 2023-03-26 R_codeP01/scripts/40_iterative_syn_02.R

@@ -1,3 +1,5 @@
+
+
 synergistic <- function(df, char_list, alpha = 0.5, lambda_seq = NULL, nfolds = 5, tol = 1e-4, max_iters = 100) {
   # Extract predictor matrix and response vector; assuming response variable in first column
   X <- as.matrix(df[, -1])
@@ -111,7 +113,7 @@ synergistic <- function(df, char_list, alpha = 0.5, lambda_seq = NULL, nfolds = 
   return(list(obj_diff=obj_diff, beta_main = named_beta_main, beta_interaction = named_beta_interaction, iterations = iter, best_lambda = best_lambda))
  }
 
-result <- synergistic(ROR_prolif_771genes, char_list, alpha = 0.0001, lambda_seq = NULL, nfolds = 5, tol = 1e-6, max_iters = 3)
+result <- synergistic(ROR_prolif_771genes, char_list, alpha = 0.1, lambda_seq = NULL, nfolds = 5, tol = 1e-5, max_iters = 100)
 
 
 char_list <- list(imm_inf_ = char_immune_inf,

### 2023-03-26 R_codeP01/scripts/90_output_ridge_01.R

@@ -3,6 +3,7 @@
 ###############################################################################
 
 library(ggplot2)
+library(gridExtra)
 
 report02_out_ridge <- function(object){
   cor_vec <- object$cor_vec
@@ -19,20 +20,10 @@ report02_out_ridge <- function(object){
   cor_median <- median(cor_vec, na.rm=TRUE)
   cat("Median:", cor_median, "\n")
   cor_var <- var(cor_vec, na.rm=TRUE)
-  cat("Variance:", cor_var, "\n")
+  # cat("Variance:", cor_var, "\n")
   cor_sd <- sd(na.omit(cor_vec)) 
   cat("st.dev.:", cor_sd, "\n")
-  
-  # Histogram correlations
-  correlations_finite <- cor_vec[is.finite(cor_vec)]
-  cor_df <- data.frame(correlation = correlations_finite)
-  
-  h <- ggplot(cor_df, aes(x=correlation)) +
-    geom_histogram(bins = 30, color = "black", fill = "white") +
-    xlab("Correlation") +
-    ylab("Frequency") +
-    ggtitle("Histogram of Correlation Values")
-  show(h)
+  cat("\n")
   
   ## MSE
   cat("MSE RESULTS", "\n")
@@ -42,20 +33,33 @@ report02_out_ridge <- function(object){
   MSE_median <- median(MSE_vec, na.rm=TRUE)
   cat("Median:", MSE_median, "\n")
   MSE_var <- var(MSE_vec, na.rm=TRUE)
-  cat("Variance:", MSE_var, "\n")
+  # cat("Variance:", MSE_var, "\n")
   MSE_sd <- sd(na.omit(MSE_vec)) 
   cat("st.dev.:", MSE_sd)
+  cat("\n")
   
+  ## HISTOGRAMS
+  # Histogram correlations
+  correlations_finite <- cor_vec[is.finite(cor_vec)]
+  cor_df <- data.frame(correlation = correlations_finite)
+  
+  h1 <- ggplot(cor_df, aes(x=correlation)) +
+    geom_histogram(bins = 30, color = "black", fill = "white") +
+    xlab("Correlation") +
+    ylab("Frequency") +
+    ggtitle("Histogram of Correlation Values")
   
   # Histogram MSE
   MSE_df <- data.frame(MSE = MSE_vec)
   
-  h <- ggplot(MSE_df, aes(x=MSE)) +
+  h2 <- ggplot(MSE_df, aes(x=MSE)) +
[…]

### 2023-03-31 R_codeP01/reports/MS2_report03_truncated.Rmd
sma adjustment of report

@@
 
-### Lasso: 771 genes -> ROR-proliferation score
+### Lasso/pca: 771 genes -> ROR-proliferation score
 ```{r}
@@
 
-### ElasticNet: 771 genes -> ROR-proliferation score
+### ElasticNet/pca: 771 genes -> ROR-proliferation score
 ```{r}
@@
 
-### Ridge: 771 genes -> ROR-proliferation score
+### Ridge/stack: 771 genes -> ROR-proliferation score
 ```{r}
@@
 
-### Ridge: 771 genes -> ROR-proliferation score + interactions between PCs
+### Ridge/stack: 771 genes -> ROR-proliferation score + interactions between base models
 ```{r}
@@
 
-### Lasso: 771 genes -> ROR-proliferation score
+### Lasso/stack: 771 genes -> ROR-proliferation score
 ```{r}
@@
 
-### Lasso: 771 genes -> ROR-proliferation score + interactions between PCs
+### Lasso/stack: 771 genes -> ROR-proliferation score + interactions between base models
 ```{r}
@@
 
-### ElasticNet: 771 genes -> ROR-proliferation score
+### ElasticNet/stack: 771 genes -> ROR-proliferation score
 ```{r}
@@
 
-### ElasticNet: 771 genes -> ROR-proliferation score + interactions between PCs
+### ElasticNet/stack: 771 genes -> ROR-proliferation score + interactions base models
 ```{r}

### 2023-03-31 R_codeP01/scripts/33_ensemble_stack_04.R

@@ -118,7 +118,7 @@ stacking_rep_cv <- function(df_data, named_list, alpha0=0, alpha1=0.5, folds=5, 
   
   return(list(cor_vec=cor_vec, coef_matrix=coef_matrix, MSE_vec=MSE_vec))
 }
-
+set.seed(1)
 t3 <- stacking_rep_cv(ROR_prolif_771genes, char_list, alpha0=0, alpha1=0.5, folds=5, repeats=20, interactions=FALSE, method="pearson")
 t3 <- stacking_rep_cv(ROR_prolif_771genes, char_list, alpha0=0, alpha1=0.5, folds=5, repeats=20, interactions=TRUE, method="pearson")
 mean(t3$cor_vec)

### 2023-04-12 R_codeP01/reports/MS2_report04_truncated.Rmd
making figures for the standard models

--- 2023-03-31 R_codeP01/reports/MS2_report03_truncated.Rmd
@@
 
-1. Repeated cross-validations (200 rep, 5-fold)
+1. Repeated cross-validations (200 repeats of 5 fold cross-validation)
 
@@
 ### Stacking using different features in the base models
-### Sparse group lasso (not done)
+### Group lasso (not done)
+### Sparse group lasso (done)
 ### Iterative learning (ongoing)
@@
 
-# Results of individual modles:
+# Results of individual models:
 
@@
 source("/Users/anders/Documents/Master/Cancer/R_codeP01/scripts/90_output_ridge_01.R")
-```
-
-# Lasso - Bootstrap
-### 6 genes -> proliferation score (lasso - bootstrap)
-```{r}
-load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_6_prolif.RData")
-l_b_6_p <- report02_out(lb_obj_6_prolif)
-```
-
-### 6 genes -> ROR_proliferation score (lasso - bootstrap)
-```{r}
-load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_6_RORprolif.RData")
-l_b_6_ROR_p <- report02_out(lb_obj_6_RORprolif)
-```
-
-### 771 genes -> proliferation score (lasso - bootstrap)
-```{r}
-load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_771_prolif.RData")
-l_b_771_p <- report02_out(lb_obj_771_prolif)
-```
-
-### 771 genes -> ROR-proliferation score (lasso - bootstrap)
-```{r}
-load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_771_RORprolif.RData")
-l_b_771_ROR_p <- report02_out(lb_obj_771_RORprolif)
-```
-
-### node values -> proliferation score (lasso - bootstrap)
-```{r}
-load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_nodes_prolif.RData")
-l_b_nodes_p <- report02_out(lb_obj_nodes_prolif)
-```
-
-### node values -> ROR-proliferation score (lasso - bootstrap) 
-```{r}
-load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_nodes_RORprolif.RData")
-l_b_nodes_ROR_p <- report02_out(lb_obj_nodes_RORprolif)
-```
-
-### Mechanistic + Residuals (additive) -> proliferation score  (lasso - bootstrap)
-```{r}
-load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_residuals_771_prolif_a.RData")
-l_b_residuals_771_p_a <- report02_out(lb_obj_residuals_771_prolif_a)
-```
-
-### Mechanistic + Residuals (multiplicative) -> proliferation score   (lasso - bootstrap)
-```{r}
-load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_residuals_771_prolif_m.RData")
-l_b_residuals_771_p_m <- report02_out(lb_obj_residuals_771_prolif_m)
-```
-
-### Mechnaistic + Residuals (additive) -> ROR-proliferation score  (lasso - bootstrap)
-```{r}
-load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_residuals_771_RORprolif_a.RData")
-l_b_residuals_ROR_p_a <- report02_out(lb_obj_residuals_771_RORprolif_a)
-```
-
-### Mechnaistic + Residuals (multiplicative) -> ROR-proliferation score (lasso - bootstrap)
-```{r}
-load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_residuals_771_RORprolif_m.RData")
-l_b_residuals_ROR_p_m <- report02_out(lb_obj_residuals_771_RORprolif_m)
-```
-
-### Summery results: lasso proliferation score (bootstrap) 
-```{r}
-library(knitr)
-data_table <- data.frame(
-  Model = c("lasso 6 genes", "lasso 771 genes", "Nodes", "Residual additive", "Residual multiplicative"),
-  cor_mean = c(l_b_6_p$cor_mean, l_b_771_p$cor_mean, l_b_nodes_p$cor_mean, l_b_residuals_771_p_a$cor_mean, l_b_residuals_771_p_m$cor_mean),
-  sd_cor = c(l_b_6_p$cor_sd, l_b_771_p$cor_sd, l_b_nodes_p$cor_sd, l_b_residuals_771_p_a$cor_sd, l_b_residuals_771_p_m$cor_sd),
-  MSE_mean = c(l_b_6_p$MSE_mean, l_b_771_p$MSE_mean, l_b_nodes_p$MSE_mean, l_b_residuals_771_p_a$MSE_mean, l_b_residuals_771_p_m$MSE_mean),
-  MSE_sd = c(l_b_6_p$MSE_sd, l_b_771_p$MSE_sd, l_b_nodes_p$MSE_sd, l_b_residuals_771_p_a$MSE_sd, l_b_residuals_771_p_m$MSE_sd)
-)
-kable(data_table)
-```
-
-### Summery results: lasso ROR+proliferation score (bootstrap) 
-```{r}
-data_table <- data.frame(
-  Model = c("lasso 6 genes", "lasso 771 genes", "Nodes", "Residual additive", "Residual multiplicative"),
-  cor_mean = c(l_b_6_ROR_p$cor_mean, l_b_771_ROR_p$cor_mean, l_b_nodes_ROR_p$cor_mean, l_b_residuals_ROR_p_a$cor_mean, l_b_residuals_ROR_p_m$cor_mean),
-  sd_cor = c(l_b_6_ROR_p$cor_sd, l_b_771_ROR_p$cor_sd, l_b_nodes_ROR_p$cor_sd, l_b_residuals_ROR_p_a$cor_sd, l_b_residuals_ROR_p_m$cor_sd),
-  MSE_mean = c(l_b_6_ROR_p$MSE_mean, l_b_771_ROR_p$MSE_mean, l_b_nodes_ROR_p$MSE_mean, l_b_residuals_ROR_p_a$MSE_mean, l_b_residuals_ROR_p_m$MSE_mean),
-  MSE_sd = c(l_b_6_ROR_p$MSE_sd, l_b_771_ROR_p$MSE_sd, l_b_nodes_ROR_p$MSE_sd, l_b_residuals_ROR_p_a$MSE_sd, l_b_residuals_ROR_p_m$MSE_sd)
-)
-kable(data_table)
-```
-
-## Lasso - Repeated cross-validation
-200 repeats of five fold cross-validation
-
-### 6 genes -> proliferation score (lasso - repeated cross-validation)
-```{r}
-load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lc_obj_6_prolif.RData")
-l_c_6_p <- report02_out(lc_obj_6_prolif)
-```
-### 6 genes -> ROR_proliferation score (lasso - repeated cross-validation)
-```{r}
-load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lc_obj_6_RORprolif.RData")
-l_c_6_ROR_p <- report02_out(lc_obj_6_RORprolif)
-```
-
-### 771 genes -> proliferation score (lasso - repeated cross-validation)
-```{r}
-load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lc_obj_771_prolif.RData")
-l_c_771_p <- report02_out(lc_obj_771_prolif)
-```
-
-### 771 genes -> ROR-proliferation score (lasso - repeated cross-validation)
-```{r}
-load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lc_obj_771_RORprolif.RData")
-l_c_771_ROR_p <- report02_out(lc_obj_771_RORprolif)
-```
-
-### node values -> proliferation score (lasso - repeated cross-validation)
-```{r}
-load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lc_obj_nodes_prolif.RData")
-l_c_nodes_p <- report02_out(lc_obj_nodes_prolif)
-```
-
-### node values -> ROR-proliferation score (lasso - repeated cross-validation)
-```{r}
-load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lc_obj_nodes_RORprolif.RData")
-l_c_nodes_ROR_p <- report02_out(lc_obj_nodes_RORprolif)
-```
-
-### Mechanistic + Residuals (additive) -> proliferation score (lasso - repeated cross-validation)
-```{r}
-load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lc_obj_residuals_771_p_a.RData")
-l_c_residuals_771_p_a <- report02_out(lc_obj_residuals_771_p_a)
-```
-
-### Mechanistic + Residuals (multiplicative) -> proliferation score (lasso - repeated cross-validation)
-```{r}
-load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lc_obj_residuals_771_p_m.RData")
-l_c_residuals_771_p_m <- report02_out(lc_obj_residuals_771_p_m)
-```
-
-### Mechnaistic + Residuals (additive) -> ROR-proliferation score (lasso - repeated cross-validation)
-```{r}
-load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lc_obj_residuals_771_ROR_p_a.RData")
-l_c_residuals_ROR_p_a <- report02_out(lc_obj_residuals_771_ROR_p_a)
-```
-
-### Mechnaistic + Residuals (multiplicative) -> ROR-proliferation score (lasso - repeated cross-validation)
-```{r}
-load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lc_obj_residuals_771_ROR_p_m.RData")
-l_c_residuals_ROR_p_m <- report02_out(lc_obj_residuals_771_ROR_p_m)
-```
-
-### Summery results: lasso proliferation score (repeated cross-validation) 
-```{r}
-library(knitr)
-data_table <- data.frame(
-  Model = c("lasso 6 genes", "lasso 771 genes", "Nodes", "Residual additive", "Residual multiplicative"),
-  cor_mean = c(l_c_6_p$cor_mean, l_c_771_p$cor_mean, l_c_nodes_p$cor_mean, l_c_residuals_771_p_a$cor_mean, l_c_residuals_771_p_m$cor_mean),
-  sd_cor = c(l_c_6_p$cor_sd, l_c_771_p$cor_sd, l_c_nodes_p$cor_sd, l_c_residuals_771_p_a$cor_sd, l_c_residuals_771_p_m$cor_sd),
-  MSE_mean = c(l_c_6_p$MSE_mean, l_b_771_p$MSE_mean, l_c_nodes_p$MSE_mean, l_c_residuals_771_p_a$MSE_mean, l_c_residuals_771_p_m$MSE_mean),
-  MSE_sd = c(l_c_6_p$MSE_sd, l_c_771_p$MSE_sd, l_c_nodes_p$MSE_sd, l_c_residuals_771_p_a$MSE_sd, l_c_residuals_771_p_m$MSE_sd)
-)
-kable(data_table)
-```
-
-### Summery results: lasso ROR+proliferation score (repeated cross-validation) 
-```{r}
-data_table <- data.frame(
-  Model = c("lasso 6 genes", "lasso 771 genes", "Nodes", "Residual additive", "Residual multiplicative"),
-  cor_mean = c(l_c_6_ROR_p$cor_mean, l_c_771_ROR_p$cor_mean, l_c_nodes_ROR_p$cor_mean, l_c_residuals_ROR_p_a$cor_mean, l_c_residuals_ROR_p_m$cor_mean),
-  sd_cor = c(l_c_6_ROR_p$cor_sd, l_c_771_ROR_p$cor_sd, l_c_nodes_ROR_p$cor_sd, l_c_residuals_ROR_p_a$cor_sd, l_c_residuals_ROR_p_m$cor_sd),
-  MSE_mean = c(l_c_6_ROR_p$MSE_mean, l_c_771_ROR_p$MSE_mean, l_c_nodes_ROR_p$MSE_mean, l_c_residuals_ROR_p_a$MSE_mean, l_c_residuals_ROR_p_m$MSE_mean),
-  MSE_sd = c(l_c_6_ROR_p$MSE_sd, l_c_771_ROR_p$MSE_sd, l_c_nodes_ROR_p$MSE_sd, l_c_residuals_ROR_p_a$MSE_sd, l_c_residuals_ROR_p_m$MSE_sd)
-)
-kable(data_table)
 ```
@@
   MSE_sd = c(r_b_771_p$MSE_sd, r_b_771_ROR_p$MSE_sd, r_c_771_p$MSE_sd, r_c_771_ROR_p$MSE_sd)
+)
+kable(data_table)
+```
+
+# Lasso - Bootstrap
+### 771 genes -> proliferation score (lasso - bootstrap)
+```{r}
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_771_prolif.RData")
+l_b_771_p <- report02_out(lb_obj_771_prolif)
+```
+
+### 771 genes -> ROR-proliferation score (lasso - bootstrap)
+```{r}
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_771_RORprolif.RData")
+l_b_771_ROR_p <- report02_out(lb_obj_771_RORprolif)
+```
+
+## Lasso - Repeated cross-validation
+### 771 genes -> proliferation score (lasso - repeated cross-validation)
+```{r}
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lc_obj_771_prolif.RData")
+l_c_771_p <- report02_out(lc_obj_771_prolif)
+```
+
+### 771 genes -> ROR-proliferation score (lasso - repeated cross-validation)
+```{r}
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lc_obj_771_RORprolif.RData")
+l_c_771_ROR_p <- report02_out(lc_obj_771_RORprolif)
+```
+
+### Summery results: lasso 771 genes bootstrap and repeated cross-validation
+```{r}
+data_table <- data.frame(
+  Model = c("prolif boot", "ROR-prolif boot", "prolif rep cross-val", "ROR-prolif rep cross-val"),
+  cor_mean = c(l_b_771_p$cor_mean, l_b_771_ROR_p$cor_mean, l_c_771_p$cor_mean, l_c_771_ROR_p$cor_mean),
+  sd_cor = c(l_b_771_p$cor_sd, l_b_771_ROR_p$cor_sd, l_c_771_p$cor_sd, l_c_771_ROR_p$cor_sd),
+  MSE_mean = c(l_b_771_p$MSE_mean, l_b_771_ROR_p$MSE_mean, l_c_771_p$MSE_mean, l_c_771_ROR_p$MSE_mean),
+  MSE_sd = c(l_b_771_p$MSE_sd, l_b_771_ROR_p$MSE_sd, l_c_771_p$MSE_sd, l_c_771_ROR_p$MSE_sd)
 )
@@
   MSE_sd = c(xg_b_771_p$MSE_sd, xg_b_771_ROR_p$MSE_sd, xg_c_771_p$MSE_sd, xg_c_771_ROR_p$MSE_sd)
+)
+kable(data_table)
+```
+
+# MECHANISTIC MODEL
+### 6 genes -> proliferation score (lasso - bootstrap)
+```{r}
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_6_prolif.RData")
+l_b_6_p <- report02_out(lb_obj_6_prolif)
+```
+
+### 6 genes -> ROR_proliferation score (lasso - bootstrap)
+```{r}
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_6_RORprolif.RData")
+l_b_6_ROR_p <- report02_out(lb_obj_6_RORprolif)
+```
+
+### 6 genes -> proliferation score (lasso - repeated cross-validation)
+```{r}
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lc_obj_6_prolif.RData")
+l_c_6_p <- report02_out(lc_obj_6_prolif)
+```
+
+### 6 genes -> ROR_proliferation score (lasso - repeated cross-validation)
+```{r}
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lc_obj_6_RORprolif.RData")
+l_c_6_ROR_p <- report02_out(lc_obj_6_RORprolif)
+```
+
+### node values -> proliferation score (lasso - bootstrap)
+```{r}
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_nodes_prolif.RData")
+l_b_nodes_p <- report02_out(lb_obj_nodes_prolif)
+```
+
+### node values -> ROR-proliferation score (lasso - bootstrap) 
+```{r}
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_nodes_RORprolif.RData")
+l_b_nodes_ROR_p <- report02_out(lb_obj_nodes_RORprolif)
+```
+
+### node values -> proliferation score (lasso - repeated cross-validation)
+```{r}
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lc_obj_nodes_prolif.RData")
+l_c_nodes_p <- report02_out(lc_obj_nodes_prolif)
+```
+
+### node values -> ROR-proliferation score (lasso - repeated cross-validation)
+```{r}
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lc_obj_nodes_RORprolif.RData")
+l_c_nodes_ROR_p <- report02_out(lc_obj_nodes_RORprolif)
+```
+
+### Mechanistic + Residuals (additive) -> proliferation score  (lasso - bootstrap)
+```{r}
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_residuals_771_prolif_a.RData")
+l_b_residuals_771_p_a <- report02_out(lb_obj_residuals_771_prolif_a)
+```
+
+### Mechanistic + Residuals (multiplicative) -> proliferation score   (lasso - bootstrap)
+```{r}
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_residuals_771_prolif_m.RData")
+l_b_residuals_771_p_m <- report02_out(lb_obj_residuals_771_prolif_m)
+```
+
+### Mechanistic + Residuals (additive) -> ROR-proliferation score  (lasso - bootstrap)
+```{r}
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_residuals_771_RORprolif_a.RData")
+l_b_residuals_ROR_p_a <- report02_out(lb_obj_residuals_771_RORprolif_a)
+```
+
+### Mechanistic + Residuals (multiplicative) -> ROR-proliferation score (lasso - bootstrap)
+```{r}
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_residuals_771_RORprolif_m.RData")
+l_b_residuals_ROR_p_m <- report02_out(lb_obj_residuals_771_RORprolif_m)
+```
+
+### Mechanistic + Residuals (additive) -> proliferation score (lasso - repeated cross-validation)
+```{r}
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lc_obj_residuals_771_p_a.RData")
+l_c_residuals_771_p_a <- report02_out(lc_obj_residuals_771_p_a)
+```
+
+### Mechanistic + Residuals (multiplicative) -> proliferation score (lasso - repeated cross-validation)
+```{r}
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lc_obj_residuals_771_p_m.RData")
+l_c_residuals_771_p_m <- report02_out(lc_obj_residuals_771_p_m)
+```
+
+### Mechanistic + Residuals (additive) -> ROR-proliferation score (lasso - repeated cross-validation)
+```{r}
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lc_obj_residuals_771_ROR_p_a.RData")
+l_c_residuals_ROR_p_a <- report02_out(lc_obj_residuals_771_ROR_p_a)
+```
+
+### Mechanistic + Residuals (multiplicative) -> ROR-proliferation score (lasso - repeated cross-validation)
+```{r}
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lc_obj_residuals_771_ROR_p_m.RData")
+l_c_residuals_ROR_p_m <- report02_out(lc_obj_residuals_771_ROR_p_m)
+```
+
+### Summery results Mechanistic: lasso proliferation score (bootstrap) 
+```{r}
+library(knitr)
+data_table <- data.frame(
+  Model = c("lasso 6 genes", "lasso 771 genes", "Nodes", "Residual additive", "Residual multiplicative"),
+  cor_mean = c(l_b_6_p$cor_mean, l_b_771_p$cor_mean, l_b_nodes_p$cor_mean, l_b_residuals_771_p_a$cor_mean, l_b_residuals_771_p_m$cor_mean),
+  sd_cor = c(l_b_6_p$cor_sd, l_b_771_p$cor_sd, l_b_nodes_p$cor_sd, l_b_residuals_771_p_a$cor_sd, l_b_residuals_771_p_m$cor_sd),
+  MSE_mean = c(l_b_6_p$MSE_mean, l_b_771_p$MSE_mean, l_b_nodes_p$MSE_mean, l_b_residuals_771_p_a$MSE_mean, l_b_residuals_771_p_m$MSE_mean),
+  MSE_sd = c(l_b_6_p$MSE_sd, l_b_771_p$MSE_sd, l_b_nodes_p$MSE_sd, l_b_residuals_771_p_a$MSE_sd, l_b_residuals_771_p_m$MSE_sd)
+)
+kable(data_table)
+```
+
+### Summery results Mechanistic: lasso ROR+proliferation score (bootstrap) 
+```{r}
+data_table <- data.frame(
+  Model = c("lasso 6 genes", "lasso 771 genes", "Nodes", "Residual additive", "Residual multiplicative"),
+  cor_mean = c(l_b_6_ROR_p$cor_mean, l_b_771_ROR_p$cor_mean, l_b_nodes_ROR_p$cor_mean, l_b_residuals_ROR_p_a$cor_mean, l_b_residuals_ROR_p_m$cor_mean),
+  sd_cor = c(l_b_6_ROR_p$cor_sd, l_b_771_ROR_p$cor_sd, l_b_nodes_ROR_p$cor_sd, l_b_residuals_ROR_p_a$cor_sd, l_b_residuals_ROR_p_m$cor_sd),
+  MSE_mean = c(l_b_6_ROR_p$MSE_mean, l_b_771_ROR_p$MSE_mean, l_b_nodes_ROR_p$MSE_mean, l_b_residuals_ROR_p_a$MSE_mean, l_b_residuals_ROR_p_m$MSE_mean),
+  MSE_sd = c(l_b_6_ROR_p$MSE_sd, l_b_771_ROR_p$MSE_sd, l_b_nodes_ROR_p$MSE_sd, l_b_residuals_ROR_p_a$MSE_sd, l_b_residuals_ROR_p_m$MSE_sd)
+)
+kable(data_table)
+```
+
+### Summery results Mechanistic: lasso proliferation score (repeated cross-validation) 
+```{r}
+library(knitr)
+data_table <- data.frame(
+  Model = c("lasso 6 genes", "lasso 771 genes", "Nodes", "Residual additive", "Residual multiplicative"),
+  cor_mean = c(l_c_6_p$cor_mean, l_c_771_p$cor_mean, l_c_nodes_p$cor_mean, l_c_residuals_771_p_a$cor_mean, l_c_residuals_771_p_m$cor_mean),
+  sd_cor = c(l_c_6_p$cor_sd, l_c_771_p$cor_sd, l_c_nodes_p$cor_sd, l_c_residuals_771_p_a$cor_sd, l_c_residuals_771_p_m$cor_sd),
+  MSE_mean = c(l_c_6_p$MSE_mean, l_b_771_p$MSE_mean, l_c_nodes_p$MSE_mean, l_c_residuals_771_p_a$MSE_mean, l_c_residuals_771_p_m$MSE_mean),
+  MSE_sd = c(l_c_6_p$MSE_sd, l_c_771_p$MSE_sd, l_c_nodes_p$MSE_sd, l_c_residuals_771_p_a$MSE_sd, l_c_residuals_771_p_m$MSE_sd)
+)
+kable(data_table)
+```
+
+### Summery results Mechanistic: lasso ROR+proliferation score (repeated cross-validation) 
+```{r}
+data_table <- data.frame(
+  Model = c("lasso 6 genes", "lasso 771 genes", "Nodes", "Residual additive", "Residual multiplicative"),
+  cor_mean = c(l_c_6_ROR_p$cor_mean, l_c_771_ROR_p$cor_mean, l_c_nodes_ROR_p$cor_mean, l_c_residuals_ROR_p_a$cor_mean, l_c_residuals_ROR_p_m$cor_mean),
+  sd_cor = c(l_c_6_ROR_p$cor_sd, l_c_771_ROR_p$cor_sd, l_c_nodes_ROR_p$cor_sd, l_c_residuals_ROR_p_a$cor_sd, l_c_residuals_ROR_p_m$cor_sd),
+  MSE_mean = c(l_c_6_ROR_p$MSE_mean, l_c_771_ROR_p$MSE_mean, l_c_nodes_ROR_p$MSE_mean, l_c_residuals_ROR_p_a$MSE_mean, l_c_residuals_ROR_p_m$MSE_mean),
+  MSE_sd = c(l_c_6_ROR_p$MSE_sd, l_c_771_ROR_p$MSE_sd, l_c_nodes_ROR_p$MSE_sd, l_c_residuals_ROR_p_a$MSE_sd, l_c_residuals_ROR_p_m$MSE_sd)
 )
@@
 # Summery of all results
+
+### Summery results: ridge 771 genes bootstrap and repeated cross-validation
+```{r}
+data_table <- tibble(
+  Model = c("prolif boot", "ROR-prolif boot", "prolif rep cross-val", "ROR-prolif rep cross-val"),
+  cor_mean = c(r_b_771_p$cor_mean, r_b_771_ROR_p$cor_mean, r_c_771_p$cor_mean, r_c_771_ROR_p$cor_mean),
+  sd_cor = c(r_b_771_p$cor_sd, r_b_771_ROR_p$cor_sd, r_c_771_p$cor_sd, r_c_771_ROR_p$cor_sd),
+  MSE_mean = c(r_b_771_p$MSE_mean, r_b_771_ROR_p$MSE_mean, r_c_771_p$MSE_mean, r_c_771_ROR_p$MSE_mean),
+  MSE_sd = c(r_b_771_p$MSE_sd, r_b_771_ROR_p$MSE_sd, r_c_771_p$MSE_sd, r_c_771_ROR_p$MSE_sd)
+)
+data_table |>  mutate(across(where(is.numeric), ~ round(., digits = 3))) |>  kable()
+```
+
+### Summery results: lasso 771 genes bootstrap and repeated cross-validation
+```{r}
+data_table <- data.frame(
+  Model = c("prolif boot", "ROR-prolif boot", "prolif rep cross-val", "ROR-prolif rep cross-val"),
+  cor_mean = c(l_b_771_p$cor_mean, l_b_771_ROR_p$cor_mean, l_c_771_p$cor_mean, l_c_771_ROR_p$cor_mean),
+  sd_cor = c(l_b_771_p$cor_sd, l_b_771_ROR_p$cor_sd, l_c_771_p$cor_sd, l_c_771_ROR_p$cor_sd),
+  MSE_mean = c(l_b_771_p$MSE_mean, l_b_771_ROR_p$MSE_mean, l_c_771_p$MSE_mean, l_c_771_ROR_p$MSE_mean),
+  MSE_sd = c(l_b_771_p$MSE_sd, l_b_771_ROR_p$MSE_sd, l_c_771_p$MSE_sd, l_c_771_ROR_p$MSE_sd)
+)
+kable(data_table)
+```
+
+### Summery results: elastic net 771 genes bootstrap and repeated cross-validation
+```{r}
+data_table <- tibble(
+  Model = c("prolif boot", "ROR-prolif boot", "prolif rep cross-val", "ROR-prolif rep cross-val"),
+  cor_mean = c(e_b_771_p$cor_mean, e_b_771_ROR_p$cor_mean, e_c_771_p$cor_mean, e_c_771_ROR_p$cor_mean),
+  sd_cor = c(e_b_771_p$cor_sd, e_b_771_ROR_p$cor_sd, e_c_771_p$cor_sd, e_c_771_ROR_p$cor_sd),
+  MSE_mean = c(e_b_771_p$MSE_mean, e_b_771_ROR_p$MSE_mean, e_c_771_p$MSE_mean, e_c_771_ROR_p$MSE_mean),
+  MSE_sd = c(e_b_771_p$MSE_sd, e_b_771_ROR_p$MSE_sd, e_c_771_p$MSE_sd, e_c_771_ROR_p$MSE_sd)
+)
+data_table |>  mutate(across(where(is.numeric), ~ round(., digits = 3))) |>  kable()
+```
+
+### Summery results: Boosting with stumps 771 genes bootstrap and repeated cross-validation
+```{r}
+data_table <- tibble(
+  Model = c("prolif boot", "ROR-prolif boot", "prolif rep cross-val", "ROR-prolif rep cross-val"),
+  cor_mean = c(xg_b_771_p$cor_mean, xg_b_771_ROR_p$cor_mean, xg_c_771_p$cor_mean, xg_c_771_ROR_p$cor_mean),
+  sd_cor = c(xg_b_771_p$cor_sd, xg_b_771_ROR_p$cor_sd, xg_c_771_p$cor_sd, xg_c_771_ROR_p$cor_sd),
+  MSE_mean = c(xg_b_771_p$MSE_mean, xg_b_771_ROR_p$MSE_mean, xg_c_771_p$MSE_mean, xg_c_771_ROR_p$MSE_mean),
+  MSE_sd = c(xg_b_771_p$MSE_sd, xg_b_771_ROR_p$MSE_sd, xg_c_771_p$MSE_sd, xg_c_771_ROR_p$MSE_sd)
+)
+data_table |>  mutate(across(where(is.numeric), ~ round(., digits = 3))) |>  kable()
+```
+
+# Summary using Mechanistic model
+
 ### Summery results: lasso proliferation score (bootstrap) 
@@
   MSE_sd = c(l_c_6_ROR_p$MSE_sd, l_c_771_ROR_p$MSE_sd, l_c_nodes_ROR_p$MSE_sd, l_c_residuals_ROR_p_a$MSE_sd, l_c_residuals_ROR_p_m$MSE_sd)
-)
-data_table |>  mutate(across(where(is.numeric), ~ round(., digits = 3))) |>  kable()
-```
-
-### Summery results: ridge 771 genes bootstrap and repeated cross-validation
-```{r}
-data_table <- tibble(
-  Model = c("prolif boot", "ROR-prolif boot", "prolif rep cross-val", "ROR-prolif rep cross-val"),
-  cor_mean = c(r_b_771_p$cor_mean, r_b_771_ROR_p$cor_mean, r_c_771_p$cor_mean, r_c_771_ROR_p$cor_mean),
-  sd_cor = c(r_b_771_p$cor_sd, r_b_771_ROR_p$cor_sd, r_c_771_p$cor_sd, r_c_771_ROR_p$cor_sd),
-  MSE_mean = c(r_b_771_p$MSE_mean, r_b_771_ROR_p$MSE_mean, r_c_771_p$MSE_mean, r_c_771_ROR_p$MSE_mean),
-  MSE_sd = c(r_b_771_p$MSE_sd, r_b_771_ROR_p$MSE_sd, r_c_771_p$MSE_sd, r_c_771_ROR_p$MSE_sd)
-)
-data_table |>  mutate(across(where(is.numeric), ~ round(., digits = 3))) |>  kable()
-```
-
-### Summery results: elastic net 771 genes bootstrap and repeated cross-validation
-```{r}
-data_table <- tibble(
-  Model = c("prolif boot", "ROR-prolif boot", "prolif rep cross-val", "ROR-prolif rep cross-val"),
-  cor_mean = c(e_b_771_p$cor_mean, e_b_771_ROR_p$cor_mean, e_c_771_p$cor_mean, e_c_771_ROR_p$cor_mean),
-  sd_cor = c(e_b_771_p$cor_sd, e_b_771_ROR_p$cor_sd, e_c_771_p$cor_sd, e_c_771_ROR_p$cor_sd),
-  MSE_mean = c(e_b_771_p$MSE_mean, e_b_771_ROR_p$MSE_mean, e_c_771_p$MSE_mean, e_c_771_ROR_p$MSE_mean),
-  MSE_sd = c(e_b_771_p$MSE_sd, e_b_771_ROR_p$MSE_sd, e_c_771_p$MSE_sd, e_c_771_ROR_p$MSE_sd)
-)
-data_table |>  mutate(across(where(is.numeric), ~ round(., digits = 3))) |>  kable()
-```
-
-### Summery results: Boosting with stumps 771 genes bootstrap and repeated cross-validation
-```{r}
-data_table <- tibble(
-  Model = c("prolif boot", "ROR-prolif boot", "prolif rep cross-val", "ROR-prolif rep cross-val"),
-  cor_mean = c(xg_b_771_p$cor_mean, xg_b_771_ROR_p$cor_mean, xg_c_771_p$cor_mean, xg_c_771_ROR_p$cor_mean),
-  sd_cor = c(xg_b_771_p$cor_sd, xg_b_771_ROR_p$cor_sd, xg_c_771_p$cor_sd, xg_c_771_ROR_p$cor_sd),
-  MSE_mean = c(xg_b_771_p$MSE_mean, xg_b_771_ROR_p$MSE_mean, xg_c_771_p$MSE_mean, xg_c_771_ROR_p$MSE_mean),
-  MSE_sd = c(xg_b_771_p$MSE_sd, xg_b_771_ROR_p$MSE_sd, xg_c_771_p$MSE_sd, xg_c_771_ROR_p$MSE_sd)
 )

### 2023-04-12 R_codeP01/figures/01_correlations01.R

@@ -6,6 +6,23 @@ library(extrafont)
 library(ggplot2)
 library(gridExtra)
 
+# Boosting with stumps as base learner - bootstrap
+### 771 genes -> proliferation score 
+
+
+
+### 771 genes -> ROR-proliferation score
+
+
+
+# Boosting with stumps as base learner cross-validation
+### 771 genes -> proliferation score  
+
+
+
+### 771 genes -> ROR-proliferation score   #
+
+
 
 
 # 771 genes -> proliferation score - bootstrap
@@ -14,7 +31,13 @@ load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/r_b_obj_771_p.RD
 cor_vec_b <- r_b_obj_771_p$cor_vec
 # (lasso)
 load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_771_prolif.RData")
-cor_vec_b <- lb_obj_771_prolif
+cor_vec_b <- lb_obj_771_prolif$cor_vec
+# (elastic)
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/e_b_obj_771_p.RData")
+cor_vec_b <- e_b_obj_771_p$cor_vec
+# (boosting)
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/xg_b_obj_771_p.RData")
+cor_vec_b <- xg_b_obj_771_p$cor_vec
 
 cor_vec_b_finite <- cor_vec_b[is.finite(cor_vec_b)]
 data1 <- data.frame(correlation = cor_vec_b_finite)
@@ -26,7 +49,13 @@ load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/r_b_obj_771_ROR_
 cor_vec_b_ROR <- r_b_obj_771_ROR_p$cor_vec
 # (lasso)
 load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_771_RORprolif.RData")
-cor_vec_b_ROR <- lb_obj_771_RORprolif
+cor_vec_b_ROR <- lb_obj_771_RORprolif$cor_vec
+# (elastic Net)
+load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/e_b_obj_771_ROR_p.RData")
+cor_vec_b_ROR <- e_b_obj_771_ROR_p$cor_vec
+# (boosting)
[…]
